---
title: "Magpie Belief Figures"
output: html_document
---

# Belief information: Magpie

This contains a bunch of figures and statistics about the beliefs (both prior and posterior) for the Magpie run from August 2024. We start by loading the data and doing some basic cleaning.

```{r echo = FALSE, warning=FALSE, message=FALSE}
rm(list=ls())

# load the packages
library(here)
library(tidyverse)
library(ggdist)
library(ggridges)
library(Polychrome)
library(corrr)
source(here("R/visualise/supplementaryFunctions.R"))

# Define subfolders
processed_files_mastodon_dir <- "data/mastodon/files/processed"
figures_files_mastodon_dir <- "data/mastodon/files/figures"
all_char_cols <- cols(.default = "c")
DRY_RUN <- FALSE
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
# set the colours
polarityColours <- c("left"="#3399CC","na"="#9999FF","right"="#CC0066")
politicalIDColours <- c("democrat"="#3399CC","independent"="#9999FF",
                     "republican"="#CC0066")

topicColours <- c("Trans"="#AA3399","Gender"="#FF99FF",
                  "Climate"="#00AA66","Environment"="#88EE22",
                  "AI"="#0066CC","SciTech"="#99CCFF",
                  "Israel"="#CC9900","Foreign"="#FFCC33",
                  "MoneyEcon" = "#555555", "CrimeGuns"="#888888",
                  "Religion" = "#AAAAAA", "Health"="#CCCCCC",
                  "Fun"="#9999FF","Total"="#CC0000")

#conditionColours <- c("Control"="#44AA44","Right"="#660066")

conditionColours <- c("Left"="#99CCFF",
                      "Control"="#339933","Right"="#FF99CC")
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
# read all of the long files
# Consistent file paths and loading
dcbl <- read_csv(here(processed_files_mastodon_dir, "control", "data_priors_long.csv"),
                 col_types = all_char_cols)
dcal <- read_csv(here(processed_files_mastodon_dir, "control", "data_posteriors_long.csv"),
                 col_types = all_char_cols)
drbl <- read_csv(here(processed_files_mastodon_dir, "right", "data_priors_long.csv"),
                 col_types = all_char_cols)
dral <- read_csv(here(processed_files_mastodon_dir, "right", "data_posteriors_long.csv"),
                 col_types = all_char_cols)
dlbl <- read_csv(here(processed_files_mastodon_dir, "left", "data_priors_long.csv"),
                 col_types = all_char_cols)
dlal <- read_csv(here(processed_files_mastodon_dir, "left", "data_posteriors_long.csv"),
                 col_types = all_char_cols)

# remove the people who did not complete the After survey
# save them in a file in case need to look at later
dc_first <- dcbl[!(dcbl$Subject %in% dcal$Subject),]
dr_first <- drbl[!(drbl$Subject %in% dral$Subject),]
dl_first <- dlbl[!(dlbl$Subject %in% dlal$Subject),]
da_first <- rbind(dc_first,dr_first,dl_first)
# save combined file
beliefs_long_first_file <- here(processed_files_mastodon_dir, "combined", 
                          "firstonly", "beliefs_long.csv")
da_first %>% save_processed_file(file = beliefs_long_first_file)


dc_before <- dcbl[dcbl$Subject %in% dcal$Subject,]
dc_after <- dcal[dcal$Subject %in% dcbl$Subject,]
dr_before <- drbl[drbl$Subject %in% dral$Subject,]
dr_after <- dral[dral$Subject %in% drbl$Subject,]
dl_before <- dlbl[dlbl$Subject %in% dlal$Subject,]
dl_after <- dlal[dlal$Subject %in% dlbl$Subject,]
dl <- rbind(dc_before,dc_after,dr_before,dr_after,dl_before,dl_after)

# save combined file
beliefs_long_file <- here(processed_files_mastodon_dir, "combined", "beliefs_long.csv")
dl %>% save_processed_file(file = beliefs_long_file)
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
# read all of the summary files
dcsb <- read_csv(here(processed_files_mastodon_dir, "control", "data_summary_priors.csv"),
                 col_types = all_char_cols)
dcsa <- read_csv(here(processed_files_mastodon_dir, "control", "data_summary_posteriors.csv"),
                 col_types = all_char_cols)
drsb <- read_csv(here(processed_files_mastodon_dir, "right", "data_summary_priors.csv"),
                 col_types = all_char_cols)
drsa <- read_csv(here(processed_files_mastodon_dir, "right", "data_summary_posteriors.csv"),
                 col_types = all_char_cols)
dlsb <- read_csv(here(processed_files_mastodon_dir, "left", "data_summary_priors.csv"),
                 col_types = all_char_cols)
dlsa <- read_csv(here(processed_files_mastodon_dir, "left", "data_summary_posteriors.csv"),
                 col_types = all_char_cols)

# remove the people who did not complete the After survey
# save them in a file in case need to look at later
dc_first <- dcsb[!(dcsb$Subject %in% dcsa$Subject),]
dr_first <- drsb[!(drsb$Subject %in% drsa$Subject),]
dl_first <- dlsb[!(dlsb$Subject %in% dlsa$Subject),]
ds_first <- rbind(dc_first,dr_first,dl_first)

# save combined file
beliefs_summary_first_file <- here(processed_files_mastodon_dir, "combined", 
                                   "firstonly", "belief_summary.csv")
ds_first %>% save_processed_file(file = beliefs_long_file)


dc_before <- dcsb[dcsb$Subject %in% dcsa$Subject,]
dc_after <- dcsa[dcsa$Subject %in% dcsb$Subject,]
dr_before <- drsb[drsb$Subject %in% drsa$Subject,]
dr_after <- drsa[drsa$Subject %in% drsb$Subject,]
dl_before <- dlsb[dlsb$Subject %in% dlsa$Subject,]
dl_after <- dlsa[dlsa$Subject %in% dlsb$Subject,]
ds <- rbind(dc_before,dc_after,dr_before,dr_after,dl_before,dl_after)

# save combined file
beliefs_summary_file <- here(processed_files_mastodon_dir, "combined", "belief_summary.csv")
ds %>% save_processed_file(file = beliefs_summary_file)
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
# set factor levels to be nice
dl$Condition <- factor(dl$Condition, levels=c("Left","Control","Right"))
dl$TimePoint <- factor(dl$TimePoint, levels=c("Before","After"))
dl$Polarity <- factor(dl$Polarity, levels=c("left","na","right"))
dl$Topic <- factor(dl$Topic, 
                   levels=c("Trans","Gender","Climate","Environment",
                            "AI","SciTech","Israel","Foreign",
                            "CrimeGuns","Health","MoneyEcon",
                            "Religion","Fun","Total"))
dl <- dl %>%
  mutate(across(
    .cols = matches("Belief"),
    .fns = as.numeric
  ))

ds$Condition <- factor(ds$Condition, levels=c("Left","Control","Right"))
ds$TimePoint <- factor(ds$TimePoint, levels=c("Before","After"))
ds$Topic <- factor(ds$Topic, 
                   levels=c("Trans","Gender","Climate","Environment",
                            "AI","SciTech","Israel","Foreign",
                            "CrimeGuns","Health","MoneyEcon",
                            "Religion","Fun","Total"))

ds <- ds %>%
  mutate(across(
    .cols = matches("Belief"),
    .fns = as.numeric
  ))

# remove extra things to keep space tidy
rm(dcal,dcbl,dcsb,dcsa,dc_after,dc_before,dc_first,
   dral,drbl,drsb,drsa,dr_after,dr_before,dr_first,
   dlal,dlbl,dlsb,dlsa,dl_after,dl_before,dl_first)

nControl <- length(unique(ds$Subject[ds$Condition=="Control"]))
nRight <- length(unique(ds$Subject[ds$Condition=="Right"]))
nLeft <- length(unique(ds$Subject[ds$Condition=="Left"]))

set.seed(935234)
myPalLong <- createPalette(nControl+nRight+nLeft+12, 
                           c("#FF0000", "#00FF00", "#0000FF"), 
                           range = c(20, 90))
names(myPalLong) <- NULL
myPalCond <- myPalLong
myPalCond[1:3] <- conditionColours
myPalTopic <- myPalLong
myPalTopic[1:5] <- c("#AA3399","#00AA66","#0066CC","#CC9900","#CC0000")

```

There were `r nControl` in the final sample in the **Control** condition. 

There were `r nRight` in the final sample in the **Right** condition.

There were `r nLeft` in the final sample in the **Left** condition.

All analyses are only on the final sample of `r length(unique(ds$Subject))` unless otherwise stated.

## Belief analysis

### Raw belief ratings

For each statement we show the mean and distribution of ratings. They are coded so that the lower they are, the more left leaning they are; thus, ratings close to 0 indicate extreme left and close to 100 indicate extreme right. 50 is neutral. Each row is one of the statements. Those from similar topics have the same colour.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
beliefMeans <- dl %>%
    group_by(Condition,ShortText,Topic,TimePoint,Order) %>%
    summarise(muAll = mean(Belief,na.rm=TRUE),
              sdAll = sd(Belief,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$ShortText,
                                 beliefMeans$Order))

postLong <- dl %>%
  left_join(beliefMeans,by=join_by(Condition,ShortText,Topic,TimePoint,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(ShortText, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(ShortText, levels = statementLevels))

pC <- beliefMeans %>%
  filter(Condition=="Control") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=Belief,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
  geom_hline(yintercept=50,colour="black",linewidth=0.3,linetype="dashed") +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Control condition",
       subtitle = "Lower rating = more to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pC

statement_bars_control_file <- here(figures_files_mastodon_dir, "statement_bars_control.png")
ggsave(filename = statement_bars_control_file,
       plot=pC,device="png",
       width=30,height=22, units="cm")

pT <- beliefMeans %>%
  filter(Condition=="Right") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=Belief,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
  geom_hline(yintercept=50,colour="black",linewidth=0.3,linetype="dashed") +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Right condition",
       subtitle = "Lower rating = more to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pT

statement_bars_right_file <- here(figures_files_mastodon_dir, "statement_bars_right.png")
ggsave(filename = statement_bars_right_file,
       plot=pT,device="png",
       width=30,height=22, units="cm")

pT <- beliefMeans %>%
  filter(Condition=="Left") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=Belief,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
  geom_hline(yintercept=50,colour="black",linewidth=0.3,linetype="dashed") +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Left condition",
       subtitle = "Lower rating = more to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pT

statement_bars_left_file <- here(figures_files_mastodon_dir, "statement_bars_left.png")
ggsave(filename = statement_bars_left_file,
       plot=pT,device="png",
       width=30,height=22, units="cm")
```


### Change in raw beliefs

What's being plotted is the difference between posterior and prior beliefs. If positive this indicates that they are moving rightward, and if negative this indicates they are moving leftward. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
dl_change <- dl %>%
  select(Subject,Condition,TimePoint,Topic,ShortText,Belief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=Belief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    group_by(Condition,ShortText,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$ShortText,
                                 beliefMeans$Order))

postLong <- dl_change %>%
  left_join(beliefMeans,by=join_by(Condition,ShortText,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(ShortText, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(ShortText, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief change from Before to After",
       subtitle = "Negative indicates a shift to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

statement_bars_change_file <- here(figures_files_mastodon_dir, "statement_bars_change.png")
ggsave(filename = statement_bars_change_file,
       plot=p,device="png",
       width=35,height=22, units="cm")
```

### Change in beliefs by topic

This is the same as above, but collapsed across topic rather than based on individual statements. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=5}
ds <- ds %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Gender"~2,
                           Topic=="Climate"~3, Topic=="Environment"~4,
                           Topic=="AI"~5,Topic=="SciTech"~6,
                           Topic=="Israel"~7,Topic=="Foreign"~8,
                           Topic=="MoneyEcon"~9,Topic=="CrimeGuns"~10,
                           Topic=="Religion"~11,Topic=="Health"~12,
                           Topic=="Total"~13))

dl_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnBelief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=mnBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    filter(Topic!="Fun") %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

postLong <- dl_change %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(Topic, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=Topic,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  ylim(-50,50) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief change from Before to After",
       subtitle = "Negative indicates a shift to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

topic_bars_change_file <- here(figures_files_mastodon_dir, "topic_bars_change.png")
ggsave(filename = topic_bars_change_file,
       plot=p,device="png",
       width=35,height=12, units="cm")

```

We'll do the same thing but just look at the four key topics.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
dl_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnBelief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=mnBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    filter(Topic=="Trans" | Topic=="Climate" | Topic=="AI" |
             Topic=="Israel" | Topic=="Total") %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

postLong <- dl_change %>%
      filter(Topic=="Trans" | Topic=="Climate" | Topic=="AI" |
             Topic=="Israel" | Topic=="Total") %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(Topic, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=Topic,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  ylim(-50,50) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief change from Before to After",
       subtitle = "Negative indicates a shift to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

topic_key_bars_change_file <- here(figures_files_mastodon_dir, "topic_key_bars_change.png")
ggsave(filename = topic_key_bars_change_file,
       plot=p,device="png",
       width=30,height=8, units="cm")

```

### Extremeness belief ratings

For each statement we show the mean and distribution of ratings. They are coded so that the lower they are, the more central they are. Thus a rating of 0 indicates that they selected 50 (i.e., exactly neutral). A rating of 20 could be either 30 or 70 (it is 20 away from neutral). The most extreme belief rating possible is 50 (corresponding to selecting 0 or 100).


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
beliefMeans <- dl %>%
    group_by(Condition,ShortText,Topic,TimePoint,Order) %>%
    summarise(muAll = mean(ExtremeBelief,na.rm=TRUE),
              sdAll = sd(ExtremeBelief,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$ShortText,
                                 beliefMeans$Order))

postLong <- dl %>%
  left_join(beliefMeans,by=join_by(Condition,ShortText,Topic,TimePoint,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(ShortText, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(ShortText, levels = statementLevels))

pC <- beliefMeans %>%
  filter(Condition=="Control") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=ExtremeBelief,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Control condition",
       subtitle = "Lower rating = more to the left") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pC

statement_extreme_bars_control_file <- here(figures_files_mastodon_dir, "statement_extreme_bars_control.png")
ggsave(filename = statement_extreme_bars_control_file,
       plot=pC,device="png",
       width=30,height=22, units="cm")

pT <- beliefMeans %>%
  filter(Condition=="Right") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=ExtremeBelief,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Right condition",
       subtitle = "Lower indicates being less extreme") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pT

statement_extreme_bars_right_file <- here(figures_files_mastodon_dir, "statement_extreme_bars_right.png")
ggsave(filename = statement_extreme_bars_right_file,
       plot=pT,device="png",
       width=30,height=22, units="cm")

pT <- beliefMeans %>%
  filter(Condition=="Left") %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=ExtremeBelief,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~TimePoint,ncol=2) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief ratings: Left condition",
       subtitle = "Lower indicates being less extreme") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
pT

statement_extreme_bars_left_file <- here(figures_files_mastodon_dir, "statement_extreme_bars_left.png")
ggsave(filename = statement_extreme_bars_left_file,
       plot=pT,device="png",
       width=30,height=22, units="cm")
```


### Change in extremeness of beliefs

What's being plotted is the difference between the extremeness of beliefs from before to after. If positive this indicates they are becoming more extreme; if negative it indicates they are becoming less extreme. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
dl_change <- dl %>%
  select(Subject,Condition,TimePoint,Topic,ShortText,ExtremeBelief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=ExtremeBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    group_by(Condition,ShortText,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$ShortText,
                                 beliefMeans$Order))

postLong <- dl_change %>%
  left_join(beliefMeans,by=join_by(Condition,ShortText,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(ShortText, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(ShortText, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=ShortText,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Extremeness of belief change from Before to After",
       subtitle = "Negative indicates becoming less extreme") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
p

statement_extreme_bars_change_file <- here(figures_files_mastodon_dir, "statement_extreme_bars_change.png")
ggsave(filename = statement_extreme_bars_change_file,
       plot=p,device="png",
       width=30,height=22, units="cm")
```

### Change in extremeness of beliefs by topic

This is the same as above, but collapsed across topic rather than based on individual statements. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=5}
dl_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnExtremeBelief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=mnExtremeBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    filter(Topic!="Fun") %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

postLong <- dl_change %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(Topic, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=Topic,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  ylim(-50,50) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Extremeness of belief change from Before to After",
       subtitle = "Negative indicates becoming less extreme") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

topic_extreme_bars_change_file <- here(figures_files_mastodon_dir, "topic_extreme_bars_change.png")
ggsave(filename = topic_extreme_bars_change_file,
       plot=p,device="png",
       width=30,height=12, units="cm")

```

We'll do the same thing but just look at the four key topics.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
dl_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnExtremeBelief,Order) %>%
  pivot_wider(names_from=TimePoint,values_from=mnExtremeBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))
dl_change$Condition <- factor(dl_change$Condition, levels=c("Left","Control","Right"))

beliefMeans <- dl_change %>%
    filter(Topic=="Trans" | Topic=="Climate" | Topic=="AI" |
             Topic=="Israel" | Topic=="Total") %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

postLong <- dl_change %>%
      filter(Topic=="Trans" | Topic=="Climate" | Topic=="AI" |
             Topic=="Israel" | Topic=="Total") %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(ShortText = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(ShortText = factor(Topic, levels = statementLevels))

p <- beliefMeans %>%
  ggplot(mapping=aes(x=Topic,y=muAll,fill=Topic)) +
  geom_jitter(data=postLong,mapping=aes(y=BeliefChange,
                                        x=ShortText,colour=Topic),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  coord_flip() +  
  scale_x_discrete(limits = rev) +
  ylim(-50,50) +
  facet_wrap(~Condition,ncol=3) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Extremeness of belief change from Before to After",
       subtitle = "Negative indicates becoming less extreme") +
  theme(axis.text.x = element_text(size=10, hjust=0.5),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

topic_key_extreme_bars_change_file <- here(figures_files_mastodon_dir, "topic_key_extreme_bars_change.png")
ggsave(filename = topic_key_extreme_bars_change_file,
       plot=p,device="png",
       width=30,height=8, units="cm")

```

### Correlations between beliefs

Here is a correlation matrix between beliefs for people, so we can see how they are related to each other.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=6}
beliefMeans <- dl %>%
    group_by(Condition,ShortText,Topic,TimePoint,Order) %>%
    summarise(muAll = mean(Belief,na.rm=TRUE),
              sdAll = sd(Belief,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

postLong <- dl %>%
  left_join(beliefMeans,
            by=join_by(Condition,ShortText,Topic,TimePoint,Order))

beforeLongC <- postLong %>% 
  filter(TimePoint=="Before" & Condition=="Control")
afterLongC <- postLong %>% 
  filter(TimePoint=="After" & Condition=="Control")

p <- plotCluster(beforeLongC,"Control",colourChoice="Topic",
                 titleText="Prior belief correlations: ")

p

prior_belief_correlations_topic_control_file <- here(figures_files_mastodon_dir, "prior_belief_correlations_topic_control.png")
ggsave(filename = prior_belief_correlations_topic_control_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

p <- plotCluster(afterLongC,"Control",colourChoice="Topic",
                 titleText="Posterior belief correlations: ")

p

posterior_belief_correlations_topic_control_file <- here(figures_files_mastodon_dir, "posterior_belief_correlations_topic_control.png")
ggsave(filename = posterior_belief_correlations_topic_control_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

beforeLongT <- postLong %>% 
  filter(TimePoint=="Before" & Condition=="Right")
afterLongT <- postLong %>% 
  filter(TimePoint=="After" & Condition=="Right")

p <- plotCluster(beforeLongT,"Right",colourChoice="Topic",
                 titleText="Prior belief correlations: ")

p

prior_belief_correlations_topic_right_file <- here(figures_files_mastodon_dir, "prior_belief_correlations_topic_right.png")
ggsave(filename = prior_belief_correlations_topic_right_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

p <- plotCluster(afterLongT,"Right",colourChoice="Topic",
                 titleText="Posterior belief correlations: ")

p

posterior_belief_correlations_topic_right_file <- here(figures_files_mastodon_dir, "posterior_belief_correlations_topic_right.png")
ggsave(filename = posterior_belief_correlations_topic_right_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

beforeLongT <- postLong %>% 
  filter(TimePoint=="Before" & Condition=="Left")
afterLongT <- postLong %>% 
  filter(TimePoint=="After" & Condition=="Left")

p <- plotCluster(beforeLongT,"Left",colourChoice="Topic",
                 titleText="Prior belief correlations: ")

p

prior_belief_correlations_topic_left_file <- here(figures_files_mastodon_dir, "prior_belief_correlations_topic_left.png")
ggsave(filename = prior_belief_correlations_topic_left_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

p <- plotCluster(afterLongT,"Left",colourChoice="Topic",
                 titleText="Posterior belief correlations: ")

p

posterior_belief_correlations_topic_left_file <- here(figures_files_mastodon_dir, "posterior_belief_correlations_topic_left.png")
ggsave(filename = posterior_belief_correlations_topic_left_file,
       plot=p,device="png",
       width=25,height=15, units="cm")

```


### Individual beliefs

For each individual, we can calculate a measure of how "extreme" they are. For this we exclude the four "neutral" topics. The others are recoded so that they are given 0 if their belief was 50, -50 if their belief was all the way to the "left" end, and 50 if their belief was all the way to the "right" end. Pscore is just the average of this (further from 0 indicates more extreme).

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
ds$Condition <- factor(ds$Condition, levels=c("Left","Control","Right"))
ds$TimePoint <- factor(ds$TimePoint, levels=c("Before","After"))
ds$pScore <- as.numeric(ds$mnBelief)-50

p <- ds %>%
  filter(Topic=="Total") %>%
  ggplot(mapping=aes(x = TimePoint, y=pScore, 
                     fill=Condition)) +
  stat_halfeye(aes(fill=Condition),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  facet_wrap(~Condition,ncol=3) +
  coord_flip() +  
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalCond) +
  scale_colour_manual(values=myPalCond) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-50,-25,0,25,50),limits=c(-52,52)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "Belief polarity by condition", 
       y="Polarity score pScore (higher = more right)",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_by_condition_file <- here(figures_files_mastodon_dir, "pscore_by_condition.png")
ggsave(filename = pscore_by_condition_file,
       plot=p,device="png",
       width=15,height=8, units="cm")

```

Same thing but viewed by topic.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
p <- ds %>%
  filter(Topic=="Trans" | Topic=="AI" | Topic=="Israel" |
           Topic=="Climate") %>%
  filter(Condition=="Control") %>%
  ggplot(mapping=aes(x = TimePoint, y=pScore, 
                     fill=Topic)) +
  stat_halfeye(aes(fill=Topic),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  coord_flip() +  
  facet_wrap(~Topic,ncol=4) +
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalTopic) +
  scale_colour_manual(values=myPalTopic) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-50,-25,0,25,50),limits=c(-52,52)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "Belief polarity by topic: Control condition", 
       y="Polarity score pScore (higher = more right)",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_by_topic_control_file <- here(figures_files_mastodon_dir, "pscore_by_topic_control.png")
ggsave(filename = pscore_by_topic_control_file,
       plot=p,device="png",
       width=15,height=8, units="cm")

p <- ds %>%
  filter(Topic=="Trans" | Topic=="AI" | Topic=="Israel" |
           Topic=="Climate") %>%
  filter(Condition=="Right") %>%
  ggplot(mapping=aes(x = TimePoint, y=pScore, 
                     fill=Topic)) +
  stat_halfeye(aes(fill=Topic),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  coord_flip() +  
  facet_wrap(~Topic,ncol=4) +
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalTopic) +
  scale_colour_manual(values=myPalTopic) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-50,-25,0,25,50),limits=c(-52,52)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "Belief polarity by topic: Right condition", 
       y="Polarity score pScore (higher = more right)",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_by_topic_right_file <- here(figures_files_mastodon_dir, "pscore_by_topic_right.png")
ggsave(filename = pscore_by_topic_right_file,
       plot=p,device="png",
       width=15,height=8, units="cm")

p <- ds %>%
  filter(Topic=="Trans" | Topic=="AI" | Topic=="Israel" |
           Topic=="Climate") %>%
  filter(Condition=="Left") %>%
  ggplot(mapping=aes(x = TimePoint, y=pScore, 
                     fill=Topic)) +
  stat_halfeye(aes(fill=Topic),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  coord_flip() +  
  facet_wrap(~Topic,ncol=4) +
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalTopic) +
  scale_colour_manual(values=myPalTopic) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-50,-25,0,25,50),limits=c(-52,52)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "Belief polarity by topic: Left condition", 
       y="Polarity score pScore (higher = more right)",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_by_topic_left_file <- here(figures_files_mastodon_dir, "pscore_by_topic_left.png")
ggsave(filename = pscore_by_topic_left_file,
       plot=p,device="png",
       width=15,height=8, units="cm")
```

### Individual changes in pScore

We calculate *pScoreDiff* which is abs(afterPScore) - abs(BeforePScore). The larger it is the more people have changed their views in the direction they already were. Smaller indicates that they changed them away from the direction they already were.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
ds_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnBelief) %>%
  pivot_wider(names_from=TimePoint,values_from=mnBelief) %>%
  mutate(BeliefChange = abs( as.numeric(After)-50) - abs(as.numeric(Before)-50))

p <- ds_change %>%
  filter(Topic=="Total" | Topic=="Trans" | Topic=="Israel" |
           Topic=="AI" | Topic=="Climate") %>%
  ggplot(mapping=aes(x = Condition, y=BeliefChange, 
                     fill=Topic)) +
  stat_halfeye(aes(fill=Topic),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  facet_wrap(~Topic,ncol=5) +
  coord_flip() +  
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalTopic) +
  scale_colour_manual(values=myPalTopic) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-25,0,25),limits=c(-27,27)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "pScoreDiff by topic and condition", 
       y="Positive is a shift in the direction they already were",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_diff_by_condition_file <- here(figures_files_mastodon_dir, "pscore_diff_by_condition.png")
ggsave(filename = pscore_diff_by_condition_file,
       plot=p,device="png",
       width=20,height=8, units="cm")

```


We calculate *BeliefChange* which is afterPScore - beforePScore. If it is positive that indicates they've shifted rightward.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
ds_change <- ds %>%
  select(Subject,Condition,TimePoint,Topic,mnBelief) %>%
  pivot_wider(names_from=TimePoint,values_from=mnBelief) %>%
  mutate(BeliefChange = as.numeric(After)-as.numeric(Before))

p <- ds_change %>%
  filter(Topic=="Total" | Topic=="Trans" | Topic=="Israel" |
           Topic=="AI" | Topic=="Climate") %>%
  ggplot(mapping=aes(x = Condition, y=BeliefChange, 
                     fill=Topic)) +
  stat_halfeye(aes(fill=Topic),adjust = .5, width = .5, .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.5, justification=-0.25,
               point_interval = "mean_qi") +
  geom_jitter(aes(fill=Subject,colour=Subject),alpha = .5, 
              width=0.05, show.legend=FALSE) +
  facet_wrap(~Topic,ncol=5) +
  coord_flip() +  
  scale_x_discrete(limits = rev, expand=expansion(add=c(0.2,0))) +
  scale_fill_manual(values=myPalTopic) +
  scale_colour_manual(values=myPalTopic) +
  theme_bw() +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(breaks=c(-25,0,25),limits=c(-27,27)) +
  geom_hline(yintercept=0,colour="black",size=0.3,linetype="dashed") +
  labs(title = "Change in polarity score by topic and condition", 
       y="Positive is a shift to more rightward views",
       subtitle = "Each dot is one person") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.title.y = element_blank())
p

pscore_change_by_condition_file <- here(figures_files_mastodon_dir, "pscore_change_by_condition.png")
ggsave(filename = pscore_change_by_condition_file,
       plot=p,device="png",
       width=20,height=8, units="cm")

```

