---
title: "Magpie Figures"
output: html_document
---

# Overall run

This contains a bunch of figures and statistics about the August 2024 Magpie run. We start by loading the data and doing some basic cleaning.

```{r echo = FALSE, warning=FALSE, message=FALSE}
rm(list=ls())

# load the packages
library(here)
library(tidyverse)
library(Polychrome)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggdist)
library(ggridges)
source(here("R/visualise/supplementaryFunctions.R"))

# Define subfolders
processed_files_mastodon_dir <- "data/mastodon/files/processed"
figures_files_mastodon_dir <- "data/mastodon/files/figures"
all_char_cols <- cols(.default = "c")
DRY_RUN <- FALSE
```

```{r echo = FALSE, warning=FALSE, message=FALSE}
# set the colours
polarityColours <- c("left"="#3399CC","na"="#9999FF","right"="#CC0066")
politicalIDColours <- c("democrat"="#3399CC","independent"="#9999FF",
                     "republican"="#CC0066")
partyColours <- c("Democrats"="#3399CC","Republicans"="#CC0066")

trustColours <- c("#00AA11","#BB0000")

topicColours <- c("Trans"="#AA3399","Gender"="#FF99FF",
                  "Climate"="#00AA66","Environment"="#88EE22",
                  "AI"="#0066CC","SciTech"="#99CCFF",
                  "Israel"="#CC9900","Foreign"="#FFCC33",
                  "MoneyEcon" = "#555555", "CrimeGuns"="#888888",
                  "Religion" = "#AAAAAA", "Health"="#CCCCCC",
                  "Fun"="#9999FF","Total"="#CC0000")

conditionColours <- c("Left"="#99CCFF",
                      "Control"="#339933","Right"="#FF99CC")

politicalIDColours <- c("democrat"="#3399CC","independent"="#9999FF",
                     "republican"="#CC0066")

ttColours <- c("#00AA11","#CCCC33","#CC9933","#BB0000")

entityColours <- c("People"="#9966FF","Universities"="#3399FF",
                "Media"="#66CC33","Government"="#FFFF00",
                "Business"="#FF9900","Overall"="#AA0000")


# read all of the long files
dcb <- read_csv(here(processed_files_mastodon_dir, "control", "data_before_all.csv"),
                col_types = all_char_cols)
dca <- read_csv(here(processed_files_mastodon_dir, "control", "data_after_all.csv"),
                col_types = all_char_cols)
drb <- read_csv(here(processed_files_mastodon_dir, "right", "data_before_all.csv"),
                col_types = all_char_cols)
dra <- read_csv(here(processed_files_mastodon_dir, "right", "data_after_all.csv"),
                col_types = all_char_cols)
dlb <- read_csv(here(processed_files_mastodon_dir, "left", "data_before_all.csv"),
                col_types = all_char_cols)
dla <- read_csv(here(processed_files_mastodon_dir, "left", "data_after_all.csv"),
                col_types = all_char_cols)

# remove the people who did not complete the After survey
# save them in a file in case need to look at later
dc_first <- dcb[!(dcb$Subject %in% dca$Subject),]
dr_first <- drb[!(drb$Subject %in% dra$Subject),]
dl_first <- dlb[!(dlb$Subject %in% dla$Subject),]
da_first <- rbind(dc_first,dr_first,dl_first)

all_first_file <- here(processed_files_mastodon_dir, "combined", 
                          "firstonly", "all.csv")
da_first %>% save_processed_file(file = all_first_file)

dc_before <- dcb[dcb$Subject %in% dca$Subject,]
dc_after <- dca[dca$Subject %in% dcb$Subject,]
dr_before <- drb[drb$Subject %in% dra$Subject,]
dr_after <- dra[dra$Subject %in% drb$Subject,]
dl_before <- dlb[dlb$Subject %in% dla$Subject,]
dl_after <- dla[dla$Subject %in% dlb$Subject,]

d_before <- rbind(dc_before,dr_before,dl_before)
d_after <- rbind(dc_after,dr_after,dl_after)
d_after$TimePoint <- "After"
# save combined file
before_file <- here(processed_files_mastodon_dir, "combined", "before.csv")
d_before %>% save_processed_file(file = before_file)

after_file <- here(processed_files_mastodon_dir, "combined", "after.csv")
d_after %>% save_processed_file(file = after_file)

```

In the **Control** condition, `r length(unique(dcb$Subject))` took the Before survey and `r length(unique(dca$Subject))` took the After survey.

In the **Right** condition, `r length(unique(drb$Subject))` took the Before survey and `r length(unique(dra$Subject))` took the After survey.

In the **Left** condition, `r length(unique(dlb$Subject))` took the Before survey and `r length(unique(dla$Subject))` took the After survey.

All analyses here consider only the people who took both surveys, i.e., `r length(unique(dc_after$Subject))` in the **Control** condition, `r length(unique(dr_after$Subject))` in the **Right** condition, and `r length(unique(dl_after$Subject))` in the **Left** condition. 

```{r echo = FALSE, warning=FALSE, message=FALSE}

# set factor levels to be nice
d_before$Condition <- factor(d_before$Condition,
                             levels=c("Left","Control","Right"))
d_after$Condition <- factor(d_after$Condition,
                             levels=c("Left","Control","Right"))
d_before$TimePoint <- factor(d_before$TimePoint,
                             levels=c("Before","After"))
d_after$TimePoint <- factor(d_after$TimePoint,
                             levels=c("Before","After"))

# demographic variables
d_before$Gender <- factor(d_before$Gender, 
                    levels = c("male","female","nbqueer","other"))
d_before$Sex <- factor(d_before$Sex, 
                       levels = c("male","female","other"))
d_before$Trans <- factor(d_before$Trans, 
                         levels = c("yes","no"))
d_before$LGBT <- factor(d_before$LGBT, 
                        levels = c("yes","no"))
d_before$English <- factor(d_before$English, 
                           levels = c("native","good","poor"))
d_before$Race <- factor(d_before$Race, 
                        levels = c("white","black","hispanic",
                                     "asian","indian","mideast",
                                     "multracial","other"))
d_before$Education <- factor(d_before$Education, 
                       levels = c("highschool","somecollege",
                                  "undergrad","postgrad"))
d_before$Religion <- factor(d_before$Religion,
                      levels=c("christian","mormon","jewish",
                               "eastern","muslim","other","none"))
d_before$PoliticalID <- factor(d_before$PoliticalID,
                      levels=c("democrat","independent","republican"))

d_after <- d_after %>% 
  mutate(across(-c(Subject,UserName,Condition,TimePoint), as.numeric))

cols_to_exclude <- c(
  # Identifiers
  "Subject", "UserName",
  
  # Encoded already or properly typed
  "Condition", "TimePoint", "Sex", "Gender", "Trans", "LGBT",
  "English", "Education", "Race", "Religion", "PoliticalID",
  "PoliticalIDNum",  # could be numeric-looking but might include labels
  
  # Lat/Lon can stay character if they contain non-numeric values or missing formats
  "LAT", "LON"
)

d_before <- d_before %>%
  mutate(across(
    .cols = -all_of(cols_to_exclude),
    .fns = as.numeric
  ))

```

## Demographics

Let's look at some basic demographics first.


### Gender

Overall there were `r table(d_before$Gender)[[1]]` (`r round(100*table(d_before$Gender)[[1]]/sum(table(d_before$Gender)))`%) males, `r table(d_before$Gender)[[2]]` (`r round(100*table(d_before$Gender)[[2]]/sum(table(d_before$Gender)))`%) females, `r table(d_before$Gender)[[3]]` (`r round(100*table(d_before$Gender)[[3]]/sum(table(d_before$Gender)))`%) non-binary people, and `r table(d_before$Gender)[[4]]` (`r round(100*table(d_before$Gender)[[4]]/sum(table(d_before$Gender)))`%) other.

In the **Control** condition there were `r table(d_before$Gender,d_before$Condition)[[5]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[5]]/sum(table(d_before$Gender[d_before$Condition=="Control"])))`%)
males, `r table(d_before$Gender,d_before$Condition)[[6]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[6]]/sum(table(d_before$Gender[d_before$Condition=="Control"])))`%) females, `r table(d_before$Gender,d_before$Condition)[[7]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[7]]/sum(table(d_before$Gender[d_before$Condition=="Control"])))`%) non-binary people, and `r table(d_before$Gender,d_before$Condition)[[8]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[8]]/sum(table(d_before$Gender[d_before$Condition=="Control"])))`%) other.

In the **Left** condition there were `r table(d_before$Gender,d_before$Condition)[[1]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[1]]/sum(table(d_before$Gender[d_before$Condition=="Left"])))`%)
males, `r table(d_before$Gender,d_before$Condition)[[2]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[2]]/sum(table(d_before$Gender[d_before$Condition=="Left"])))`%) females, `r table(d_before$Gender,d_before$Condition)[[3]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[3]]/sum(table(d_before$Gender[d_before$Condition=="Left"])))`%) non-binary people, and `r table(d_before$Gender,d_before$Condition)[[4]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[4]]/sum(table(d_before$Gender[d_before$Condition=="Left"])))`%) other.

In the **Right** condition there were `r table(d_before$Gender,d_before$Condition)[[9]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[9]]/sum(table(d_before$Gender[d_before$Condition=="Right"])))`%)
males, `r table(d_before$Gender,d_before$Condition)[[10]]` (`r round(100*table(d_before$Gender,d_before$Condition)[[10]]/sum(table(d_before$Gender[d_before$Condition=="Right"])))`%) females, `r table(d_before$Gender,d_before$Condition)[[11]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[11]]/sum(table(d_before$Gender[d_before$Condition=="Right"])))`%) non-binary people, and `r table(d_before$Gender,d_before$Condition)[[12]]` 
(`r round(100*table(d_before$Gender,d_before$Condition)[[12]]/sum(table(d_before$Gender[d_before$Condition=="Right"])))`%) other.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
d_before$Condition <- factor(d_before$Condition, 
                             levels=c("Right","Control","Left"))

myTable <- d_before %>%
  group_by(Condition,Gender) %>%
  summarise(Number = n()) %>%
  ungroup() %>%
  filter(!is.na(Gender))

p <- myTable %>%
  ggplot(mapping=aes(y=Condition,x=Number,fill=Gender)) +
  geom_col(position=position_stack(),colour="black") +
  theme_bw() +
  theme(axis.text.y = element_text(angle = 90, size=10),
        axis.ticks.y = element_blank(), axis.ticks.x = element_blank(),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=c("#66CCFF","#FF99FF","#FFFF33","#BBBBBB")) +
  labs(title = "Gender breakdown by condition") 

p

gender_breakdown_file <- here(figures_files_mastodon_dir, "gender_breakdown.png")
ggsave(filename = gender_breakdown_file,
       plot=p,device="png",
       width=12,height=8, units="cm")
```

### Locations of people in all conditions

Now we can look at where people come from. Let's use latitude and longitude for that as it is more exact (I rounded them to the closest whole number so as to keep people anonymous, so this gives their location within about a 60 mile square). 

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=5}
d_before$Condition <- factor(d_before$Condition, 
                             levels=c("Left","Control","Right"))
dtemp <- d_before
world <- ne_countries(scale = "medium", returnclass = "sf")
d_sf <- st_as_sf(dtemp, coords = c('LON', 'LAT'))

p <- d_sf %>% 
  st_set_crs(4326) %>%
  ggplot() +
    theme_bw() +
    geom_sf(data=world,show.legend=FALSE,
            colour="darkgrey",fill="white") +
    geom_sf(aes(color = PoliticalID),
            alpha=0.7,show.legend=FALSE,size=1.5) +
    coord_sf(xlim = c(-140,-50), ylim = c(10,60)) +
    scale_fill_manual(values=politicalIDColours) +
    scale_colour_manual(values=politicalIDColours) +
    facet_wrap(~Condition,ncol=3) +
    theme(strip.background = element_rect(colour = "black", fill = "white")) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(), axis.ticks.x= element_blank())

p

location_by_condition_file <- here(figures_files_mastodon_dir, "location_by_condition.png")
ggsave(filename = location_by_condition_file,
       plot=p,device="png",
       width=24,height=8, units="cm")

d_before$Condition <- factor(d_before$Condition, 
                             levels=c("Right","Control","Left"))
```

### Age 

Let's look at the distribution over ages in different conditions. The mean age overall was `r round(mean(d_before$Age,na.rm=TRUE),1)` with a standard deviation of `r round(sd(d_before$Age,na.rm=TRUE),1)`. The maximum age was `r max(d_before$Age,na.rm=TRUE)` and the minimum was `r min(d_before$Age,na.rm=TRUE)`.

The mean age in the **Control** condition was `r round(mean(d_before$Age[d_before$Condition=="Control"],na.rm=TRUE),1)` with a standard deviation of `r round(sd(d_before$Age[d_before$Condition=="Control"],na.rm=TRUE),1)`. The maximum age was `r max(d_before$Age[d_before$Condition=="Control"],na.rm=TRUE)` and the minimum was `r min(d_before$Age[d_before$Condition=="Control"],na.rm=TRUE)`.

The mean age in the **Right** condition was `r round(mean(d_before$Age[d_before$Condition=="Right"],na.rm=TRUE),1)` with a standard deviation of `r round(sd(d_before$Age[d_before$Condition=="Right"],na.rm=TRUE),1)`. The maximum age was `r max(d_before$Age[d_before$Condition=="Right"],na.rm=TRUE)` and the minimum was `r min(d_before$Age[d_before$Condition=="Right"],na.rm=TRUE)`.

The mean age in the **Left** condition was `r round(mean(d_before$Age[d_before$Condition=="Left"],na.rm=TRUE),1)` with a standard deviation of `r round(sd(d_before$Age[d_before$Condition=="Left"],na.rm=TRUE),1)`. The maximum age was `r max(d_before$Age[d_before$Condition=="Left"],na.rm=TRUE)` and the minimum was `r min(d_before$Age[d_before$Condition=="Left"],na.rm=TRUE)`.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
maxAge <- max(as.numeric(d_before$Age),na.rm=TRUE)

p <- d_before %>%
  ggplot(mapping=aes(x = Condition, y=as.numeric(Age),fill=Condition)) +
  stat_halfeye(aes(fill=Condition),adjust = .5, width = .5, 
               .width = c(0.5, 1),
               show.legend=FALSE, alpha=0.8, justification=-0.35,
               point_interval = "mean_qi") +
  geom_boxplot(width = .1, outlier.shape = NA,fill=NA,
               colour="black",show.legend=FALSE) +
  geom_jitter(aes(fill=Condition,colour=Condition),alpha = .6, 
              width=0.1, height=0.05, show.legend=FALSE) +
  coord_flip() +  
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme_bw() +
  #facet_wrap(~Condition,ncol=2) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_continuous(limits=c(15,maxAge+5)) +
  labs(title = "Age differences by condition", 
       y="Reported age in years") +
  theme(axis.text.y = element_text(angle = 90, hjust=0.3, size=10),
        axis.ticks.y = element_blank(), axis.ticks.x = element_blank(),
        axis.title.y = element_blank())

p

age_by_condition_file <- here(figures_files_mastodon_dir, "age_by_condition.png")
ggsave(filename = age_by_condition_file,
       plot=p,device="png",
       width=15,height=8, units="cm")

```


### Education

Breakdown of education of participants, using the four broad categories.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
myTable <- d_before %>%
  group_by(Condition,Education) %>%
  summarise(Number = n()) %>%
  ungroup() %>%
  filter(!is.na(Education))

p <- myTable %>%
  ggplot(mapping=aes(y=Condition,x=Number,fill=Education)) +
  geom_col(position=position_stack(reverse = TRUE),colour="black") +
  theme_bw() +
  theme(axis.text.y = element_text(angle = 90, size=10),
        axis.ticks.y = element_blank(), axis.ticks.x = element_blank(),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_brewer(palette="Blues",direction=-1) +
  labs(title = "Education breakdown by condition") 

p

education_breakdown_file <- here(figures_files_mastodon_dir, "education_breakdown.png")
ggsave(filename = education_breakdown_file,
       plot=p,device="png",
       width=12,height=8, units="cm")
```

## Beliefs

### Beliefs by topic

We can visualise beliefs by topic at both Before and After. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
d_before$Condition <- factor(d_before$Condition, 
                             levels=c("Left","Control","Right"))

# first we need to construct our datasets
dbB <- d_before %>%
  select(Subject,UserName,Condition,TimePoint,
         Belief,BeliefAI,BeliefClimate,BeliefIsrael,BeliefTrans,
         ExtremeBelief,ExtremeBeliefAI,ExtremeBeliefClimate,
         ExtremeBeliefIsrael,ExtremeBeliefTrans)
dbA <- d_after %>%
  select(Subject,UserName,Condition,TimePoint,
         Belief,BeliefAI,BeliefClimate,BeliefIsrael,BeliefTrans,
         ExtremeBelief,ExtremeBeliefAI,ExtremeBeliefClimate,
         ExtremeBeliefIsrael,ExtremeBeliefTrans)
db <- rbind(dbB,dbA)

conds <- db %>% filter(TimePoint=="After") %>%
  select(Subject,Condition)

# construct the wide dataset
db_wide <- db %>% 
  select(Subject,TimePoint,Belief,BeliefAI,BeliefIsrael,
         BeliefClimate,BeliefTrans) %>%
  pivot_longer(cols=-c(Subject,TimePoint), names_to="Topic",
               values_to="Beliefs") %>%
  mutate(Topic = case_when(
    Topic=="Belief"~"Total",
    Topic=="BeliefAI"~"AI",
    Topic=="BeliefIsrael"~"Israel",
    Topic=="BeliefTrans"~"Trans",
    Topic=="BeliefClimate"~"Climate")) %>%
  left_join(conds,by="Subject")

# put it in a nice order for visualisation
db_wide <- db_wide %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Climate"~2,
                           Topic=="AI"~3,Topic=="Israel"~4,
                           Topic=="Total"~5))

# calculate means for bars for visualisation
beliefMeans <- db_wide %>%
    group_by(Condition,TimePoint,Topic,Order) %>%
    summarise(muAll = mean(as.numeric(Beliefs),na.rm=TRUE),
              sdAll = sd(as.numeric(Beliefs),na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

# put everything in the right order
postLong <- db_wide %>%
  left_join(beliefMeans,by=join_by(Condition,TimePoint,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of beliefs
p <- beliefMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
    geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=db_wide,
              mapping=aes(y=as.numeric(Beliefs),x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=50,linetype=2) +
  ylim(0,100) +
  facet_grid(TimePoint~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_y_continuous(breaks=c(10,50,95),labels=c("left","mid","right")) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Overall beliefs by topic",
       subtitle = "Each dot is one person",
       y = "Belief rating") +
  theme(axis.text.x = element_text(size=10), #, angle=45, vjust=0.5),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
p

topic_key_bars_vertical_file <- here(figures_files_mastodon_dir, "topic_key_bars_vertical.png")
ggsave(filename = topic_key_bars_vertical_file,
       plot=p,device="png",
       width=20,height=14, units="cm")

```

### Belief change by topic

We can visualise how beliefs change by topic. First we need to construct the right datasets out of our main one, and then create the figure.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# construct the belief change dataset
beliefChange <- db %>% 
  select(Subject,TimePoint,Belief) %>%
  mutate(Belief=as.numeric(Belief)) %>% 
  pivot_wider(names_from="TimePoint",values_from="Belief") %>%
  mutate(BeliefChange = After-Before) %>%
  select(-c(After,Before))
beliefAIChange <- db %>% 
  select(Subject,TimePoint,BeliefAI) %>%
  mutate(BeliefAI=as.numeric(BeliefAI)) %>% 
  pivot_wider(names_from="TimePoint",values_from="BeliefAI") %>%
  mutate(BeliefAIChange = After-Before) %>%
  select(-c(After,Before))
beliefTransChange <- db %>% 
  select(Subject,TimePoint,BeliefTrans) %>%
  mutate(BeliefTrans=as.numeric(BeliefTrans)) %>% 
  pivot_wider(names_from="TimePoint",values_from="BeliefTrans") %>%
  mutate(BeliefTransChange = After-Before) %>%
  select(-c(After,Before))
beliefClimateChange <- db %>% 
  select(Subject,TimePoint,BeliefClimate) %>%
  mutate(BeliefClimate=as.numeric(BeliefClimate)) %>% 
  pivot_wider(names_from="TimePoint",values_from="BeliefClimate") %>%
  mutate(BeliefClimateChange = After-Before) %>%
  select(-c(After,Before))
beliefIsraelChange <- db %>% 
  select(Subject,TimePoint,BeliefIsrael) %>%
  mutate(BeliefIsrael=as.numeric(BeliefIsrael)) %>% 
  pivot_wider(names_from="TimePoint",values_from="BeliefIsrael") %>%
  mutate(BeliefIsraelChange = After-Before) %>%
  select(-c(After,Before))

dBC <- beliefChange %>%
  left_join(beliefAIChange,by="Subject") %>%
  left_join(beliefTransChange,by="Subject") %>%
  left_join(beliefClimateChange,by="Subject") %>%
  left_join(beliefIsraelChange,by="Subject") %>%
  pivot_longer(cols=-c(Subject),names_to="Topic",
               values_to="BeliefChange") %>%
  mutate(Topic = case_when(
    Topic=="BeliefChange"~"Total",
    Topic=="BeliefAIChange"~"AI",
    Topic=="BeliefIsraelChange"~"Israel",
    Topic=="BeliefTransChange"~"Trans",
    Topic=="BeliefClimateChange"~"Climate")) %>%
  left_join(conds,by="Subject")

# remove things to keep it tidy
rm(beliefChange,beliefAIChange,beliefClimateChange,
   beliefTransChange,beliefIsraelChange)

# put it in a nice order for visualisation
dBC <- dBC %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Climate"~2,
                           Topic=="AI"~3,Topic=="Israel"~4,
                           Topic=="Total"~5))

# calculate means for bars for visualisation
beliefMeans <- dBC %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

# put everything in the right order
postLong <- dBC %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of beliefs
p <- beliefMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
    geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=postLong,
              mapping=aes(y=BeliefChange,x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  ylim(-10,10) +
  facet_wrap(~Topic,ncol=5) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief change by topic",
       subtitle = "Each dot is one person",
       y = "Belief change (higher = right shift)") +
  theme(axis.text.x = element_text(size=10), #, angle=45, vjust=0.5),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

topic_key_bars_change_vertical_file <- here(figures_files_mastodon_dir, "topic_key_bars_change_vertical.png")
ggsave(filename = topic_key_bars_change_vertical_file,
       plot=p,device="png",
       width=20,height=8, units="cm")

```

### Extremeness of belief change by topic

Same idea as before, except this time we're plotting whether beliefs are shifting to be more extreme than before.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# construct the extreme belief change dataset
beliefChange <- db %>% 
  select(Subject,TimePoint,ExtremeBelief) %>%
  mutate(ExtremeBelief=as.numeric(ExtremeBelief)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ExtremeBelief") %>%
  mutate(BeliefChange = After-Before) %>%
  select(-c(After,Before))
beliefAIChange <- db %>% 
  select(Subject,TimePoint,ExtremeBeliefAI) %>%
  mutate(ExtremeBeliefAI=as.numeric(ExtremeBeliefAI)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ExtremeBeliefAI") %>%
  mutate(BeliefAIChange = After-Before) %>%
  select(-c(After,Before))
beliefTransChange <- db %>% 
  select(Subject,TimePoint,ExtremeBeliefTrans) %>%
  mutate(ExtremeBeliefTrans=as.numeric(ExtremeBeliefTrans)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ExtremeBeliefTrans") %>%
  mutate(BeliefTransChange = After-Before) %>%
  select(-c(After,Before))
beliefClimateChange <- db %>% 
  select(Subject,TimePoint,ExtremeBeliefClimate) %>%
  mutate(ExtremeBeliefClimate=as.numeric(ExtremeBeliefClimate)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ExtremeBeliefClimate") %>%
  mutate(BeliefClimateChange = After-Before) %>%
  select(-c(After,Before))
beliefIsraelChange <- db %>% 
  select(Subject,TimePoint,ExtremeBeliefIsrael) %>%
  mutate(ExtremeBeliefIsrael=as.numeric(ExtremeBeliefIsrael)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ExtremeBeliefIsrael") %>%
  mutate(BeliefIsraelChange = After-Before) %>%
  select(-c(After,Before))

dBE <- beliefChange %>%
  left_join(beliefAIChange,by="Subject") %>%
  left_join(beliefTransChange,by="Subject") %>%
  left_join(beliefClimateChange,by="Subject") %>%
  left_join(beliefIsraelChange,by="Subject") %>%
  pivot_longer(cols=-c(Subject),names_to="Topic",
               values_to="BeliefChange") %>%
  mutate(Topic = case_when(
    Topic=="BeliefChange"~"Total",
    Topic=="BeliefAIChange"~"AI",
    Topic=="BeliefIsraelChange"~"Israel",
    Topic=="BeliefTransChange"~"Trans",
    Topic=="BeliefClimateChange"~"Climate")) %>%
  left_join(conds,by="Subject")

# remove things to keep it tidy
rm(beliefChange,beliefAIChange,beliefClimateChange,
   beliefTransChange,beliefIsraelChange)

# put it in a nice order for visualisation
dBE <- dBE %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Climate"~2,
                           Topic=="AI"~3,Topic=="Israel"~4,
                           Topic=="Total"~5))

# calculate means for bars for visualisation
beliefMeans <- dBE %>%
    group_by(Condition,Topic,Order) %>%
    summarise(muAll = mean(BeliefChange,na.rm=TRUE),
              sdAll = sd(BeliefChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(beliefMeans$Topic,
                                 beliefMeans$Order))

# put everything in the right order
postLong <- dBE %>%
  left_join(beliefMeans,by=join_by(Condition,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
beliefMeans <- beliefMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of beliefs
p <- beliefMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
    geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=postLong,
              mapping=aes(y=BeliefChange,x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  ylim(-30,30) +
  facet_wrap(~Topic,ncol=5) +
    scale_fill_manual(values=topicColours) +
    scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
    labs(title = "Change in extremeness of belief",
       subtitle = "Each dot is one person",
       y = "Belief change (higher = more extreme)") +
  theme(axis.text.x = element_text(size=10), #, angle=45, vjust=0.5),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

topic_extreme_key_bars_change_vertical_file <- here(figures_files_mastodon_dir, "topic_extreme_key_bars_change_vertical.png")
ggsave(filename = topic_extreme_key_bars_change_vertical_file,
       plot=p,device="png",
       width=20,height=10, units="cm")

```

# Relationship between beliefs and extremeness of beliefs

```{r echo=FALSE, message=FALSE, warning=FALSE}
# create dataset to compare prior beliefs to belief change
dbr <- db_wide %>%
  left_join(dBC,by=c("Subject","Topic","Condition","Order")) %>%
  filter(TimePoint=="Before")

# create plot of relative positioning
p <- dbr %>%
  mutate(Beliefs=as.numeric(Beliefs), BeliefChange=as.numeric(BeliefChange)) %>% 
  ggplot(mapping=aes(x=Beliefs,y=BeliefChange,fill=Topic,colour=Topic)) +
  geom_hline(yintercept=0,linetype=3) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.3,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  ylim(-50,50) +
  xlim(0,100) +
  #scale_y_continuous(breaks=c(-50,0,50)) +
  #scale_x_continuous(breaks=c(0,50,100)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and belief change",
       subtitle = "Each dot is one person",
       x = "Initial beliefs (low=left)",
       y = "Belief change (negative = more left)") +
  theme(#axis.text.x = element_text(size=8),
        #axis.text.y = element_text(size=8, angle=90),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_blank(), axis.text.y = element_blank())
  
p

priors_beliefchange_scatterplot_file <- here(figures_files_mastodon_dir, "priors_beliefchange_scatterplot.png")
ggsave(filename = priors_beliefchange_scatterplot_file,
       plot=p,device="png",
       width=20,height=14, units="cm")
```

### Relative politics

Let's look at answers to the ``where do you place yourself politically relative to everyone else'' question, both before and after. Answers were from 0-100 where 0=left and 100=right.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# first we need to construct our datasets
dpB <- d_before %>%
  select(Subject,UserName,Condition,TimePoint,
         RelativePolitics,RelativeAI,RelativeClimate,RelativeTrans,
         RelativeIsrael,ConsensusPolitics,ConsensusAI,
         ConsensusClimate,ConsensusTrans,ConsensusIsrael)
dpA <- d_after %>%
  select(Subject,UserName,Condition,TimePoint,
         RelativePolitics,RelativeAI,RelativeClimate,RelativeTrans,
         RelativeIsrael,ConsensusPolitics,ConsensusAI,
         ConsensusClimate,ConsensusTrans,ConsensusIsrael)
dp <- rbind(dpB,dpA)

conds <- dp %>% filter(TimePoint=="After") %>%
  select(Subject,Condition)


# construct the wide dataset
dp_wide <- dp %>% 
  select(Subject,TimePoint,RelativePolitics,RelativeAI,
         RelativeClimate,RelativeTrans,RelativeIsrael) %>%
  pivot_longer(cols=-c(Subject,TimePoint),names_to="Topic",
               values_to="Relative") %>%
  mutate(Topic = case_when(
    Topic=="RelativePolitics"~"Total",
    Topic=="RelativeAI"~"AI",
    Topic=="RelativeIsrael"~"Israel",
    Topic=="RelativeTrans"~"Trans",
    Topic=="RelativeClimate"~"Climate")) %>%
  left_join(conds,by="Subject")

# put it in a nice order for visualisation
dp_wide <- dp_wide %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Climate"~2,
                           Topic=="AI"~3,Topic=="Israel"~4,
                           Topic=="Total"~5))

# calculate means for bars for visualisation
relativeMeans <- dp_wide %>%
    group_by(Condition,TimePoint,Topic,Order) %>%
    summarise(muAll = mean(Relative,na.rm=TRUE),
              sdAll = sd(Relative,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(relativeMeans$Topic,
                                 relativeMeans$Order))

# put everything in the right order
postLong <- dp_wide %>%
  left_join(relativeMeans,by=join_by(Condition,TimePoint,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
relativeMeans <- relativeMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of relative positioning
p <- relativeMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=dp_wide,
              mapping=aes(y=as.numeric(Relative),x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=50,linetype=2) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,50,95),labels=c("left","mid","right")) +
  facet_grid(TimePoint~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Relative political positioning",
       subtitle = "Each dot is one person",
       y = "Relative positioning") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank())
  
p

relative_politics_key_bars_vertical_file <- here(figures_files_mastodon_dir, "relative_politics_key_bars_vertical.png")
ggsave(filename = relative_politics_key_bars_vertical_file,
       plot=p,device="png",
       width=20,height=14, units="cm")

```

### Consensus perception

Let's look at answers to the ``where do you think the political consensus is'' question, both before and after. Answers were from 0-100 where 0=left and 100=right.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# construct the wide dataset
dc_wide <- dp %>% 
  select(Subject,TimePoint,ConsensusPolitics,ConsensusAI,
         ConsensusClimate,ConsensusTrans,ConsensusIsrael) %>%
  pivot_longer(cols=-c(Subject,TimePoint),names_to="Topic",
               values_to="Consensus") %>%
  mutate(Topic = case_when(
    Topic=="ConsensusPolitics"~"Total",
    Topic=="ConsensusAI"~"AI",
    Topic=="ConsensusIsrael"~"Israel",
    Topic=="ConsensusTrans"~"Trans",
    Topic=="ConsensusClimate"~"Climate")) %>%
  left_join(conds,by="Subject") %>% 
  mutate(Consensus=as.numeric(Consensus))

# put it in a nice order for visualisation
dc_wide <- dc_wide %>%
  mutate(Order = case_when(Topic=="Trans"~1, Topic=="Climate"~2,
                           Topic=="AI"~3,Topic=="Israel"~4,
                           Topic=="Total"~5))

# calculate means for bars for visualisation
consensusMeans <- dc_wide %>%
    group_by(Condition,TimePoint,Topic,Order) %>%
    summarise(muAll = mean(Consensus,na.rm=TRUE),
              sdAll = sd(Consensus,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(consensusMeans$Topic,
                                 consensusMeans$Order))

# put everything in the right order
postLong <- dc_wide %>%
  left_join(consensusMeans,by=join_by(Condition,TimePoint,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
consensusMeans <- consensusMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of relative positioning
p <- consensusMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=dc_wide,
              mapping=aes(y=Consensus,x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=50,linetype=2) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,50,95),labels=c("left","mid","right")) +
  facet_grid(TimePoint~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Perception of political consensus",
       subtitle = "Each dot is one person",
       y = "Consensus perception") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

consensus_politics_key_bars_vertical_file <- here(figures_files_mastodon_dir, "consensus_politics_key_bars_vertical.png")
ggsave(filename = consensus_politics_key_bars_vertical_file,
       plot=p,device="png",
       width=20,height=14, units="cm")

```

### Perception relative to consensus

This is their relative judgment minus the consensus judgment. It gives a measure of how far off consensus people think they are, with negative values indicating they think they are left of consensus and positive values indicating they think they are right of consensus.

So if my relative judgment is 30 (indicating I think I'm on the left by 20, since 50 is center) but that I think consensus is at 20 then this value would be 10, indicating that I think I'm to the right of the consensus judgment.

```{r echo=FALSE, message=FALSE, warning=FALSE}
dcr <- dp_wide %>%
  left_join(dc_wide,by=c("Subject","TimePoint","Topic",
                         "Condition","Order")) %>%
  mutate(RCDiff = as.numeric(Relative)-as.numeric(Consensus))


# calculate means for bars for visualisation
rcMeans <- dcr %>%
    group_by(Condition,TimePoint,Topic,Order) %>%
    summarise(muAll = mean(RCDiff,na.rm=TRUE),
              sdAll = sd(RCDiff,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

statementLevels <- levels(reorder(rcMeans$Topic,
                                 rcMeans$Order))

# put everything in the right order
postLong <- dcr %>%
  left_join(rcMeans,by=join_by(Condition,TimePoint,Topic,Order))

postLong <- postLong %>% 
  mutate(Topic = factor(Topic, levels = statementLevels))
rcMeans <- rcMeans %>%
  mutate(Topic = factor(Topic, levels = statementLevels))

# create plot of relative positioning
p <- rcMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Topic)) +
  geom_hline(yintercept=0,linetype=2) +
  geom_jitter(data=dcr,
              mapping=aes(y=RCDiff,x=Condition,colour=Topic),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  ylim(-100,100) +
  scale_y_continuous(breaks=c(-90,0,95),labels=c("left","mid","right")) +
  facet_grid(TimePoint~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Perception of self relative to consensus",
       subtitle = "Each dot is one person",
       y = "Relative politics - Consensus perception") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

self_relative_consensus_key_bars_vertical_file <- here(figures_files_mastodon_dir, "self_relative_consensus_key_bars_vertical.png")
ggsave(filename = self_relative_consensus_key_bars_vertical_file,
       plot=p,device="png",
       width=20,height=14, units="cm")

```

We can also look at this as a scatterplot relating their relative position to what they think the consensus position is. Reflects only After, since we woudln't expect condition differences on Before.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# create plot of relative positioning
p <- dcr %>%
  filter(TimePoint=="After") %>%
  mutate(Consensus=as.numeric(Consensus), Relative=as.numeric(Consensus)) %>% 
  ggplot(mapping=aes(x=Consensus,y=Relative,fill=Topic,colour=Topic)) +
  geom_hline(yintercept=50,linetype=2) +
  geom_vline(xintercept=50,linetype=2) +
  geom_point(alpha=0.3,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  ylim(0,100) +
  xlim(0,100) +
  scale_x_continuous(breaks=c(5,50,95),labels=c("left","mid","right")) +
  scale_y_continuous(breaks=c(5,50,95),labels=c("left","mid","right")) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Perception of self relative to consensus",
       subtitle = "Each dot is one person",
       y = "Relative political perception",
       x = "Consensus perception") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

self_relative_consensus_key_scatterplot_file <- here(figures_files_mastodon_dir, "self_relative_consensus_key_scatterplot.png")
ggsave(filename = self_relative_consensus_key_scatterplot_file,
       plot=p,device="png",
       width=20,height=16, units="cm")

```

## Consensus and relative overall only

Let's make a graph just showing the total, not broken down by topic.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# first we need to construct our datasets
dpB <- d_before %>%
  select(Subject,UserName,Condition,TimePoint,
         RelativePolitics,ConsensusPolitics)
dpA <- d_after %>%
  select(Subject,UserName,Condition,TimePoint,
         RelativePolitics,ConsensusPolitics)
dp <- rbind(dpB,dpA)

conds <- dp %>% filter(TimePoint=="Before") %>%
  select(Subject,Condition)

# construct the wide dataset
dp_wide <- dp %>% 
  select(Subject,TimePoint,ConsensusPolitics) %>%
  left_join(conds,by="Subject") %>% 
  mutate(ConsensusPolitics=as.numeric(ConsensusPolitics))

# calculate means for bars for visualisation
dpMeans <- dp_wide %>%
    group_by(Condition,TimePoint) %>%
    summarise(muAll = mean(ConsensusPolitics,na.rm=TRUE),
              sdAll = sd(ConsensusPolitics,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of relative positioning
p <- dpMeans %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=dp_wide,
              mapping=aes(y=ConsensusPolitics,
                          x=Condition,colour=Condition),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=50,linetype=2) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,98),labels=c("none","full")) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Perceived political consensus (Before)",
       subtitle = "Rating of amount that people in the US generally agree with each other politically",
       y = "Consensus estimate\n") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), 
        axis.ticks.y = element_blank())
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank())
  
p

consensus_totalonly_bars_vertical_file <- here(figures_files_mastodon_dir, "consensus_totalonly_bars_vertical.png")
ggsave(filename = consensus_totalonly_bars_vertical_file,
       plot=p,device="png",
       width=16,height=10, units="cm")

# construct the wide dataset
dp_wide <- dp %>% 
  select(Subject,TimePoint,RelativePolitics) %>%
  left_join(conds,by="Subject") %>% 
  mutate(RelativePolitics=as.numeric(RelativePolitics))

# calculate means for bars for visualisation
dpMeans <- dp_wide %>%
    group_by(Condition,TimePoint) %>%
    summarise(muAll = mean(RelativePolitics,na.rm=TRUE),
              sdAll = sd(RelativePolitics,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of relative positioning
p <- dpMeans %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=dp_wide,
              mapping=aes(y=RelativePolitics,
                          x=Condition,colour=Condition),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=50,linetype=2) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,50,98),labels=c("left","center",
                                                 "right")) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Perceived relative politics (Before)",
       subtitle = "Participant ratings of own beliefs relative to others in US",
       y = "Relative estimate\n") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), 
        axis.ticks.y = element_blank())
        #axis.title.x = element_blank(),
        #axis.title.y = element_blank())
  
p

relative_totalonly_bars_vertical_file <- here(figures_files_mastodon_dir, "relative_totalonly_bars_vertical.png")
ggsave(filename = relative_totalonly_bars_vertical_file,
       plot=p,device="png",
       width=16,height=10, units="cm")

```

## Consensus and relative shifts

Let's make a graph just showing the shifts overall.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# construct the belief change dataset
consensusChange <- dp %>% 
  select(Subject,TimePoint,ConsensusPolitics) %>%
  mutate(ConsensusPolitics=as.numeric(ConsensusPolitics)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="ConsensusPolitics") %>%
  mutate(ConsensusChange = After-Before) %>%
  select(-c(After,Before)) %>%
  left_join(conds,by="Subject")

# calculate means for bars for visualisation
dpMeans <- consensusChange %>%
    group_by(Condition) %>%
    summarise(muAll = mean(ConsensusChange,na.rm=TRUE),
              sdAll = sd(ConsensusChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()


p <- dpMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=consensusChange,
              mapping=aes(y=ConsensusChange,
                          x=Condition,colour=Condition),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=0,linetype=2) +
  ylim(-10,10) +
  #scale_y_continuous(breaks=c(-25,0,25),labels=c("less","same",
  #                                               "more")) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Shift in perceived political consensus",
       subtitle = "Change in how much participants thought people in US agreed politically",
       y = "Consensus change (positive = more consensus)") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), 
        axis.ticks.y = element_blank())
  
p

consensus_shift_totalonly_bars_vertical_file <- here(figures_files_mastodon_dir, "consensus_shift_totalonly_bars_vertical.png")
ggsave(filename = consensus_shift_totalonly_bars_vertical_file,
       plot=p,device="png",
       width=14,height=10, units="cm")


# construct the change dataset
relativeChange <- dp %>% 
  select(Subject,TimePoint,RelativePolitics) %>%
  mutate(RelativePolitics=as.numeric(RelativePolitics)) %>% 
  pivot_wider(names_from="TimePoint",
              values_from="RelativePolitics") %>%
  mutate(RelativeChange = After-Before) %>%
  select(-c(After,Before)) %>%
  left_join(conds,by="Subject")

# calculate means for bars for visualisation
dpMeans <- relativeChange %>%
    group_by(Condition) %>%
    summarise(muAll = mean(RelativeChange,na.rm=TRUE),
              sdAll = sd(RelativeChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()


p <- dpMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_hline(yintercept=0,colour="grey") +
  geom_jitter(data=relativeChange,
              mapping=aes(y=RelativeChange,
                          x=Condition,colour=Condition),
              alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  #coord_flip() +  
  #scale_x_discrete(limits = rev) +
  geom_hline(yintercept=0,linetype=2) +
  ylim(-10,10) +
  #scale_y_continuous(breaks=c(-25,0,25),labels=c("less","same",
  #                                               "more")) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Shift in perceived relative politics",
       subtitle = "Change in how participants rated own beliefs relative to others in US",
       y = "Shift in relative beliefs (positive = right)") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), 
        axis.ticks.y = element_blank())
  
p

relative_shift_totalonly_bars_vertical_file <- here(figures_files_mastodon_dir, "relative_shift_totalonly_bars_vertical.png")
ggsave(filename = relative_shift_totalonly_bars_vertical_file,
       plot=p,device="png",
       width=14,height=10, units="cm")

```


## Emotions

### Affective polarisation

We can visualise how affective polarisation changes. Remember that higher numbers indicate more polarisation. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
d_before$Condition <- factor(d_before$Condition, 
                             levels=c("Left","Control","Right"))

# first we need to construct our datasets
deB <- d_before %>%
  select(Subject,UserName,Condition,TimePoint,
         AffPol,RepThermometer,DemThermometer,
         RepNeg,RepPos,DemNeg,DemPos)
deA <- d_after %>%
  select(Subject,UserName,Condition,TimePoint,
         AffPol,RepThermometer,DemThermometer,
         RepNeg,RepPos,DemNeg,DemPos)
de <- rbind(deB,deA)

# calculate means for bars for visualisation
apMeans <- de %>%
    group_by(Condition,TimePoint) %>%
    mutate(AffPol=as.numeric(AffPol)) %>% 
    summarise(muAll = mean(AffPol,na.rm=TRUE),
              sdAll = sd(AffPol,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of affective polarisation
p <-  apMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_jitter(data=de,mapping=aes(y=AffPol,x=Condition,
                                 colour=Condition),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_wrap(~TimePoint,ncol=2) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Affective polarisation by condition",
       subtitle = "Positive = more polarised") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

affective_polarisation_file <- here(figures_files_mastodon_dir, "affective_polarisation.png")
ggsave(filename = affective_polarisation_file,
       plot=p,device="png",
       width=12,height=8, units="cm")


# construct the affpol change dataset
apD <- de %>% 
  select(Subject,Condition,TimePoint,AffPol) %>%
  mutate(AffPol=as.numeric(AffPol)) %>% 
  pivot_wider(names_from="TimePoint",values_from="AffPol") %>%
  mutate(apChange = After-Before) 

# calculate means for bars for visualisation
apCMeans <- apD %>%
    group_by(Condition) %>%
    summarise(muAll = mean(apChange,na.rm=TRUE),
              sdAll = sd(apChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()


# create plot of affective polarisation
p <-  apCMeans %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=Condition)) +
  geom_jitter(data=apD,mapping=aes(y=apChange,x=Condition,
                                 colour=Condition),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Change in affective polarisation by condition",
       subtitle = "Positive = more polarised at end of experiment") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank(),axis.title.y = element_blank())
  
p

change_affective_polarisation_file <- here(figures_files_mastodon_dir, "change_affective_polarisation.png")
ggsave(filename = change_affective_polarisation_file,
       plot=p,device="png",
       width=12,height=8, units="cm")
```

### Affective polarisation based on political id

Now let's break down the affective polarisation to see what's happening precisely, as a function of political id

```{r echo=FALSE, message=FALSE, warning=FALSE}
dpol <- d_before %>%
  select(Subject,PoliticalID,PoliticalIDNum)

dePol <- de %>%
  left_join(dpol,by="Subject") %>%
  filter(!is.na(PoliticalID)) %>% 
  mutate(AffPol=as.numeric(AffPol))

# calculate means for bars for visualisation
apMeans <- dePol %>%
    group_by(Condition,PoliticalID,TimePoint) %>%
    summarise(muAll = mean(AffPol,na.rm=TRUE),
              sdAll = sd(AffPol,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of affective polarisation
p <-  apMeans %>%
  ggplot(mapping=aes(x=TimePoint,y=muAll,fill=PoliticalID)) +
  geom_jitter(data=dePol,mapping=aes(y=AffPol,x=TimePoint,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Condition) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(15,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Affective polarisation by political ID",
       subtitle = "Each dot is one person",
       y = "Affective polarisation") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.y = element_blank(),axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

affective_polarisation_politicalID_file <- here(figures_files_mastodon_dir, "affective_polarisation_politicalID.png")
ggsave(filename = affective_polarisation_politicalID_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# look at the change now
dePolChange <- dePol %>%
  select(Subject,Condition,TimePoint,PoliticalID,AffPol) %>%
  pivot_wider(names_from=TimePoint,values_from=AffPol) %>%
  mutate(AffPolChange = After-Before)

# calculate means for bars for visualisation
apcMeans <- dePolChange %>%
    group_by(Condition,PoliticalID) %>%
    summarise(muAll = mean(AffPolChange,na.rm=TRUE),
              sdAll = sd(AffPolChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of affective polarisation
p <-  apcMeans %>%
  ggplot(mapping=aes(x=PoliticalID,y=muAll,fill=PoliticalID)) +
  geom_jitter(data=dePolChange,mapping=aes(y=AffPolChange,x=PoliticalID,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_wrap(~Condition) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  ylim(-75,75) +
  scale_y_continuous(breaks=c(-65,70),labels=c("less","more")) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Change in affective polarisation by political ID",
       subtitle = "Each dot is one person",
       y = "Change in affective polarisation") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.y = element_blank(),axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
  
p

change_affective_polarisation_politicalID_file <- here(figures_files_mastodon_dir, "change_affective_polarisation_politicalID.png")
ggsave(filename = change_affective_polarisation_politicalID_file,
       plot=p,device="png",
       width=20,height=10, units="cm")

```

### Thermometers

Now let's break down the affective polarisation to see what's happening precisely, as a function of thermometers as well

```{r echo=FALSE, message=FALSE, warning=FALSE}
# calculate means for bars for visualisation
dePolParty <- dePol %>%
  pivot_longer(cols=c(RepThermometer,DemThermometer),names_to="Party",
               values_to="Thermometer") %>%
  mutate(Party = case_when(Party=="RepThermometer" ~ "Republicans",
                           Party=="DemThermometer" ~ "Democrats")) %>% 
  mutate(Thermometer=as.numeric(Thermometer))

aptMeans <- dePolParty %>%
  group_by(Condition,Party,PoliticalID,TimePoint) %>%
  summarise(n = n(),
            muAll = mean(Thermometer,na.rm=TRUE),
            sdAll = sd(Thermometer,na.rm=TRUE),
            sderrAll = sdAll/sqrt(n)) %>%
    ungroup()

dePolPartyCont <- dePolParty %>% filter(Condition=="Control")
dePolPartyRight <- dePolParty %>% filter(Condition=="Right")
dePolPartyLeft <- dePolParty %>% filter(Condition=="Left")

# create plot of affective polarisation
p <-  aptMeans %>%
  filter(Condition=="Control") %>%
  ggplot(mapping=aes(x=TimePoint,y=muAll,fill=PoliticalID)) +
  #geom_hline(yintercept=50,linetype=2) +
  geom_jitter(data=dePolPartyCont,mapping=aes(y=Thermometer,x=TimePoint,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Party) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Control: Thermometer ratings about each party",
       subtitle = "Rows = political ID; Columns = ratings about them",
       y = "Amount of liking") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=9, angle=90),
        axis.title.x = element_blank()) 
  
p

polid_party_thermometer_control_file <- here(figures_files_mastodon_dir, "polid_party_thermometer_control.png")
ggsave(filename = polid_party_thermometer_control_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of affective polarisation
p <-  aptMeans %>%
  filter(Condition=="Right") %>%
  ggplot(mapping=aes(x=TimePoint,y=muAll,fill=PoliticalID)) +
  #geom_hline(yintercept=50,linetype=2) +
  geom_jitter(data=dePolPartyRight,mapping=aes(y=Thermometer,x=TimePoint,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Party) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Right: Thermometer ratings about each party",
       subtitle = "Rows = political ID; Columns = ratings about them",
       y = "Amount of liking") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=9, angle=90),
        axis.title.x = element_blank()) 
  
p

polid_party_thermometer_right_file <- here(figures_files_mastodon_dir, "polid_party_thermometer_right.png")
ggsave(filename = polid_party_thermometer_right_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of affective polarisation
p <-  aptMeans %>%
  filter(Condition=="Left") %>%
  ggplot(mapping=aes(x=TimePoint,y=muAll,fill=PoliticalID)) +
  #geom_hline(yintercept=50,linetype=2) +
  geom_jitter(data=dePolPartyLeft,mapping=aes(y=Thermometer,x=TimePoint,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Party) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Left: Thermometer ratings about each party",
       subtitle = "Rows = political ID; Columns = ratings about them",
       y = "Amount of liking") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.title.x = element_blank()) 
  
p

polid_party_thermometer_left_file <- here(figures_files_mastodon_dir, "polid_party_thermometer_left.png")
ggsave(filename = polid_party_thermometer_left_file,
       plot=p,device="png",
       width=20,height=12, units="cm")


# look at the change now
dePolPartyChange <- dePolParty %>%
  select(Subject,Condition,TimePoint,PoliticalID,Party,Thermometer) %>%
  pivot_wider(names_from=TimePoint,values_from=Thermometer) %>%
  mutate(ThermChange = After-Before)

# calculate means for bars for visualisation
atcMeans <- dePolPartyChange %>%
    group_by(Condition,Party,PoliticalID) %>%
    summarise(muAll = mean(ThermChange,na.rm=TRUE),
              sdAll = sd(ThermChange,na.rm=TRUE),
              n = n(),
              sderrAll = sdAll/sqrt(n))  %>%
    ungroup()

# create plot of affective polarisation
p <-  atcMeans %>%
  ggplot(mapping=aes(x=PoliticalID,y=muAll,fill=PoliticalID)) +
  geom_hline(yintercept=0,linetype=2) +
  geom_jitter(data=dePolPartyChange,mapping=aes(y=ThermChange,
                                                x=PoliticalID,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  ylim(-30,30) +
  scale_y_continuous(breaks=c(-25,25),labels=c("less","more")) +
  facet_grid(Party~Condition) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Change in thermometer by political ID",
       subtitle = "Row = party being rated",
       y = "Change in liking",
       x = "Political ID of person doing the rating") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9,angle=90),
        axis.ticks.x = element_blank(),axis.ticks.y = element_blank())
  
p

change_polid_party_thermometer_file <- here(figures_files_mastodon_dir, "change_polid_party_thermometer.png")
ggsave(filename = change_polid_party_thermometer_file,
       plot=p,device="png",
       width=24,height=14, units="cm")

```

Now let's display the same information slightly differently, just focusing on Before and After in separate diagrams.

```{r echo=FALSE, message=FALSE, warning=FALSE}
dePolPartyBefore <- dePolParty %>% filter(TimePoint=="Before")
dePolPartyAfter <- dePolParty %>% filter(TimePoint=="After")

# create plot of affective polarisation
p <-  aptMeans %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=PoliticalID)) +
  #geom_hline(yintercept=50,linetype=2) +
  geom_jitter(data=dePolPartyBefore,mapping=aes(y=Thermometer,x=Condition,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Party) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Before: Thermometer ratings about each party",
       subtitle = "Rows = political ID; Columns = ratings about them",
       y = "Amount of liking") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=9, angle=90),
        axis.title.x = element_blank()) 
  
p

polid_party_thermometer_before_file <- here(figures_files_mastodon_dir, "polid_party_thermometer_before.png")
ggsave(filename = polid_party_thermometer_before_file,
       plot=p,device="png",
       width=20,height=12, units="cm")


# create plot of affective polarisation
p <-  aptMeans %>%
  filter(TimePoint=="After") %>%
  ggplot(mapping=aes(x=Condition,y=muAll,fill=PoliticalID)) +
  #geom_hline(yintercept=50,linetype=2) +
  geom_jitter(data=dePolPartyAfter,mapping=aes(y=Thermometer,x=Condition,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(PoliticalID~Party) +
  ylim(0,100) +
  scale_y_continuous(breaks=c(10,90),labels=c("none","lots")) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "After: Thermometer ratings about each party",
       subtitle = "Rows = political ID; Columns = ratings about them",
       y = "Amount of liking") +
  theme(axis.text.x = element_text(size=10, angle=30, vjust=0.7),
        axis.text.y = element_text(size=9, angle=90),
        axis.title.x = element_blank()) 
  
p

polid_party_thermometer_after_file <- here(figures_files_mastodon_dir, "polid_party_thermometer_after.png")
ggsave(filename = polid_party_thermometer_after_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

```



# Magpie experience

Now let's relate all of this to their experiences on Magpie. First, overall.


```{r echo=FALSE, message=FALSE, warning=FALSE}
# first we need to construct our datasets
dmPol <- d_before %>%
  select(Subject,PoliticalID,PoliticalIDNum)
dm <- d_after %>%
  select(Subject,UserName,Condition,RelativePolitics,
         OverallExperience,PropLiked,PropAligned,PropTrolls) %>%
  left_join(dmPol,by="Subject") %>% 
  mutate(OverallExperience=as.numeric(OverallExperience),
         RelativePolitics=as.numeric(RelativePolitics))
dmM <- dm %>% filter(!is.na(PoliticalID))

# look at overall experience by condition and politicalID
magMeans <- dmM %>%
  group_by(Condition,PoliticalID) %>%
  summarise(n = n(),
            muAll = mean(OverallExperience,na.rm=TRUE),
            sdAll = sd(OverallExperience,na.rm=TRUE),
            sderrAll = sdAll/sqrt(n)) %>%
    ungroup()

# create plot
p <-  magMeans %>%
  ggplot(mapping=aes(x=PoliticalID,y=muAll,fill=PoliticalID)) +
  geom_jitter(data=dmM,mapping=aes(y=OverallExperience,x=PoliticalID,
                                 colour=PoliticalID),
              alpha=0.6,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_wrap(~Condition) +
  ylim(0,10) +
  scale_y_continuous(breaks=c(0,5,10)) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Overall Magpie experience",
       subtitle = "By condition and political identification",
       y = "Rating (higher = liked it more)",
       x = "Political ID of person doing the rating") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9), axis.ticks.x = element_blank()) 
  
p

overallexperience_polid_file <- here(figures_files_mastodon_dir, "overallexperience_polid.png")
ggsave(filename = overallexperience_polid_file,
       plot=p,device="png",
       width=20,height=10, units="cm")
```

Next, their perception of who else is on Magpie


```{r echo=FALSE, message=FALSE, warning=FALSE}
# first we need to construct our datasets
dm_wide <- dmM %>%
  pivot_longer(cols=c("PropAligned","PropLiked","PropTrolls"),
               names_to="Proportion",values_to="Rating") %>%
  mutate(Proportion = case_when(Proportion=="PropLiked" ~ "Like",
                                Proportion=="PropAligned" ~ "Aligned",
                                Proportion=="PropTrolls" ~ "Trolls"))

# look at overall experience by condition and politicalID
magMeans <- dm_wide %>%
  group_by(Condition,PoliticalID,Proportion) %>%
  summarise(n = n(),
            muAll = mean(Rating,na.rm=TRUE),
            sdAll = sd(Rating,na.rm=TRUE),
            sderrAll = sdAll/sqrt(n)) %>%
    ungroup()

# create plot
p <-  magMeans %>%
  ggplot(mapping=aes(x=PoliticalID,y=muAll,fill=PoliticalID)) +
  geom_jitter(data=dm_wide,mapping=aes(y=Rating,x=PoliticalID,
                                 colour=PoliticalID),
              alpha=0.75,show.legend=FALSE,width=0.2,height=0.05) +
  geom_col(colour="black",position="dodge",
           show.legend=FALSE,alpha=0.35) +
  geom_errorbar(mapping=aes(ymin = muAll-sderrAll,
                            ymax=muAll+sderrAll),width=0.2) +
  theme_bw() +
  facet_grid(Proportion~Condition) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Participant estimations of people on Magpie",
       subtitle = "Rows are the political ID of the participant",
       y = "Estimated proportion") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=10),
        axis.title.x = element_blank()) 
  
p

proportions_estimated_polid_file <- here(figures_files_mastodon_dir, "proportions_estimated_polid.png")
ggsave(filename = proportions_estimated_polid_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

```

Now let's look at how their initial relative political rating is related to the overall experience.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# create plot of relative positioning
p <- dmM %>%
  ggplot(mapping=aes(x=RelativePolitics,y=OverallExperience,
                     fill=PoliticalID,colour=PoliticalID)) +
  geom_vline(xintercept=50,linetype=2) +
  geom_point(alpha=0.6,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  ylim(0,10) +
  xlim(0,100) +
  scale_y_continuous(breaks=c(0,5,10)) +
  scale_x_continuous(breaks=c(10,50,90),labels=c("left","mid","right")) +
  facet_grid(PoliticalID~Condition) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Political views and the Magpie experience",
       subtitle = "Columns = condition; rows = political ID",
       x = "Relative political alignment",
       y = "Magpie rating (higher = liked it more)") +
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(), axis.ticks.y=element_blank())
  
p

overallexperience_relativepol_file <- here(figures_files_mastodon_dir, "overallexperience_relativepol.png")
ggsave(filename = overallexperience_relativepol_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of how many they liked
p <- dmM %>%
  ggplot(mapping=aes(x=RelativePolitics,y=PropLiked,
                     fill=PoliticalID,colour=PoliticalID)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  facet_grid(Condition~PoliticalID) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Political views and liking on Magpie",
       x = "Relative political alignment (low=left)",
       y = "Proportion of Magpie users they liked") +
  theme(axis.text.x = element_text(size=10, angle=45, vjust=0.5),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

propliked_relativepol_file <- here(figures_files_mastodon_dir, "propliked_relativepol.png")
ggsave(filename = propliked_relativepol_file,
       plot=p,device="png",
       width=20,height=12, units="cm")


# create plot of how many they aligned
p <- dmM %>%
  ggplot(mapping=aes(x=RelativePolitics,y=PropAligned,
                     fill=PoliticalID,colour=PoliticalID)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  facet_grid(Condition~PoliticalID) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Political views and alignment on Magpie",
       x = "Relative political alignment (low=left)",
       y = "Proportion of Magpie users they aligned with") +
  theme(axis.text.x = element_text(size=10, angle=45, vjust=0.5),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

propaligned_relativepol_file <- here(figures_files_mastodon_dir, "propaligned_relativepol.png")
ggsave(filename = propaligned_relativepol_file,
       plot=p,device="png",
       width=20,height=12, units="cm")


# create plot of how many they aligned
p <- dmM %>%
  ggplot(mapping=aes(x=RelativePolitics,y=PropTrolls,
                     fill=PoliticalID,colour=PoliticalID)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  facet_grid(Condition~PoliticalID) +
  scale_fill_manual(values=politicalIDColours) +
  scale_colour_manual(values=politicalIDColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Political views and troll estimation on Magpie",
       x = "Relative political alignment (low=left)",
       y = "Proportion of Magpie users they thought trolls") +
  theme(axis.text.x = element_text(size=10, angle=45, vjust=0.5),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

proptrolls_relativepol_file <- here(figures_files_mastodon_dir, "proptrolls_relativepol.png")
ggsave(filename = proptrolls_relativepol_file,
       plot=p,device="png",
       width=20,height=12, units="cm")
```

### Relationship between beliefs and Magpie experience

Look at initial beliefs compared to how much they liked Magpie

```{r echo=FALSE, message=FALSE, warning=FALSE}
dbmRel <- db_wide %>%
  left_join(dm,by=c("Subject","Condition")) %>% 
  mutate(Beliefs=as.numeric(Beliefs),
         OverallExperience=as.numeric(OverallExperience),
         PropLiked=as.numeric(PropLiked),
         PropAligned=as.numeric(PropAligned),
         PropTrolls=as.numeric(PropTrolls))

# create plot of relative positioning
p <- dbmRel %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Beliefs,y=OverallExperience,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,5,10),limits=c(0,10)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and the Magpie experience",
       x = "Initial beliefs (lower = more left)",
       y = "Magpie rating (higher = more positive)") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

overallexperience_initialbeliefs_file <- here(figures_files_mastodon_dir, "overallexperience_initialbeliefs.png")
ggsave(filename = overallexperience_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of relative positioning
p <- dbmRel %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Beliefs,y=PropLiked,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,50,100),limits=c(0,100)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and Magpie participants liked",
       x = "Initial beliefs (lower = more left)",
       y = "Prop Magpie participants liked") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

propliked_initialbeliefs_file <- here(figures_files_mastodon_dir, "propliked_initialbeliefs.png")
ggsave(filename = propliked_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of relative positioning
p <- dbmRel %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Beliefs,y=PropAligned,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,50,100),limits=c(0,100)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and Magpie participants aligned",
       x = "Initial beliefs (lower = more left)",
       y = "Prop Magpie participants thought aligned") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

propaligned_initialbeliefs_file <- here(figures_files_mastodon_dir, "propaligned_initialbeliefs.png")
ggsave(filename = propaligned_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

# create plot of relative positioning
p <- dbmRel %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Beliefs,y=PropTrolls,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,50,100),limits=c(0,100)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and Magpie participants trolls",
       x = "Initial beliefs (lower = more left)",
       y = "Prop Magpie participants thought trolls") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

proptrolls_initialbeliefs_file <- here(figures_files_mastodon_dir, "proptrolls_initialbeliefs.png")
ggsave(filename = proptrolls_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")
```

Let's also look at this by just condition.

```{r echo=FALSE, message=FALSE, warning=FALSE}
dbmRel <- db_wide %>%
  left_join(dm,by=c("Subject","Condition")) %>% 
  mutate(Beliefs=as.numeric(Beliefs),
         OverallExperience=as.numeric(OverallExperience))

# create plot of relative positioning
p <- dbmRel %>%
  filter(TimePoint=="Before") %>%
  filter(Topic=="Total") %>%
  ggplot(mapping=aes(x=Beliefs,y=OverallExperience,
                     fill=Condition,colour=Condition)) +
  geom_vline(xintercept=50,linetype=2) +
  geom_point(alpha=0.6,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,5,10),limits=c(0,10)) +
  scale_x_continuous(breaks=c(10,50,90),limits=c(0,100),
                     labels=c("left","center","right")) +
  facet_wrap(~Condition) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = 
          element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and the Magpie experience",
       x = "Initial beliefs",
       y = "Magpie enjoyment") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
  
p

overallexperience_initialbeliefs_condonly_file <- here(figures_files_mastodon_dir, "overallexperience_initialbeliefs_condonly.png")
ggsave(filename = overallexperience_initialbeliefs_condonly_file,
       plot=p,device="png",
       width=14,height=7, units="cm")

```



### Relationship between belief change and Magpie experience

Look at belief change compared to how much they liked Magpie

```{r echo=FALSE, message=FALSE, warning=FALSE}
dbmRelChange <- dbmRel %>%
  pivot_wider(names_from="TimePoint",values_from="Beliefs") %>%
  mutate(BeliefChange = After-Before)

# create plot of relative positioning
p <- dbmRelChange %>%
  ggplot(mapping=aes(y=BeliefChange,x=OverallExperience,
                     fill=Topic,colour=Topic)) +
  geom_hline(yintercept=0,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_x_continuous(breaks=c(0,5,10),limits=c(0,10)) +
  scale_y_continuous(breaks=c(-25,0,25),limits=c(-25,25)) +
  facet_grid(Condition~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Belief change and the Magpie experience",
       y = "Belief change (negative = more left)",
       x = "Magpie rating (higher = more positive)") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

overallexperience_beliefchange_file <- here(figures_files_mastodon_dir, "overallexperience_beliefchange.png")
ggsave(filename = overallexperience_beliefchange_file,
       plot=p,device="png",
       width=20,height=12, units="cm")
```

L

### Relationship between beliefs and polarisation

Look at initial beliefs compared to different measures of polarisation

```{r echo=FALSE, message=FALSE, warning=FALSE}
dBelPol <- dePol %>%
  left_join(db_wide,by=c("Subject","TimePoint","Condition")) %>% 
  mutate(Beliefs=as.numeric(Beliefs),
         AffPol=as.numeric(AffPol))

# create plot of relative positioning
p <- dBelPol %>%
  ggplot(mapping=aes(x=Beliefs,y=AffPol,
                     fill=Condition,colour=Condition)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  #scale_y_continuous(breaks=c(0,5,10),limits=c(0,10)) +
  facet_grid(Condition~TimePoint) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and affective polarisation",
       x = "Initial beliefs (lower = more left)",
       y = "Affective polarisation (higher = more polarised)") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

affpol_initialbeliefs_file <- here(figures_files_mastodon_dir, "affpol_initialbeliefs.png")
ggsave(filename = affpol_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

dBelPolTherm <- dBelPol %>%
  pivot_longer(cols=c(RepThermometer,DemThermometer),names_to="Party",
               values_to="Thermometer") %>%
  mutate(Party = case_when(Party=="RepThermometer" ~ "Republicans",
                           Party=="DemThermometer" ~ "Democrats")) %>% 
  mutate(Beliefs=as.numeric(Beliefs),
         Thermometer=as.numeric(Thermometer))


p <- dBelPolTherm %>%
  filter(TimePoint=="Before") %>%
  ggplot(mapping=aes(x=Beliefs,y=Thermometer,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_hline(yintercept=50,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  scale_y_continuous(breaks=c(0,50,100),limits=c(0,100)) +
  facet_grid(Party~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and thermometers",
       x = "Initial beliefs (lower = more left)",
       y = "Thermometer rating") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

therm_initialbeliefs_file <- here(figures_files_mastodon_dir, "therm_initialbeliefs.png")
ggsave(filename = therm_initialbeliefs_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

dppC <- dePolPartyChange %>%
  select(Subject,Condition,Party,ThermChange)
dbwBefore <- db_wide %>% filter(TimePoint=="Before") %>%
  select(-c(TimePoint))

dbptChange <- dppC %>%
  left_join(dbwBefore,by=c("Subject","Condition"),
            relationship="many-to-many") %>% 
  mutate(Beliefs=as.numeric(Beliefs),
         ThermChange=as.numeric(ThermChange))

p <- dbptChange %>%
  filter(Condition=="Control") %>%
  ggplot(mapping=aes(x=Beliefs,y=ThermChange,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_hline(yintercept=0,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  #scale_y_continuous(breaks=c(-50,,10),limits=c(0,10)) +
  facet_grid(Party~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Control: Initial beliefs and thermometer change",
       subtitle = "Rows are the target party of the thermometer",
       x = "Initial beliefs (lower = more left)",
       y = "Thermometer rating change") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

thermchange_initialbeliefs_control_file <- here(figures_files_mastodon_dir, "thermchange_initialbeliefs_control.png")
ggsave(filename = thermchange_initialbeliefs_control_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

p <- dbptChange %>%
  filter(Condition=="Right") %>%
  ggplot(mapping=aes(x=Beliefs,y=ThermChange,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_hline(yintercept=0,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  #scale_y_continuous(breaks=c(-50,,10),limits=c(0,10)) +
  facet_grid(Party~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Right: Initial beliefs and thermometer change",
       subtitle = "Rows are the target party of the thermometer",
       x = "Initial beliefs (lower = more left)",
       y = "Thermometer rating change") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

thermchange_initialbeliefs_right_file <- here(figures_files_mastodon_dir, "thermchange_initialbeliefs_right.png")
ggsave(filename = thermchange_initialbeliefs_right_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

p <- dbptChange %>%
  filter(Condition=="Left") %>%
  ggplot(mapping=aes(x=Beliefs,y=ThermChange,
                     fill=Topic,colour=Topic)) +
  geom_vline(xintercept=50,linetype=3) +
  geom_hline(yintercept=0,linetype=3) +
  geom_point(alpha=0.4,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  #scale_y_continuous(breaks=c(-50,,10),limits=c(0,10)) +
  facet_grid(Party~factor(Topic,levels=c("Trans","Climate",
                                             "AI","Israel","Total"))) +
  scale_fill_manual(values=topicColours) +
  scale_colour_manual(values=topicColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Left: Initial beliefs and thermometer change",
       subtitle = "Rows are the target party of the thermometer",
       x = "Initial beliefs (lower = more left)",
       y = "Thermometer rating change") +
  theme(axis.text.x = element_text(size=9),
        axis.text.y = element_text(size=9, angle=90),
        axis.ticks.x = element_blank())
  
p

thermchange_initialbeliefs_left_file <- here(figures_files_mastodon_dir, "thermchange_initialbeliefs_left.png")
ggsave(filename = thermchange_initialbeliefs_left_file,
       plot=p,device="png",
       width=20,height=12, units="cm")

p <- dbptChange %>%
  filter(Topic=="Total") %>%
  ggplot(mapping=aes(x=Beliefs,y=ThermChange,
                     fill=Condition,colour=Condition)) +
  geom_vline(xintercept=50,linetype=2) +
  geom_hline(yintercept=0,linetype=2) +
  geom_point(alpha=0.6,show.legend=FALSE,width=0.4,height=0.05) +
  geom_smooth(method="lm",colour="black",show.legend=FALSE) +
  theme_bw() +
  ylim(-25,25) +
  xlim(0,100) +
  scale_y_continuous(breaks=c(-20,20),
                     limits=c(-25,25), labels=c("less","more")) +
  scale_x_continuous(breaks=c(10,50,90),labels=c("left","mid","right")) +
  facet_grid(Party~Condition) +
  scale_fill_manual(values=conditionColours) +
  scale_colour_manual(values=conditionColours) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  labs(title = "Initial beliefs and thermometer change",
       subtitle = "Rows are the target party of the thermometer",
       x = "Initial beliefs (lower = more left)",
       y = "Thermometer rating change") +
  theme(axis.text.x = element_text(size=8),
        axis.text.y = element_text(size=8, angle=90),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
  
p

thermchange_initialbeliefs_total_file <- here(figures_files_mastodon_dir, "thermchange_initialbeliefs_total.png")
ggsave(filename = thermchange_initialbeliefs_total_file,
       plot=p,device="png",
       width=20,height=10, units="cm")
```