---
title: "Visualisation for Magpie conversation data"
author: "Andrew Perfors"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
rm(list=ls())

library(tidyverse)
library(here)
library(Polychrome)
library(patchwork)
source(here("R/visualise/supplementaryFunctions.R"))

# Define subfolders
processed_files_mastodon_dir <- "data/mastodon/files/processed"
raw_files_mastodon_dir <- "data/mastodon/files/raw"
figures_files_mastodon_dir <- "data/mastodon/files/figures"
all_char_cols <- cols(.default = "c")
DRY_RUN <- FALSE
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
# load the combined data
d_before <- read_csv(here(processed_files_mastodon_dir, "combined", "before.csv"),
                     col_types = all_char_cols)
d_after <- read_csv(here(processed_files_mastodon_dir, "combined", "after.csv"),
                    col_types = all_char_cols)


# load the conversation data
# Favourites
dc_fav <- read_csv(here(processed_files_mastodon_dir, "control", "favourites.csv"),
                   col_types = all_char_cols)
dl_fav <- read_csv(here(processed_files_mastodon_dir, "left", "favourites.csv"),
                   col_types = all_char_cols)
dr_fav <- read_csv(here(processed_files_mastodon_dir, "right", "favourites.csv"),
                   col_types = all_char_cols)
d_fav <- rbind(dc_fav,dl_fav,dr_fav)
rm(dc_fav,dl_fav,dr_fav)

# Account Summaries
dc_accSum <- read_csv(here(processed_files_mastodon_dir, "control", "account_summaries.csv"),
                      col_types = all_char_cols)
dl_accSum <- read_csv(here(processed_files_mastodon_dir, "left", "account_summaries.csv"),
                      col_types = all_char_cols)
dr_accSum <- read_csv(here(processed_files_mastodon_dir, "right", "account_summaries.csv"),
                      col_types = all_char_cols)
d_accSum <- rbind(dc_accSum,dl_accSum,dr_accSum)
rm(dc_accSum,dl_accSum,dr_accSum)

# Status Summaries
dc_statSum <- read_csv(here(processed_files_mastodon_dir, "control", "status_summaries.csv"),
                       col_types = all_char_cols)
dl_statSum <- read_csv(here(processed_files_mastodon_dir, "left", "status_summaries.csv"),
                       col_types = all_char_cols)
dr_statSum <- read_csv(here(processed_files_mastodon_dir, "right", "status_summaries.csv"),
                       col_types = all_char_cols)
d_statSum <- rbind(dc_statSum,dl_statSum,dr_statSum)
rm(dc_statSum,dl_statSum,dr_statSum)

# Status with Annotation
dc_stat <- read_csv(here(raw_files_mastodon_dir, "control", "statuses_with_annotation.csv"),
                    col_types = all_char_cols) %>% 
  filter(Time >= "2024-08-06T21:00:00Z" & Time <= "2024-08-09T21:00:00Z")

dl_stat <- read_csv(here(raw_files_mastodon_dir, "left", "statuses_with_annotation.csv"),
                    col_types = all_char_cols) %>% 
  filter(Time >= "2024-09-03T20:30:00Z" & Time <= "2024-09-06T20:30:00Z")

dr_stat <- read_csv(here(raw_files_mastodon_dir, "right", "statuses_with_annotation.csv"),
                    col_types = all_char_cols) %>% 
  filter(Time >= "2024-08-20T21:00:00Z" & Time <= "2024-08-23T21:00:00Z")

d_stat <- rbind(dc_stat,dl_stat,dr_stat)
rm(dc_stat,dl_stat,dr_stat)

# Follows
dc_fol <- read_csv(here(processed_files_mastodon_dir, "control", "follows.csv"),
                   col_types = all_char_cols)
dl_fol <- read_csv(here(processed_files_mastodon_dir, "left", "follows.csv"),
                   col_types = all_char_cols)
dr_fol <- read_csv(here(processed_files_mastodon_dir, "right", "follows.csv"),
                   col_types = all_char_cols)
d_fol <- rbind(dc_fol,dl_fol,dr_fol)
rm(dc_fol,dl_fol,dr_fol)

db <- d_before %>%
  select(UserName,PoliticalID,PoliticalIDNum,BeliefAI,BeliefClimate,
         BeliefIsrael,BeliefTrans,Belief,RepThermometer,DemThermometer,
         AffPol,RepNeg,RepPos,DemNeg,DemPos) %>% 
  mutate(across(-UserName, as.numeric))
da <- d_after %>%
  select(UserName,BeliefAI,BeliefClimate,BeliefIsrael,BeliefTrans,
         Belief,RepThermometer,DemThermometer,
         AffPol,RepNeg,RepPos,DemNeg,DemPos,OverallExperience) %>%
  rename(AfterBeliefAI = BeliefAI,
         AfterBeliefClimate = BeliefClimate,
         AfterBeliefIsrael = BeliefIsrael,
         AfterBeliefTrans = BeliefTrans,
         AfterBelief = Belief,
         AfterRepThermometer = RepThermometer,
         AfterDemThermometer = DemThermometer,
         AfterAffPol = AffPol, AfterRepNeg = RepNeg,
         AfterRepPos = RepPos, AfterDemNeg = DemNeg,
         AfterDemPos = DemPos)%>%
  mutate(across(-UserName, as.numeric))
d_exp <- db %>%
  left_join(da,by="UserName") %>%
  mutate(BeliefChangeAI = AfterBeliefAI - BeliefAI,
         BeliefChangeClimate = AfterBeliefClimate - BeliefClimate,
         BeliefChangeIsrael = AfterBeliefIsrael - BeliefIsrael,
         BeliefChangeTrans = AfterBeliefTrans - BeliefTrans,
         BeliefChange = AfterBelief - Belief,
         RepThermChange = AfterRepThermometer - RepThermometer,
         DemThermChange = AfterDemThermometer - DemThermometer,
         AffPolChange = AfterAffPol - AffPol,
         RepNegChange = AfterRepNeg - RepNeg,
         RepPosChange = AfterRepPos - RepPos,
         DemNegChange = AfterDemNeg - DemNeg,
         DemPosChange = AfterDemPos - DemPos) %>%
  select(UserName,PoliticalID,PoliticalIDNum,Belief,BeliefChange,
         BeliefAI,BeliefChangeAI,BeliefClimate,BeliefChangeClimate,
         BeliefIsrael,BeliefChangeIsrael,BeliefTrans,BeliefChangeTrans,
         RepThermometer,RepThermChange,DemThermometer,DemThermChange,
         AffPol,AffPolChange,RepNeg,RepNegChange,RepPos,RepPosChange,
         DemNeg,DemNegChange,DemPos,DemPosChange,OverallExperience)
rm(da,db)

d_stat <- d_stat %>%
  left_join(d_exp,by="UserName")
```

Do some basic organisational things

```{r message=FALSE, warning=FALSE, echo=FALSE}

# set type colours by hand
statusColours <- c("Post"="#0000CC","Reply"="#0099FF","Reblog"="#CCCCFF",
                   "Favourite"="#9933FF")

goodBadColour <- c("Good"="#00AA11","Bad"="#BB0000")

conditionColours <- c("Left"="#99CCFF",
                      "Control"="#339933","Right"="#FF99CC")

dayColours <- c("Day1"="#66FF99","Day2"="#66DD33",
                "Day3"="#009933","Day4"="#007700","Day5"="#CCFF33")

topicColours <- c("Trans"="#AA3399","Gender"="#FF99FF",
                  "Climate"="#00AA66","Environment"="#88EE22",
                  "AI"="#0066CC","SciTech"="#99CCFF",
                  "Israel"="#CC9900","Foreign"="#FFCC33",
                  "MoneyEcon" = "#555555", "CrimeGuns"="#888888",
                  "Religion" = "#AAAAAA", "Health"="#CCCCCC",
                  "Fun"="#9999FF","Total"="#CC0000")

shortTopicColours <- c("Trans"="#AA3399","Climate"="#00AA66",
                  "AI"="#0066CC","Israel"="#CC9900",
                  "Offtopic" = "#AAAAAA", 
                  "Friendly"="#9955FF","Meta"="#CC0000")

polarityColours <- c("left"="#3399CC","na"="#9999FF","right"="#CC0066")
politicalIDColours <- c("democrat"="#3399CC","independent"="#9999FF",
                     "republican"="#CC0066")
partyColours <- c("Democrats"="#3399CC","Republicans"="#CC0066")

# set factor levels
d_fav$Condition <- factor(d_fav$Condition,
                             levels=c("Left","Control","Right"))
d_fol$Condition <- factor(d_fol$Condition,
                             levels=c("Left","Control","Right"))
d_stat$Condition <- factor(d_stat$Condition,
                             levels=c("Left","Control","Right"))
d_accSum$Condition <- factor(d_accSum$Condition,
                             levels=c("Left","Control","Right"))
d_statSum$Condition <- factor(d_statSum$Condition,
                             levels=c("Left","Control","Right"))

d_fav$ExpDay <- factor(d_fav$ExpDay,
                       levels=c("Day1","Day2","Day3","Day4","Day5"))
d_fol$ExpDay <- factor(d_fol$ExpDay,
                       levels=c("Day1","Day2","Day3","Day4","Day5"))
d_stat$ExpDay <- factor(d_stat$ExpDay,
                       levels=c("Day1","Day2","Day3","Day4","Day5"))
```


## Engagement metrics

### Engagement overall

Let's first look at the amount of engagement in each condition, broken down by: posts, replies, reposts, favourites. We remove all of the posts from troll accounts but don't remove favourites or reblogs of those posts as they originated from non-trolls.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Troll==0) %>%
  group_by(Condition) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,Type,n)

dSumFav <- d_fav %>% 
  filter(ExpDay!="Day5") %>%
  group_by(Condition) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  select(Condition, Type, n)

dEngSum <- rbind(dEngSumTemp,dSumFav)
dEngSum$Type <- ordered(dEngSum$Type, 
                        levels=c("Favourite","Reblog","Reply",
                                               "Post"))

p <- dEngSum %>%
  ggplot(mapping=aes(y=Condition,x=n,fill=Type)) +
  geom_col(position="stack",orientation="y",colour="black") +
  theme_bw() +
  scale_y_discrete(limits = rev) +
  theme(axis.text.y = element_text(angle = 90, size=10, hjust=0.5),
        axis.title.y = element_blank(), axis.title.x=element_blank(),
        axis.ticks.y = element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Engagment by condition") 

p

quantity_by_condition_file <- here(figures_files_mastodon_dir, "quantity_by_condition.png")
ggsave(filename = quantity_by_condition_file,
       plot=p,device="png",
       width=12,height=8, units="cm")
```

### Engagement by day

Broken down by day of the experiment, again removing troll accounts.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Troll==0) %>%
  group_by(Condition,ExpDay) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,ExpDay, Type,n)

dSumFav <- d_fav %>% 
  filter(ExpDay!="Day5") %>%
  group_by(Condition,ExpDay) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  select(Condition, ExpDay, Type, n)

dEngSum <- rbind(dEngSumTemp,dSumFav)
dEngSum$Type <- ordered(dEngSum$Type, 
                        levels=c("Favourite","Reblog","Reply",
                                               "Post"))

p <- dEngSum %>%
  ggplot(mapping=aes(x=ExpDay,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black") +
  theme_bw() +
  facet_wrap(~Condition,ncol=3) +
    theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 90, size=10, hjust=0.5),
        axis.title.y = element_blank(), axis.title.x=element_blank(),
        axis.ticks.y = element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Engagement by condition") 

p

quantity_by_condition_byday_file <- here(figures_files_mastodon_dir, "quantity_by_condition_byday.png")
ggsave(filename = quantity_by_condition_byday_file,
       plot=p,device="png",
       width=18,height=10, units="cm")
```


### Engagement by topic

Now for each topic we can show the same thing. 

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4, eval=FALSE}
statTopics <- d_stat %>% select(StatusID,Topic,UserName) %>%
  rename(FavouritedID=UserName)
dFavNew <- d_fav %>% left_join(statTopics,by=join_by(StatusID))

dEngSumTemp <- d_stat %>%
  filter(!is.na(Topic)) %>%
  filter(ExpDay!="Day5") %>%
  filter(Troll==0) %>%
  group_by(Condition,Topic) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,Topic,Type,n)

dSumFav <- dFavNew %>%
  filter(!is.na(Topic)) %>%
  filter(ExpDay!="Day5") %>%
  group_by(Condition,Topic) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  select(Condition, Topic, Type, n)

dEngSum <- rbind(dEngSumTemp,dSumFav)
dEngSum$Type <- ordered(dEngSum$Type, levels=c("Favourite","Reblog","Reply",
                                               "Post"))
dEngSum$Topic <- ordered(dEngSum$Topic,  
                              levels=c("Trans","Climate","AI","Israel",
                                       "Meta","Friendly","Offtopic"))


dSum <- dEngSum %>% group_by(Condition,Topic) %>%
  summarise(n = sum(n)) %>%
  ungroup() %>% mutate(Type="Sum") %>%
  select(Condition,Topic,Type,n)
dEngSum <- rbind(dEngSum,dSum)

p <- dEngSum %>%
  filter(Type!="Sum") %>%
  ggplot(mapping=aes(x=Condition,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black") +
  theme_bw() +
  facet_wrap(~Topic,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  #scale_y_discrete(limits=rev) +
  #scale_x_continuous(limits=c(0,450)) +
  theme(axis.text.y = element_blank(), #element_text(angle = 30, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank(),
        axis.ticks.y = element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by topic") 

p

engagement_by_topic_file <- here(figures_files_mastodon_dir, "engagement_by_topic.png")
ggsave(filename = engagement_by_topic_file,
       plot=p,device="png",
       width=30,height=12, units="cm")
```


### Conversations by topic

Now for each topic we can show the how the engagement was split up into conversations

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4, eval=FALSE}
statTopics <- d_stat %>% select(StatusID,Topic,ConvID) 
dFavNew <- d_fav %>% left_join(statTopics,by=join_by(StatusID))

dEngSumTemp <- d_stat %>%
  filter(!is.na(Topic)) %>%
  filter(ExpDay!="Day5") %>%
  #filter(Troll==0) %>%
  group_by(Condition,Topic,ConvID) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,Topic,ConvID,Type,n)

dSumFav <- dFavNew %>%
  filter(!is.na(Topic)) %>%
  filter(ExpDay!="Day5") %>%
  group_by(Condition,Topic,ConvID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  select(Condition, Topic, ConvID, Type, n)

dEngSum <- rbind(dEngSumTemp,dSumFav) 
dEngSum$Type <- ordered(dEngSum$Type, levels=c("Favourite","Reblog","Reply","Post"))

dEngSum$Topic <- ordered(dEngSum$Topic, 
                         levels=c("Trans","Climate","AI","Israel",
                                       "Meta","Friendly","Offtopic"))

dSum <- dEngSum %>% group_by(Condition,Topic,ConvID) %>%
  summarise(n = sum(n)) %>%
  ungroup() %>% mutate(Type="Sum") %>%
  select(Condition,Topic,ConvID,Type,n) 
dSumOrd <- dSum %>% group_by(Condition,Topic) %>%
  summarise(order = rank(ConvID),
            ConvID = ConvID) %>%
  ungroup()
dSum <- dSum %>% left_join(dSumOrd,by=join_by(Condition,Topic,ConvID))
dEngSum <- dEngSum %>% left_join(dSumOrd,by=join_by(Condition,Topic,ConvID)) 
dEngSum <- rbind(dEngSum,dSum)


p <- dEngSum %>%
  filter(Condition=="Control") %>%
  filter(Type!="Sum") %>%
  ggplot(mapping=aes(y=order,x=n,fill=Type)) +
  geom_col(position="stack",orientation="y",colour="black") +
  theme_bw() +
  facet_wrap(~Topic,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_reverse() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Control: Magpie Social threads") 

p

threads_by_topic_control_file <- here(figures_files_mastodon_dir, "threads_by_topic_control.png")
ggsave(filename = threads_by_topic_control_file,
       plot=p,device="png",
       width=30,height=25, units="cm")

p <- dEngSum %>%
  filter(Condition=="Right") %>%
  filter(Type!="Sum") %>%
  ggplot(mapping=aes(y=order,x=n,fill=Type)) +
  geom_col(position="stack",orientation="y",colour="black") +
  theme_bw() +
  facet_wrap(~Topic,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_reverse() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Right: Magpie Social threads") 

p

threads_by_topic_right_file <- here(figures_files_mastodon_dir, "threads_by_topic_right.png")
ggsave(filename = threads_by_topic_right_file,
       plot=p,device="png",
       width=30,height=25, units="cm")

p <- dEngSum %>%
  filter(Condition=="Left") %>%
  filter(Type!="Sum") %>%
  ggplot(mapping=aes(y=order,x=n,fill=Type)) +
  geom_col(position="stack",orientation="y",colour="black") +
  theme_bw() +
  facet_wrap(~Topic,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  scale_y_reverse() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Left: Magpie Social threads") 

p

threads_by_topic_left_file <- here(figures_files_mastodon_dir, "threads_by_topic_left.png")
ggsave(filename = threads_by_topic_left_file,
       plot=p,device="png",
       width=30,height=25, units="cm")


```

### Engagement by individual

Now for each individual we can show the same thing. The x axis is their overall belief (calculated from the sum of all their responses). Note that these values are jittered slightly so that people with beliefs at the exact same location aren't combined into the same bar.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  group_by(Condition,UserName,Troll) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,UserName,Troll,Type,n) %>%
  filter(UserName!="Admin") 

# jitters belief for ease of viewing
db <- d_exp %>% select(UserName,Belief)
db$Belief <- db$Belief + rnorm(n=nrow(db),mean=0,sd=1) 

dSumFav <- d_fav %>%
  filter(ExpDay!="Day5") %>%
  group_by(Condition,FavouriterID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  rename(UserName=FavouriterID) %>%
  left_join(db,by="UserName") %>%
  filter(UserName!="Admin") %>%
  mutate(Troll = 0) %>%
  select(Condition, UserName,Troll,Type, n)

dEngSum <- rbind(dEngSumTemp,dSumFav) %>%
  left_join(db,by="UserName") %>%
  filter(!is.na(Belief)) %>%
  mutate(pScore = Belief-50) %>%
  mutate(Polarity = case_when(pScore<0 ~ "left", 
                              is.na(pScore) ~ "troll",
                              TRUE~"right"),
         Colour = case_when(Polarity=="left" ~ "#3399CC", 
                            Polarity=="right" ~ "#CC0066",
                            Polarity=="troll" & Condition=="Left" ~ "#0000AA",
                            Polarity=="troll" & Condition=="Right" ~ "#AA0000"))
  
dEngSum$Type <- ordered(dEngSum$Type, levels=c("Favourite","Reblog","Reply",
                                               "Post"))

dSumOrd <- dEngSum %>% group_by(UserName) %>%
  filter(Type!="Favourite") %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSum <- dEngSum %>%
  left_join(dSumOrd,by="UserName")

p <- dEngSum %>%
  filter(Type!="Favourite") %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,200)) +
  scale_x_continuous(limits=c(-1,101)) +
  theme(legend.position=c(0.9,0.53)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user") 

p

individual_engagement_file <- here(figures_files_mastodon_dir, "individual_engagement.png")
ggsave(filename = individual_engagement_file,
       plot=p,device="png",
       width=30,height=24, units="cm")

dSumOrdFav <- dEngSum %>% group_by(UserName) %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSumFav <- dEngSum %>%
  select(-Sum) %>%
  left_join(dSumOrdFav,by="UserName")

p <- dEngSumFav %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,400)) +
  scale_x_continuous(limits=c(-1,101)) +
  theme(legend.position=c(0.9,0.53)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user") 

p

individual_engagement_with_favs_file <- here(figures_files_mastodon_dir, "individual_engagement_with_favs.png")
ggsave(filename = individual_engagement_with_favs_file,
       plot=p,device="png",
       width=30,height=24, units="cm")
```

Let's look at something similar broken down by topic.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumTransTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Trans") %>%
  group_by(Condition,UserName,Troll) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,UserName,Troll,Type,n) %>%
  filter(UserName!="Admin")

# get topic of favourites
ds_top <- d_stat %>% select(StatusID,Topic)
d_fav_top <- d_fav %>% left_join(ds_top,by="StatusID")

dSumTransFav <- d_fav_top %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Trans") %>%
  group_by(Condition,FavouriterID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  rename(UserName=FavouriterID) %>%
  filter(UserName!="Admin") %>%
  mutate(Troll = 0) %>%
  select(Condition, UserName, Troll,Type, n) 

# jitters belief for ease of viewing
db <- d_exp %>% select(UserName,BeliefTrans)
db$Belief <- db$BeliefTrans + rnorm(n=nrow(db),mean=0,sd=1) 
db$BeliefTrans <- NULL

dEngSumTrans <- rbind(dEngSumTransTemp,dSumTransFav) %>%
  left_join(db,by="UserName") %>%
  filter(!is.na(Belief)) %>%
  mutate(pScore = Belief-50) %>%
  mutate(Polarity = case_when(pScore<0 ~ "left", 
                              is.na(pScore) ~ "troll",
                              TRUE~"right"),
         Colour = case_when(Polarity=="left" ~ "#3399CC", 
                            Polarity=="right" ~ "#CC0066",
                            Polarity=="troll" & Condition=="Left" ~ "#0000AA",
                            Polarity=="troll" & Condition=="Right" ~ "#AA0000"))
 
dEngSumTrans$Type <- ordered(dEngSumTrans$Type, 
                             levels=c("Favourite","Reblog","Reply","Post"))

dSumTransOrd <- dEngSumTrans %>% group_by(UserName) %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSumTrans <- dEngSumTrans %>%
  left_join(dSumTransOrd,by="UserName")

p <- dEngSumTrans %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,100)) +
  scale_x_continuous(limits=c(-5,105)) +
  #theme(legend.position=c(0.93,0.93)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user: Trans topics") 

p

individual_trans_engagement_file <- here(figures_files_mastodon_dir, "individual_trans_engagement.png")
ggsave(filename = individual_trans_engagement_file,
       plot=p,device="png",
       width=30,height=24, units="cm")

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumIsraelTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Israel") %>%
  group_by(Condition,UserName,Troll) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,UserName,Troll,Type,n) %>%
  filter(UserName!="Admin")

# get topic of favourites
ds_top <- d_stat %>% select(StatusID,Topic)
d_fav_top <- d_fav %>% left_join(ds_top,by="StatusID")

dSumIsraelFav <- d_fav_top %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Israel") %>%
  group_by(Condition,FavouriterID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  rename(UserName=FavouriterID) %>%
  filter(UserName!="Admin") %>%
  mutate(Troll = 0) %>%
  select(Condition, UserName, Troll,Type, n) 

# jitters belief for ease of viewing
db <- d_exp %>% select(UserName,BeliefIsrael)
db$Belief <- db$BeliefIsrael + rnorm(n=nrow(db),mean=0,sd=1) 
db$BeliefIsrael <- NULL

dEngSumIsrael <- rbind(dEngSumIsraelTemp,dSumIsraelFav) %>%
  left_join(db,by="UserName") %>%
  filter(!is.na(Belief)) %>%
  mutate(pScore = Belief-50) %>%
  mutate(Polarity = case_when(pScore<0 ~ "left", 
                              is.na(pScore) ~ "troll",
                              TRUE~"right"),
         Colour = case_when(Polarity=="left" ~ "#3399CC", 
                            Polarity=="right" ~ "#CC0066",
                            Polarity=="troll" & Condition=="Left" ~ "#0000AA",
                            Polarity=="troll" & Condition=="Right" ~ "#AA0000"))
 
dEngSumIsrael$Type <- ordered(dEngSumIsrael$Type, 
                             levels=c("Favourite","Reblog","Reply","Post"))

dSumIsraelOrd <- dEngSumIsrael %>% group_by(UserName) %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSumIsrael <- dEngSumIsrael %>%
  left_join(dSumIsraelOrd,by="UserName")

p <- dEngSumIsrael %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,100)) +
  scale_x_continuous(limits=c(-5,105)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user: Israel topics") 

p

individual_israel_engagement_file <- here(figures_files_mastodon_dir, "individual_israel_engagement.png")
ggsave(filename = individual_israel_engagement_file,
       plot=p,device="png",
       width=30,height=24, units="cm")

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumClimateTemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Climate") %>%
  group_by(Condition,UserName,Troll) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,UserName,Troll,Type,n) %>%
  filter(UserName!="Admin")

# get topic of favourites
ds_top <- d_stat %>% select(StatusID,Topic)
d_fav_top <- d_fav %>% left_join(ds_top,by="StatusID")

dSumClimateFav <- d_fav_top %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="Climate") %>%
  group_by(Condition,FavouriterID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  rename(UserName=FavouriterID) %>%
  filter(UserName!="Admin") %>%
  mutate(Troll = 0) %>%
  select(Condition, UserName, Troll,Type, n) 

# jitters belief for ease of viewing
db <- d_exp %>% select(UserName,BeliefClimate)
db$Belief <- db$BeliefClimate + rnorm(n=nrow(db),mean=0,sd=1) 
db$BeliefClimate <- NULL

dEngSumClimate <- rbind(dEngSumClimateTemp,dSumClimateFav) %>%
  left_join(db,by="UserName") %>%
  filter(!is.na(Belief)) %>%
  mutate(pScore = Belief-50) %>%
  mutate(Polarity = case_when(pScore<0 ~ "left", 
                              is.na(pScore) ~ "troll",
                              TRUE~"right"),
         Colour = case_when(Polarity=="left" ~ "#3399CC", 
                            Polarity=="right" ~ "#CC0066",
                            Polarity=="troll" & Condition=="Left" ~ "#0000AA",
                            Polarity=="troll" & Condition=="Right" ~ "#AA0000"))
 
dEngSumClimate$Type <- ordered(dEngSumClimate$Type, 
                             levels=c("Favourite","Reblog","Reply","Post"))

dSumClimateOrd <- dEngSumClimate %>% group_by(UserName) %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSumClimate <- dEngSumClimate %>%
  left_join(dSumClimateOrd,by="UserName")

p <- dEngSumClimate %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,100)) +
  scale_x_continuous(limits=c(-5,105)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user: Climate topics") 

p

individual_climate_engagement_file <- here(figures_files_mastodon_dir, "individual_climate_engagement.png")
ggsave(filename = individual_climate_engagement_file,
       plot=p,device="png",
       width=30,height=24, units="cm")

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.height=4}
dEngSumAITemp <- d_stat %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="AI") %>%
  group_by(Condition,UserName,Troll) %>%
  count(isReblog = ifelse(is.na(StatusReblogID),"notReblog","isReblog"),
        isReply = ifelse(Reply,"isReply","notReply")) %>%
  ungroup() %>%
  mutate(Type = case_when(isReblog=="notReblog" & isReply=="notReply" ~ "Post",
                          isReblog=="isReblog" ~ "Reblog",
                          isReply=="isReply" ~ "Reply")) %>%
  select(Condition,UserName,Troll,Type,n) %>%
  filter(UserName!="Admin")

# get topic of favourites
ds_top <- d_stat %>% select(StatusID,Topic)
d_fav_top <- d_fav %>% left_join(ds_top,by="StatusID")

dSumAIFav <- d_fav_top %>%
  filter(ExpDay!="Day5") %>%
  filter(Topic=="AI") %>%
  group_by(Condition,FavouriterID) %>% 
  summarise(n=n()) %>% 
  ungroup %>% 
  mutate(Type="Favourite") %>%
  rename(UserName=FavouriterID) %>%
  filter(UserName!="Admin") %>%
  mutate(Troll = 0) %>%
  select(Condition, UserName, Troll,Type, n) 

# jitters belief for ease of viewing
db <- d_exp %>% select(UserName,BeliefAI)
db$Belief <- db$BeliefAI + rnorm(n=nrow(db),mean=0,sd=1) 
db$BeliefAI <- NULL

dEngSumAI <- rbind(dEngSumAITemp,dSumAIFav) %>%
  left_join(db,by="UserName") %>%
  filter(!is.na(Belief)) %>%
  mutate(pScore = Belief-50) %>%
  mutate(Polarity = case_when(pScore<0 ~ "left", 
                              is.na(pScore) ~ "troll",
                              TRUE~"right"),
         Colour = case_when(Polarity=="left" ~ "#3399CC", 
                            Polarity=="right" ~ "#CC0066",
                            Polarity=="troll" & Condition=="Left" ~ "#0000AA",
                            Polarity=="troll" & Condition=="Right" ~ "#AA0000"))
 
dEngSumAI$Type <- ordered(dEngSumAI$Type, 
                             levels=c("Favourite","Reblog","Reply","Post"))

dSumAIOrd <- dEngSumAI %>% group_by(UserName) %>%
  summarise(Sum = sum(n)) %>%
  ungroup() 
dEngSumAI <- dEngSumAI %>%
  left_join(dSumAIOrd,by="UserName")

p <- dEngSumAI %>%
  ggplot(mapping=aes(x=Belief,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black",
           width=0.5) +
  geom_text(aes(label=UserName,y=-5),size=2,angle=90,
            vjust="center",hjust="right") +
  geom_vline(xintercept=50,linetype ="dashed",colour="darkgrey") +
  theme_bw() +
  facet_wrap(~Condition,ncol=1) +
  scale_y_continuous(limits=c(-75,100)) +
  scale_x_continuous(limits=c(-5,105)) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(axis.text.y = element_text(angle = 0, size=9, hjust=0),
        axis.title.y = element_blank(), axis.title.x=element_blank()) +
  scale_fill_manual(values=statusColours) +
  labs(title = "Magpie Social engagement by user: AI topics") 

p

individual_ai_engagement_file <- here(figures_files_mastodon_dir, "individual_ai_engagement.png")
ggsave(filename = individual_ai_engagement_file,
       plot=p,device="png",
       width=30,height=24, units="cm")

```
# Still to be done

There is a lot more to do, but I've run out of time, so I will just list them.

## Condition differences

One question is whether there was more engagement from the right/left in the Right/Left conditions (i.e., did the troll accounts license more people on that side to speak out)? Seems like maybe from the figures so far but can create ones that specifically look at this better.

## Relationships to engagement

There are a lot of scatterplots to be done comparing engagement to various things (e.g., belief extremity, belief change, how much they liked it, affective polarisation, change in affective polarisation, etc). Some of these can be broken down by topic.

Also, instead of looking at overall engagement, can look at the engagement specifically received by each person (i.e., how many times their posts were favourited or reblogged or how many replies they got). Would be interesting to see if this relates to belief change, beliefs, affective polarisation, etc.

## Specific individuals

Can also see how much specific individuals were liked by others (this can be found in the `data_magpie_users` csv in the `trust` folder). How is this related to their engagement, their belief change, etc.

## Engagement over time

Aside from one figure, I haven't looked at how any of this changed over time (partly because the division into Day1, Day2, etc is so rough - it's based just on the timestamp which doesn't correspond to the 24-hour segments of the study; so to do it properly you'd have to fix that.

## Engagement with trolls

Would be interesting to see who engaged with the trolls, liked them, etc. All that information is there but I haven't done anything with it.

## More coding of conversations

Once the conversations are coded as left/right and maybe even for role in the conversation, can do much more interesting analyses relating these things to belief change, consensus perception, etc.

