---
title: "03_lm-condition-effects"
format: html
echo: false
message: false
warning:  false
---

```{r}
library(here)
library(tidyverse)
library(dotwhisker)
library(broom)
library(ggpubr)
library(brms)
library(patchwork)

source("R/visualise/colour-palettes.R")
source("R/helper-functions/lm-functions.R")

Bayesian <- TRUE
run_models <- FALSE

```

```{r}
# load before and after data separately
load(here("data/magpie/original/combined/before.Rdata"))
load(here("data/magpie/original/combined/after.Rdata"))

# load before, after, change combined data
load(here(
  "data/magpie/processed/combined/survey-before-after-change.Rdata"
))
```

# Condition Effects

Bayesian linear models examining how variables in the troll condition differed relative to the control.

```{r}


# get variable names
before_questions <- colnames(d_before)
after_questions <- colnames(d_after)

# questions asked at the end related to their overall experience
after_only_questions <- c("PropLiked",
                          "PropTrolls",
                          "PropAligned",
                          "MagpieSimilarity",
                          "OverallExperience")

# questions relating to their feelings towards republicans/democrats
change_partisan <- c(after_questions[grepl("Dem", after_questions) |
                                       grepl("Rep", after_questions)], "AffPol")


# questions pertaining to political beliefs
change_beliefs <- after_questions[grepl("Belief", after_questions) != grepl("Extreme", after_questions)]

# belief questions transformed to mark non partisan extremity
change_beliefs_extreme <- after_questions[grepl("Extreme", after_questions)]

# questions asking how politically divided they think the us is
change_consensus <- after_questions[grepl("Consensus", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_relative <- after_questions[grepl("Relative", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_trust <- after_questions[grepl("Trust", after_questions)]
change_trust <- change_trust["WVSTrust" != change_trust]

# get the number of comparisons for bonferroni adjustment
n_comparison = 17 + length(after_only_questions)
```

## Post experiment experience questions

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- after_only_questions
titles <- c(
    "A. How much did they enjoy the experience overall?",
  "B. What proportion of other users did they like?",
  "C. What proportion of accounts did they think were trolls?",
  "D. How politically aligned did they think they were with other participants?",
  "E. How similar was the experiment to normal social media?"
)
x_labs_lm <- c(
    "< 0 = enjoyed less compared to control",
  "<  0 = liked fewer other users compared to control",
  "< 0 = fewer trolls compared to control",
  "< 0 = less politicaly aligned compared to control",
  "< 0 = experience less similar compared to control"
)

x_labs_bar <- c(
    "Lower = less enjoyment",
  "Lower = liked fewer participants",
  "Lower = fewer trolls",
  "Lower = less aligned politically",
  "Lower = less similar to social media"
)

# scale data to between 0 and 1 
d_before_after_change_scale01 <- d_before_after_change %>%
  mutate(across(
    where(is.numeric) & 
      (ends_with("Before") | ends_with("After")|any_of(after_only_questions)),
    scale_to_01
  ))


d_lm <- d_before_after_change_scale01
d_bar <- d_before_after_change

p_list_survey_qs <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = FALSE,
  Bayesian = Bayesian,
  run_models = FALSE,
  ytext = FALSE
)
p_survey_qs <- ggarrange(plotlist = p_list_survey_qs,
                         ncol = 1,
                         common.legend = TRUE,
                         heights = c(2.1,1.5,1.5,1.5,1.5)
)
p_survey_qs 
file = paste0("R/visualise/plots/combined-bar-lm-post-survey-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 23, height = 22, units = "cm", plot = p_survey_qs) # roughly a4 size
```
### Did enjoyment of the platform correlate with prior beliefs in each condition? 

Enjoyment only correlated with prior beliefs in the Right condition: those with more right wing initial beliefs enjoyed the right wing condition more. 

```{r}
d_before_after_change %>%
  split(.$Condition) %>%
  map(~ cor.test(.x$BeliefBefore, .x$OverallExperience))

```
## Before/After Change variables

Bayesian linear modelling for the variables that were measured both before and after the experiment. The general structure of the models was: `Variable After ~ Variable Before + Condition`, thus essentially measuring the change in each variable by condition. 

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(change_beliefs,
                        change_consensus,
                        change_relative,
                        "TrustOverall",
                        "AffPol"
                        )
titles <- c(
  "A. Political beliefs", 
  "B. Perceptions of conesnsus",
  "C. Perceived own beliefs relative to population",
  "D. Overall trust in government and other institutions",
  "E. Affective polarisation"
)
#: 'Where would you classify your overall political beliefs, relative to most people in the US?'
#'To what extent do you think that most people in the US generally agree with each other about their overall political beliefs?'
x_labs_lm <- c(
  "< 0 = more left wing than control",
  "< 0 = less belief there is a consensus compared to control",
  "< 0 = beliefs more left wing relative to population compared to control",
  "< 0 = less trusting than control",
  "< 0 = less polarised than control"
)

x_labs_bar <- c(
  "< 0 = left wing change",
  "< 0 = reduced belief that there is a consensus",
  "< 0 = beliefs became more left wing relative to population",
  "< 0 = became less trusting",
  "< 0 = became less polarised"
)


p_list_change_vars <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  xlim = c(-0.5,0.5),
  Bayesian = Bayesian,
  run_models = run_models,
  title_size = 20,
  base_size = 17
)
p_change_vars <- ggarrange(
  plotlist = p_list_change_vars,
  ncol = 1,
  heights = c(6, 5, 5, 1.7, 1.7, 5)
)
p_change_vars
file = paste0("R/visualise/plots/combined-bar-lm-change-vars-Bayes-",Bayesian,".png")
ggsave(filename =file, width = 35, height = 45, units = "cm", plot = p_change_vars) 
```

### Full trust and affective polarisation plots

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(
  change_trust,
  change_partisan
)

titles <- c(
  "Trust Measures",
  "Affective Polarisation Measures"
)

x_labs_lm = c(
  "< 0 = trust less than control",
  "< 0 = less polarised than control"
)

x_labs_bar = c(
  "< 0 = became less trusting",
  "< 0 = became less polarised"
)

p_list_aff_trust <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  #xlim = c(-0.5,0.5),
  by_topic = FALSE,
  Bayesian = Bayesian,
  run_models = run_models
)
p_aff_trust <- ggarrange(
  plotlist = p_list_aff_trust,
  ncol = 1,
  heights = c(1,2)
)
p_aff_trust
file = paste0("R/visualise/plots/combined-bar-lm-aff-trust-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 30, height = 37, units = "cm", plot = p_aff_trust) # roughly a4 size

```

## Initial values of measures

### Change variables 

```{r}
# check priors of trust measures 
d_before %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = c(change_beliefs, change_consensus, change_relative, change_trust, change_partisan)) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

## Experience variables
```{r}
d_after %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = after_only_questions) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

```{r}
print(paste0("Mean initial overall trust: ", round(mean(d_before$TrustOverall),2), " SD: ", round(sd(d_before$TrustOverall))))
```

# Predicting changes in measures as a function of the types of posts seen

We were also able to collect data on the exact posts that people saw. This can provide insight into what it was that affected participants' experiences and was shifting people's beliefs and perceptions of consensus in the troll conditions. 

## Comparing sample characteristics for full sample versus sample with posts seen data available

Unfortunately, we were unable to collect posts seen data for all participants. So we wanted to check to make sure that the sample with and without posts seen were similar. 


```{r}

load(here("data/magpie/processed/combined/posts-seen-by-user.Rdata"))

d_seen_by_troll <- unique_posts_seen_by_user %>%
  # Join the troll-only proportions
  left_join(
    unique_posts_seen_by_user_nontroll %>% 
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_troll = prop_right,
             prop_left_troll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Join the non-troll proportions
  left_join(
    unique_posts_seen_by_user_troll %>% 
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_nontroll = prop_right,
             prop_left_nontroll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Rename the all-posts proportions for clarity
  rename(
    prop_right_all = prop_right,
    prop_left_all = prop_left
  ) %>%
  # Replace NAs with 0 (participants who saw no troll/non-troll content)
  mutate(
    prop_right_troll = replace_na(prop_right_troll, 0),
    prop_left_troll = replace_na(prop_left_troll, 0),
    prop_right_nontroll = replace_na(prop_right_nontroll, 0),
    prop_left_nontroll = replace_na(prop_left_nontroll, 0)
  )


d_survey_seen_by_troll <- d_before_after_change_scale01 %>%
  left_join(
    d_seen_by_troll,
    by = c(UserName = "username", "Condition")
  )

print(paste0("Posts seen data is missing for ", sum(is.na(d_survey_seen_by_troll$prop_left_nontroll)), " participants total"))
print("Breakdown by condition: ")
# check number of missing in each condition
d_survey_seen_by_troll %>%
  group_by(Condition) %>%
  summarise(Missing = sum(is.na(prop_right_all)))

summarise_vars = function(data) {
  data %>%
    summarise(
      m_beliefs    = mean(BeliefBefore, na.rm = TRUE),
      sd_beliefs   = sd(BeliefBefore, na.rm = TRUE),
      m_polID      = mean(PoliticalIDNum, na.rm = TRUE),
      sd_polID     = sd(PoliticalIDNum, na.rm = TRUE),
      m_extreme    = mean(ExtremeBeliefBefore, na.rm = TRUE),
      sd_extreme   = sd(ExtremeBeliefBefore, na.rm = TRUE),
      m_consensus  = mean(ConsensusPoliticsBefore, na.rm = TRUE),
      sd_consensus = sd(ConsensusPoliticsBefore, na.rm = TRUE),
      m_age        = mean(Age, na.rm = TRUE),
      sd_age       = sd(Age, na.rm = TRUE)
    )
}

base_data <- d_survey_seen_by_troll %>% filter(Condition != "Control")

summary_stats <- bind_rows(
  base_data %>% summarise_vars() %>% mutate(group = "Full Sample"),
  base_data %>% filter(!is.na(prop_right_all)) %>% summarise_vars() %>% mutate(group = "Posts Seen Data Available")
)

# Pivot to long format for plotting
summary_long <- summary_stats %>%
  pivot_longer(
    cols = -group,
    names_to = c(".value", "variable"),
    names_pattern = "(m|sd)_(.*)"
  )

# Bar graph
ggplot(summary_long, aes(x = group, y = m, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = m - sd, ymax = m + sd),
    position = position_dodge(width = 0.8),
    width = 0.25
  ) +
  facet_wrap(~ variable, scales = "free_y", labeller = labeller(variable = c(
    "beliefs"   = "Belief Before",
    "polID"     = "Political ID Before",
    "extreme"   = "Extremity of Beliefs Before",
    "consensus" = "Perceptions of Consensus Before",
    "age"       = "Age"
  ))) +
  labs(
    title = "Comparison of Variables by Posts Seen Data Availability",
    x     = NULL,
    y     = "Mean (Scaled except for age and Political ID)",
    fill  = "Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank()
  )
  

```

```{r}
d_survey_seen_by_troll %>%
  group_by(Condition) %>%
  summarise(
    var_troll     = var(prop_right_troll + prop_left_troll, na.rm = TRUE),
    mean_troll    = mean(prop_right_troll + prop_left_troll, na.rm = TRUE),
    var_nontroll  = var(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    mean_nontroll = mean(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    var_all       = var(prop_right_all + prop_left_all, na.rm = TRUE),
    mean_all      = mean(prop_right_all + prop_left_all, na.rm = TRUE)
  )
```

## What impact does seeing troll-initated content have on our measures? And how does this compare to condition effects? 

We tested whether changes in each measure could be predicted by the type of content people saw: the proportion of friendly content, right-wing content, left-wing content, or both. As a baseline, we included a model based solely on participants' assigned condition.

We then repeated this analysis excluding content from troll-initiated conversations (defined as troll posts and any participant replies to those posts), to test whether the overall shift in discourse predicted outcomes above and beyond direct troll influence. Because troll posts were absent from the control condition by design, this analysis was restricted to participants in the \textsc{Left} and \textsc{Right} conditions. Troll-initiated content accounted for approximately 16% of posts seen by users in these conditions.

To compare the relative importance of each predictor, we computed pseudo-Bayesian model averaging (PseudoBMA) weights, which assign weights to models proportional to their estimated out-of-sample predictive accuracy via leave-one-out cross-validation (LOO-CV). Higher weights indicate greater support for that predictor; if weights are clustered near the dashed chance line, all predictors perform similarly. We focus specifically on how content-based predictors (``Right'', ``Left'', ``Right $+$ Left'', ``Friendly'') compared to condition assignment, and how this pattern changed when troll-initiated content was excluded. This analysis was not conducted for relative belief or affective polarisation measures, as these showed no credible condition effects.



```{r}
plotWeightsComparison = function(outcomes, title = NULL) {
  load(here(paste0("R/analyse/lm-output/posts-seen/weights/", outcomes, ".rdata")))
  
  prep_weights = function(results, name) {
    results$weights %>%
      mutate(
        weight     = as.numeric(weight),
        comparison = name,
        predictor  = case_when(
          predictors == "Condition"                                ~ "Condition",
          predictors == "prop_right_all"                           ~ "Right",
          predictors == "prop_left_all"                            ~ "Left",
          predictors == "prop_right_all + prop_left_all"           ~ "Left + Right",
          predictors == "prop_right_nontroll"                      ~ "Right",
          predictors == "prop_left_nontroll"                       ~ "Left",
          predictors == "prop_right_nontroll + prop_left_nontroll" ~ "Left + Right",
          predictors == "prop_friendly_all"                        ~ "Friendly"
        ),
        predictor = factor(predictor, levels = c(
          "Condition", "Right", "Left", "Left + Right", "Friendly"
        ))
      )
  }
  
  combined_results <- bind_rows(
    prep_weights(results_all,      "All Content"),
    prep_weights(results_nontroll, "Non-Troll Initiated Content")
  ) %>%
      mutate(comparison = factor(comparison, levels = c("All Content", "Non-Troll Initiated Content")))
  
  
   # Strip the variable names to their core topic so that the order can be aligned with the coeffient plots
  keywords <- c("AI", "Trans", "Climate", "Israel")
  
  # check if this is a variable that needs to be broken down by topic (keyword)
  if (any(str_extract(combined_results$variable, paste(keywords, collapse = "|")) %in% keywords)) {
    combined_results <- combined_results %>%
      mutate(
        variable = str_extract(variable, paste(keywords, collapse = "|")),
        variable = if_else(is.na(variable), "Overall", variable),
        variable = factor(variable, levels = rev(c(
          keywords, "Overall"
        )))
      )
  }
  
  
  
  plot <- combined_results %>%
    ggplot(aes(x = weight, y = variable, colour = predictor, shape = predictor)) +
    geom_vline(xintercept = 1/5, linetype = "dashed", colour = "grey70") +
    geom_point(size = 3, position = position_dodge(width = 0.5)) +
    scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
    scale_colour_brewer(palette = "Set2") +
    facet_wrap(~ comparison) +
    labs(
      x      = "Model Weight",
      y      = NULL,
      colour = "Predictor",
      shape  = "Predictor",
      title = title
    ) +
    theme_minimal(base_size = 16) +
    theme(
      panel.grid.minor = element_blank(),
      strip.text       = element_text(face = "bold"),
      legend.position = "top",
      title = element_text(face = "bold")
    )
  
  if (length(unique(combined_results$variable)) == 1){
    plot <- plot +
      theme(axis.text.y = element_blank())
  }
  
  list(plot, 
       combined_results)
}

p_beliefs_seen <- plotWeightsComparison("change_beliefs", title = "A. Political Beliefs")
p_beliefs_seen[[1]]
```

Below shows the coefficients of the models shown in the plot above, so that we can interpret the directions of the effects. 

```{r}
loadFixedEffects = function(outcomes,
                            save_dir = "R/analyse/lm-output/posts-seen/") {
  
  load(here(paste0(save_dir, "weights/", outcomes, ".rdata")))
  
  bind_rows(
    results_all$fixef      %>% mutate(comparison = "All Content"),
    results_nontroll$fixef %>% mutate(comparison = "Non-Troll Content")
  ) %>%
    filter(term != "Intercept") %>%
    mutate(
      predictor = case_when(
        predictors == "Condition"                                ~ "Condition",
        predictors == "prop_right_all"                           ~ "Right",
        predictors == "prop_left_all"                            ~ "Left",
        predictors == "prop_right_all + prop_left_all"           ~ "Left + Right",
        predictors == "prop_right_nontroll"                      ~ "Right",
        predictors == "prop_left_nontroll"                       ~ "Left",
        predictors == "prop_right_nontroll + prop_left_nontroll" ~ "Left + Right",
        predictors == "prop_friendly_all"                        ~ "Friendly"
      ),
      credible = sign(Q2.5) == sign(Q97.5)
    ) %>%
    select(variable, term, Estimate, Q2.5, Q97.5) %>%
    arrange(variable, term)
}

# check strength direction of specific predictors 

# right did well for most of the beliefs except AI
loadFixedEffects("change_beliefs") %>% 
  filter(
    grepl("prop_right", term),
    !grepl("Before", term),
    variable != "BeliefAI"
  )

# left did well for AI
loadFixedEffects("change_beliefs") %>% 
  filter(
    grepl("prop_left", term),
    !grepl("Before", term),
    variable == "BeliefAI"
  )
```
```{r}
p_consensus_seen <- plotWeightsComparison("change_consensus", title = "B. Perceptions of Consensus")
p_consensus_seen[[1]]
```
```{r}
loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("prop_right", term),
    !grepl("Before", term),
    variable %in% c("ConsensusClimate", "ConsensusIsrael", "ConsensusPolitics")
  )

loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("prop_left_all", term),
    !grepl("Before", term),
    variable %in% c("ConsensusAI", "ConsensusTrans")
  )

loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("prop_right_nontroll", term),
    !grepl("Before", term),
    variable %in% c("ConsensusClimate", "ConsensusPolitics")
  )

loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("friendly_nontroll", term),
    !grepl("Before", term),
    variable %in% c("ConsensusAI", "ConsensusTrans", "ConsensusIsrael")
  )
```


```{r}
p_trust_seen <-  plotWeightsComparison("change_trust")
p_trust_seen[[1]]
```

```{r}
loadFixedEffects("change_trust") %>% 
  filter(
    grepl("friendly", term),
    !grepl("Before", term),
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustMedia")
  )

loadFixedEffects("change_trust") %>% 
  filter(
    grepl("prop_left", term),
    !grepl("Before", term),
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustPeople")
  )

loadFixedEffects("change_trust") %>% 
  filter(
    grepl("prop_right", term),
    !grepl("Before", term),
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustGovt")
  )
```


```{r}
p_experience_seen <- plotWeightsComparison("after_only_questions")
p_experience_seen[[1]]
```

```{r}
loadFixedEffects("after_only_questions") %>% 
  filter(
    grepl("friendly", term),
    !grepl("Before", term)
    #,comparison == "Non-Troll Content",
   # variable %in% c("TrustGovt")
  )
```

Belief changes were best predicted by the troll condition, not by any broader norms of conversation that may have been induced by the trolls. 

```{r}
p_beliefs_seen    <- p_beliefs_seen[[1]]
p_consensus_seen  <- p_consensus_seen[[1]]
p_trust_seen      <- plotWeightsComparison("trust_overall",      title = "C. Overall trust")[[1]]
p_experience_seen <- plotWeightsComparison("overall_experience", title = "D. Overall experience")[[1]]
p_liked_seen      <- plotWeightsComparison("prop_liked",         title = "E. Proportion of users liked")[[1]]
p_trolls_seen     <- plotWeightsComparison("prop_trolls",        title = "F. Proportion perceived as trolls")[[1]]
p_aligned_seen    <- plotWeightsComparison("prop_aligned",       title = "G. Perceived political alignment")[[1]]
p_similarity_seen <- plotWeightsComparison("magpie_similarity",  title = "H. Similarity to real social media")[[1]]

col_left <- (p_beliefs_seen / p_consensus_seen) +
  plot_layout(heights = c(1, 1))

col_right <- (p_trust_seen / p_experience_seen / p_liked_seen / p_trolls_seen / p_aligned_seen / p_similarity_seen) +
  plot_layout(heights = c(1, 1, 1, 1, 1, 1))

combined_seen_plot <- (col_left | col_right) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

ggsave(
  plot     = combined_seen_plot,
  filename = here("R/visualise/plots/combined-seen-plot.png"),
  width    = 30, height = 35, units = "cm"
)
```
