---
title: "03_lm-condition-effects"
format: html
echo: false
message: false
warning:  false
---

```{r}
library(here)
library(tidyverse)
library(dotwhisker)
library(broom)
library(ggpubr)
library(brms)
library(patchwork)

source("R/visualise/colour-palettes.R")
source("R/helper-functions/lm-functions.R")

Bayesian <- TRUE
run_models <- FALSE

```

```{r}
# load before and after data separately
load(here("data/magpie/original/combined/before.Rdata"))
load(here("data/magpie/original/combined/after.Rdata"))

# load before, after, change combined data
load(here(
  "data/magpie/processed/combined/survey-before-after-change.Rdata"
))
```

# Condition Effects

Bayesian linear models examining how variables in the troll condition differed relative to the control.

```{r}


# get variable names
before_questions <- colnames(d_before)
after_questions <- colnames(d_after)

# questions asked at the end related to their overall experience
after_only_questions <- c("PropLiked",
                          "PropTrolls",
                          "PropAligned",
                          "MagpieSimilarity",
                          "OverallExperience")

# questions relating to their feelings towards republicans/democrats
change_partisan <- c(after_questions[grepl("Dem", after_questions) |
                                       grepl("Rep", after_questions)], "AffPol")


# questions pertaining to political beliefs
change_beliefs <- after_questions[grepl("Belief", after_questions) != grepl("Extreme", after_questions)]

# belief questions transformed to mark non partisan extremity
change_beliefs_extreme <- after_questions[grepl("Extreme", after_questions)]

# questions asking how politically divided they think the us is
change_consensus <- after_questions[grepl("Consensus", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_relative <- after_questions[grepl("Relative", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_trust <- after_questions[grepl("Trust", after_questions)]
change_trust <- change_trust["WVSTrust" != change_trust]

# get the number of comparisons for bonferroni adjustment
n_comparison = 17 + length(after_only_questions)
```

## Post experiment experience questions

```{r}
#| fig.width: 13
#| fig.height: 15
# Andy adds hack here to put in the right order
after_only_questions <- c("OverallExperience","PropLiked","PropTrolls",
                          "PropAligned","MagpieSimilarity")

variable_groups <- after_only_questions



titles <- c(
    "A. How much did they enjoy the experience overall?",
      "B. What proportion of other users did they like?",
  "C. What proportion of accounts did they think were trolls?",
      "D. How politically aligned did they think they were with other participants?",
  "E. How similar was the experiment to normal social media?"
)
x_labs_lm <- c(
    "< 0 = enjoyed less compared to control",
   "<  0 = liked fewer other users compared to control",
  "< 0 = fewer trolls compared to control",
   "< 0 = less politicaly aligned compared to control",
  "< 0 = experience less similar compared to control"
)

x_labs_bar <- c(
    "lower = less enjoyment",
       "lower = liked fewer participants",
  "lower = fewer trolls",
      "lower = less aligned politically",
  "lower = less similar to social media"
)

# scale data to between 0 and 1 
d_before_after_change_scale01 <- d_before_after_change %>%
  mutate(across(
    where(is.numeric) & 
      (ends_with("Before") | ends_with("After")|any_of(after_only_questions)),
    scale_to_01
  ))


d_lm <- d_before_after_change_scale01
d_bar <- d_before_after_change

p_list_survey_qs <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = FALSE,
  Bayesian = Bayesian,
  run_models = FALSE,
  ytext = FALSE
)
p_survey_qs <- ggarrange(plotlist = p_list_survey_qs,
                         ncol = 1,
                         common.legend = TRUE,
                         heights = c(2.1,1.5,1.5,1.5,1.5)
)
p_survey_qs 
file = paste0("R/visualise/plots/combined-bar-lm-post-survey-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 23, height = 22, units = "cm", plot = p_survey_qs) # roughly a4 size
```
### Did enjoyment of the platform correlate with prior beliefs in each condition? 

Enjoyment only correlated with prior beliefs in the Right condition: those with more right wing initial beliefs enjoyed the right wing condition more. 

```{r}
d_before_after_change %>%
  split(.$Condition) %>%
  map(~ cor.test(.x$BeliefBefore, .x$OverallExperience))

```
## Before/After Change variables

Bayesian linear modelling for the variables that were measured both before and after the experiment. The general structure of the models was: `Variable After ~ Variable Before + Condition`, thus essentially measuring the change in each variable by condition. 

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(change_beliefs,
                        change_consensus,
                        #change_relative,
                        "RelativePolitics",
                        "TrustOverall",
                        "AffPol"
                        )
titles <- c(
  "A. Political beliefs", 
  "B. Perceptions of consensus",
  "C. Perceived own beliefs relative to population",
  "D. Overall trust in government and other institutions",
  "E. Affective polarisation"
)
#: 'Where would you classify your overall political beliefs, relative to most people in the US?'
#'To what extent do you think that most people in the US generally agree with each other about their overall political beliefs?'
x_labs_lm <- c(
  "< 0 = beliefs more left wing than control",
  "< 0 = less belief in consensus than control",
  "< 0 = perceive beliefs more left wing than control",
  "< 0 = less trusting than control",
  "< 0 = less affectively polarised than control"
)

x_labs_bar <- c(
  "< 0 = beliefs more left wing than before",
  "< 0 = less belief in consensus than before",
  "< 0 = perceive beliefs more left wing than before",
  "< 0 = less trusting than before",
  "< 0 = less affective polarisation than before"
)


p_list_change_vars <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  xlim = c(-0.5,0.5),
  Bayesian = Bayesian,
  run_models = run_models,
  title_size = 20,
  base_size = 17
)
p_change_vars <- ggarrange(
  plotlist = p_list_change_vars,
  ncol = 1,
  heights = c(6, 5, 1.7, 1.7, 1.7, 5)
)
p_change_vars
file = paste0("R/visualise/plots/combined-bar-lm-change-vars-Bayes-",Bayesian,".png")
ggsave(filename =file, width = 35, height = 45, units = "cm", plot = p_change_vars) 
```

### Full trust, affective polarisation, and relative belief breakdowns

The by-subscale breakdowns of the trust, affective polarisation, and relative
belief measures are reported in the Supplementary Materials
(`04_supplementary-materials.qmd`). Only the aggregate `TrustOverall`, `AffPol`,
and `RelativePolitics` measures appear in the main-text figures, so the
subscale-level plots are kept with the other supplementary analyses.

## Initial values of measures

### Change variables 

```{r}
# check priors of trust measures 
d_before %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = c(change_beliefs, change_consensus, change_relative, change_trust, change_partisan)) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

## Experience variables
```{r}
d_after %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = after_only_questions) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

```{r}
print(paste0("Mean initial overall trust: ", round(mean(d_before$TrustOverall),2), " SD: ", round(sd(d_before$TrustOverall))))
```

# Predicting changes in measures as a function of the types of posts seen

We were also able to collect data on the exact posts that people saw. This can provide insight into what it was that affected participants' experiences and was shifting people's beliefs and perceptions of consensus in the troll conditions. 

## Comparing sample characteristics for full sample versus sample with posts seen data available

Because posts-seen data could not be collected for every participant, we checked
that the sub-sample with posts-seen data did not differ from the full sample.
This comparison is reported in the Supplementary Materials
(`04_supplementary-materials.qmd`).

## What impact does seeing troll-initated content have on our measures? And how does this compare to condition effects? 
We tested whether changes in each measure could be predicted by the type of content people saw: the proportion of friendly content, right-wing content or left-wing content.

We then repeated this analysis excluding content from troll-initiated conversations (defined as troll posts and any participant replies to those posts), to test whether the overall shift in discourse predicted outcomes above and beyond direct troll influence. Because troll posts were absent from the control condition by design, this analysis was restricted to participants in the \textsc{Left} and \textsc{Right} conditions. Troll-initiated content accounted for approximately 16% of posts seen by users in these conditions.

The Figure below shows the posterior coefficients for each content-based predictor (``Right'', ``Left", ``Friendly'') across all outcome measures, comparing models fitted on all content to models fitted on non-troll-initiated content only. Each model also included the corresponding before-measurement as a covariate, so coefficients reflect change in each measure rather than absolute levels. Points that are transparent indicate credible intervals that overlap zero. This analysis was not conducted for relative belief or affective polarisation measures, as these showed no credible condition effects.


```{r}
# The grid-plotting functions (make_coef_panel, assemble_grid,
# plotCoefficientsGrid, plotCorrelationsGrid) live in a shared script so that
# both this document and 04_supplementary-materials.qmd can use them.
source(here("R/visualise/functions/posts-seen-grid-plots.R"))

run_label = "_visibility50"

# Main figure (Figure 5) — coefficient grid using overall trust
p_coef_grid <- plotCoefficientsGrid(run_label = run_label, trust_type = "overall")
ggsave(plot = p_coef_grid, filename=here(paste0("R/visualise/plots/posts-seen-coefficients-grid",run_label,".png")),
       width = 14, height = 18, units = "cm", scale = 2)
p_coef_grid

# The supplementary variants of this figure — the trust-subscale coefficient
# grid and the correlation-based grids — are produced in
# 04_supplementary-materials.qmd.
```

