---
title: "03_lm-condition-effects"
format: html
echo: false
message: false
warning:  false
---

```{r}
library(here)
library(tidyverse)
library(dotwhisker)
library(broom)
library(ggpubr)
library(brms)
library(patchwork)

source("R/visualise/colour-palettes.R")
source("R/helper-functions/lm-functions.R")

Bayesian <- TRUE
run_models <- FALSE

```

```{r}
# load before and after data separately
load(here("data/magpie/original/combined/before.Rdata"))
load(here("data/magpie/original/combined/after.Rdata"))

# load before, after, change combined data
load(here(
  "data/magpie/processed/combined/survey-before-after-change.Rdata"
))
```

# Condition Effects

Bayesian linear models examining how variables in the troll condition differed relative to the control.

```{r}


# get variable names
before_questions <- colnames(d_before)
after_questions <- colnames(d_after)

# questions asked at the end related to their overall experience
after_only_questions <- c("PropLiked",
                          "PropTrolls",
                          "PropAligned",
                          "MagpieSimilarity",
                          "OverallExperience")

# questions relating to their feelings towards republicans/democrats
change_partisan <- c(after_questions[grepl("Dem", after_questions) |
                                       grepl("Rep", after_questions)], "AffPol")


# questions pertaining to political beliefs
change_beliefs <- after_questions[grepl("Belief", after_questions) != grepl("Extreme", after_questions)]

# belief questions transformed to mark non partisan extremity
change_beliefs_extreme <- after_questions[grepl("Extreme", after_questions)]

# questions asking how politically divided they think the us is
change_consensus <- after_questions[grepl("Consensus", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_relative <- after_questions[grepl("Relative", after_questions)]

# questions asking how extreme their own beliefs are relative to the population
change_trust <- after_questions[grepl("Trust", after_questions)]
change_trust <- change_trust["WVSTrust" != change_trust]

# get the number of comparisons for bonferroni adjustment
n_comparison = 17 + length(after_only_questions)
```

## Post experiment experience questions

```{r}
#| fig.width: 13
#| fig.height: 15
# Andy adds hack here to put in the right order
after_only_questions <- c("OverallExperience","PropLiked","PropTrolls",
                          "PropAligned","MagpieSimilarity")

variable_groups <- after_only_questions



titles <- c(
    "A. How much did they enjoy the experience overall?",
      "B. What proportion of other users did they like?",
  "C. What proportion of accounts did they think were trolls?",
      "D. How politically aligned did they think they were with other participants?",
  "E. How similar was the experiment to normal social media?"
)
x_labs_lm <- c(
    "< 0 = enjoyed less compared to control",
   "<  0 = liked fewer other users compared to control",
  "< 0 = fewer trolls compared to control",
   "< 0 = less politicaly aligned compared to control",
  "< 0 = experience less similar compared to control"
)

x_labs_bar <- c(
    "lower = less enjoyment",
       "lower = liked fewer participants",
  "lower = fewer trolls",
      "lower = less aligned politically",
  "lower = less similar to social media"
)

# scale data to between 0 and 1 
d_before_after_change_scale01 <- d_before_after_change %>%
  mutate(across(
    where(is.numeric) & 
      (ends_with("Before") | ends_with("After")|any_of(after_only_questions)),
    scale_to_01
  ))


d_lm <- d_before_after_change_scale01
d_bar <- d_before_after_change

p_list_survey_qs <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = FALSE,
  Bayesian = Bayesian,
  run_models = FALSE,
  ytext = FALSE
)
p_survey_qs <- ggarrange(plotlist = p_list_survey_qs,
                         ncol = 1,
                         common.legend = TRUE,
                         heights = c(2.1,1.5,1.5,1.5,1.5)
)
p_survey_qs 
file = paste0("R/visualise/plots/combined-bar-lm-post-survey-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 23, height = 22, units = "cm", plot = p_survey_qs) # roughly a4 size
```
### Did enjoyment of the platform correlate with prior beliefs in each condition? 

Enjoyment only correlated with prior beliefs in the Right condition: those with more right wing initial beliefs enjoyed the right wing condition more. 

```{r}
d_before_after_change %>%
  split(.$Condition) %>%
  map(~ cor.test(.x$BeliefBefore, .x$OverallExperience))

```
## Before/After Change variables

Bayesian linear modelling for the variables that were measured both before and after the experiment. The general structure of the models was: `Variable After ~ Variable Before + Condition`, thus essentially measuring the change in each variable by condition. 

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(change_beliefs,
                        change_consensus,
                        #change_relative,
                        "RelativePolitics",
                        "TrustOverall",
                        "AffPol"
                        )
titles <- c(
  "A. Political beliefs", 
  "B. Perceptions of consensus",
  "C. Perceived own beliefs relative to population",
  "D. Overall trust in government and other institutions",
  "E. Affective polarisation"
)
#: 'Where would you classify your overall political beliefs, relative to most people in the US?'
#'To what extent do you think that most people in the US generally agree with each other about their overall political beliefs?'
x_labs_lm <- c(
  "< 0 = beliefs more left wing than control",
  "< 0 = less belief in consensus than control",
  "< 0 = perceive beliefs more left wing than control",
  "< 0 = less trusting than control",
  "< 0 = less affectively polarised than control"
)

x_labs_bar <- c(
  "< 0 = beliefs more left wing than before",
  "< 0 = less belief in consensus than before",
  "< 0 = perceive beliefs more left wing than before",
  "< 0 = less trusting than before",
  "< 0 = less affective polarisation than before"
)


p_list_change_vars <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  xlim = c(-0.5,0.5),
  Bayesian = Bayesian,
  run_models = run_models,
  title_size = 20,
  base_size = 17
)
p_change_vars <- ggarrange(
  plotlist = p_list_change_vars,
  ncol = 1,
  heights = c(6, 5, 1.7, 1.7, 1.7, 5)
)
p_change_vars
file = paste0("R/visualise/plots/combined-bar-lm-change-vars-Bayes-",Bayesian,".png")
ggsave(filename =file, width = 35, height = 45, units = "cm", plot = p_change_vars) 
```

### Full trust and affective polarisation plots

```{r}
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(
  change_trust,
  change_partisan
)

titles <- c(
  "Trust Measures",
  "Affective Polarisation Measures"
)

x_labs_lm = c(
  "< 0 = trust less than control",
  "< 0 = less polarised than control"
)

x_labs_bar = c(
  "< 0 = became less trusting",
  "< 0 = became less polarised"
)

p_list_aff_trust <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  #xlim = c(-0.5,0.5),
  by_topic = FALSE,
  Bayesian = Bayesian,
  run_models = run_models
)
p_aff_trust <- ggarrange(
  plotlist = p_list_aff_trust,
  ncol = 1,
  heights = c(1,2)
)
p_aff_trust
file = paste0("R/visualise/plots/combined-bar-lm-aff-trust-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 30, height = 37, units = "cm", plot = p_aff_trust) # roughly a4 size

```

### Full relative belief plots 

```{r}
#| fig.width: 13
#| fig.height: 8
variable_groups <- list(
  change_relative
)

titles <- c(
  "Perceived own beliefs relative to population, by topic"
)

x_labs_lm = c(
  "< 0 = perceive beliefs more left wing than control"
)

x_labs_bar = c(
  "< 0 = perceive beliefs more left wing than before"
)

p_list_aff_trust <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  #xlim = c(-0.5,0.5),
  by_topic = FALSE,
  Bayesian = Bayesian,
  run_models = run_models
)
p_aff_trust <- ggarrange(
  plotlist = p_list_aff_trust,
  ncol = 1,
  heights = c(1,2)
)
p_aff_trust
file = paste0("R/visualise/plots/combined-bar-lm-relative-Bayes-",Bayesian,".png")
ggsave(filename = file, width = 30, height = 37, units = "cm", plot = p_aff_trust) # roughly a4 size
```


## Initial values of measures

### Change variables 

```{r}
# check priors of trust measures 
d_before %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = c(change_beliefs, change_consensus, change_relative, change_trust, change_partisan)) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

## Experience variables
```{r}
d_after %>%
  pivot_longer(values_to = "Value", names_to = "Variable", cols = after_only_questions) %>%
  group_by(Variable) %>%
  summarise(Mean = round(mean(Value),2), SD = round(sd(Value),2))
```

```{r}
print(paste0("Mean initial overall trust: ", round(mean(d_before$TrustOverall),2), " SD: ", round(sd(d_before$TrustOverall))))
```

# Predicting changes in measures as a function of the types of posts seen

We were also able to collect data on the exact posts that people saw. This can provide insight into what it was that affected participants' experiences and was shifting people's beliefs and perceptions of consensus in the troll conditions. 

## Comparing sample characteristics for full sample versus sample with posts seen data available

Unfortunately, we were unable to collect posts seen data for all participants. So we wanted to check to make sure that the sample with and without posts seen were similar. 


```{r}

load(here("data/magpie/processed/combined/posts-seen-by-user.Rdata"))

d_seen_by_troll <- unique_posts_seen_by_user %>%
  # Join the troll-only proportions
  left_join(
    unique_posts_seen_by_user_nontroll %>% 
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_troll = prop_right,
             prop_left_troll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Join the non-troll proportions
  left_join(
    unique_posts_seen_by_user_troll %>% 
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_nontroll = prop_right,
             prop_left_nontroll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Rename the all-posts proportions for clarity
  rename(
    prop_right_all = prop_right,
    prop_left_all = prop_left
  ) %>%
  # Replace NAs with 0 (participants who saw no troll/non-troll content)
  mutate(
    prop_right_troll = replace_na(prop_right_troll, 0),
    prop_left_troll = replace_na(prop_left_troll, 0),
    prop_right_nontroll = replace_na(prop_right_nontroll, 0),
    prop_left_nontroll = replace_na(prop_left_nontroll, 0)
  )


d_survey_seen_by_troll <- d_before_after_change_scale01 %>%
  left_join(
    d_seen_by_troll,
    by = c(UserName = "username", "Condition")
  )

print(paste0("Posts seen data is missing for ", sum(is.na(d_survey_seen_by_troll$prop_left_nontroll)), " participants total"))
print("Breakdown by condition: ")
# check number of missing in each condition
d_survey_seen_by_troll %>%
  group_by(Condition) %>%
  summarise(Missing = sum(is.na(prop_right_all)))

summarise_vars = function(data) {
  data %>%
    summarise(
      m_beliefs    = mean(BeliefBefore, na.rm = TRUE),
      sd_beliefs   = sd(BeliefBefore, na.rm = TRUE),
      m_polID      = mean(PoliticalIDNum, na.rm = TRUE),
      sd_polID     = sd(PoliticalIDNum, na.rm = TRUE),
      m_extreme    = mean(ExtremeBeliefBefore, na.rm = TRUE),
      sd_extreme   = sd(ExtremeBeliefBefore, na.rm = TRUE),
      m_consensus  = mean(ConsensusPoliticsBefore, na.rm = TRUE),
      sd_consensus = sd(ConsensusPoliticsBefore, na.rm = TRUE),
      m_age        = mean(Age, na.rm = TRUE),
      sd_age       = sd(Age, na.rm = TRUE)
    )
}

base_data <- d_survey_seen_by_troll %>% filter(Condition != "Control")

summary_stats <- bind_rows(
  base_data %>% summarise_vars() %>% mutate(group = "Full Sample"),
  base_data %>% filter(!is.na(prop_right_all)) %>% summarise_vars() %>% mutate(group = "Posts Seen Data Available")
)

# Pivot to long format for plotting
summary_long <- summary_stats %>%
  pivot_longer(
    cols = -group,
    names_to = c(".value", "variable"),
    names_pattern = "(m|sd)_(.*)"
  )

# Bar graph
ggplot(summary_long, aes(x = group, y = m, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = m - sd, ymax = m + sd),
    position = position_dodge(width = 0.8),
    width = 0.25
  ) +
  facet_wrap(~ variable, scales = "free_y", labeller = labeller(variable = c(
    "beliefs"   = "Belief Before",
    "polID"     = "Political ID Before",
    "extreme"   = "Extremity of Beliefs Before",
    "consensus" = "Perceptions of Consensus Before",
    "age"       = "Age"
  ))) +
  labs(
    title = "Comparison of Variables by Posts Seen Data Availability",
    x     = NULL,
    y     = "Mean (Scaled except for age and Political ID)",
    fill  = "Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank()
  )
  

```

```{r}
d_survey_seen_by_troll %>%
  group_by(Condition) %>%
  summarise(
    var_troll     = var(prop_right_troll + prop_left_troll, na.rm = TRUE),
    mean_troll    = mean(prop_right_troll + prop_left_troll, na.rm = TRUE),
    var_nontroll  = var(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    mean_nontroll = mean(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    var_all       = var(prop_right_all + prop_left_all, na.rm = TRUE),
    mean_all      = mean(prop_right_all + prop_left_all, na.rm = TRUE)
  )
```

## What impact does seeing troll-initated content have on our measures? And how does this compare to condition effects? 

We tested whether changes in each measure could be predicted by the type of content people saw: the proportion of friendly content, right-wing content, left-wing content, or both. As a baseline, we included a model based solely on participants' assigned condition.

We then repeated this analysis excluding content from troll-initiated conversations (defined as troll posts and any participant replies to those posts), to test whether the overall shift in discourse predicted outcomes above and beyond direct troll influence. Because troll posts were absent from the control condition by design, this analysis was restricted to participants in the \textsc{Left} and \textsc{Right} conditions. Troll-initiated content accounted for approximately 16% of posts seen by users in these conditions.

To compare the relative importance of each predictor, we computed pseudo-Bayesian model averaging (PseudoBMA) weights, which assign weights to models proportional to their estimated out-of-sample predictive accuracy via leave-one-out cross-validation (LOO-CV). Higher weights indicate greater support for that predictor; if weights are clustered near the dashed chance line, all predictors perform similarly. We focus specifically on how content-based predictors (``Right'', ``Left'', ``Right $+$ Left'', ``Friendly'') compared to condition assignment, and how this pattern changed when troll-initiated content was excluded. This analysis was not conducted for relative belief or affective polarisation measures, as these showed no credible condition effects.



```{r}
plotWeightsComparison = function(outcomes, title = NULL, run_label = NULL) {
  load(here(paste0("R/analyse/lm-output/posts-seen/weights/", outcomes, run_label, ".rdata")))
  
  prep_weights = function(results, name) {
    results$weights %>%
      mutate(
        weight     = as.numeric(weight),
        comparison = name,
        predictor  = case_when(
          predictors == "Condition"                                ~ "Condition",
          predictors == "prop_right_all"                           ~ "Right",
          predictors == "prop_left_all"                            ~ "Left",
          predictors == "prop_right_all + prop_left_all"           ~ "Left + Right",
          predictors == "prop_right_nontroll"                      ~ "Right",
          predictors == "prop_left_nontroll"                       ~ "Left",
          predictors == "prop_right_nontroll + prop_left_nontroll" ~ "Left + Right",
          predictors == "prop_friendly_all"                        ~ "Friendly",
          predictors == "prop_friendly_nontroll"                   ~ "Friendly"
        ),
        predictor = factor(predictor, levels = c(
          "Condition", "Right", "Left", "Left + Right", "Friendly"
        ))
      )
  }
  
  prep_compare = function(results, name) {
    results$compare %>%
      mutate(
        comparison   = name,
        # compute error bar bounds here so columns are guaranteed to exist after bind_rows
        elpd_diff_lo = elpd_diff - 1.96 * se_diff,
        elpd_diff_hi = elpd_diff + 1.96 * se_diff,
        predictor  = case_when(
          predictors == "Condition"                                ~ "Condition",
          predictors == "prop_right_all"                           ~ "Right",
          predictors == "prop_left_all"                            ~ "Left",
          predictors == "prop_right_all + prop_left_all"           ~ "Left + Right",
          predictors == "prop_right_nontroll"                      ~ "Right",
          predictors == "prop_left_nontroll"                       ~ "Left",
          predictors == "prop_right_nontroll + prop_left_nontroll" ~ "Left + Right",
          predictors == "prop_friendly_all"                        ~ "Friendly",
          predictors == "prop_friendly_nontroll"                   ~ "Friendly"
        ),
        predictor = factor(predictor, levels = c(
          "Condition", "Right", "Left", "Left + Right", "Friendly"
        ))
      )
  }
  
  # Helper to apply keyword stripping so that variable order aligns with coefficient plots
  strip_keywords = function(df) {
    keywords <- c("AI", "Trans", "Climate", "Israel")
    if (any(str_extract(df$variable, paste(keywords, collapse = "|")) %in% keywords)) {
      df <- df %>%
        mutate(
          variable = str_extract(variable, paste(keywords, collapse = "|")),
          variable = if_else(is.na(variable), "Overall", variable),
          variable = factor(variable, levels = rev(c(keywords, "Overall")))
        )
    }
    df
  }
  
  # Helper to build a plot given prepped data and plot-type-specific parameters
  make_plot = function(combined_results, x_var, xmin_var, xmax_var, x_label, vline, x_scale) {
    p <- combined_results %>%
      ggplot(aes(x = .data[[x_var]], y = variable, colour = predictor, shape = predictor)) +
      geom_vline(xintercept = vline, linetype = "dashed", colour = "grey30") +
      geom_errorbarh(
        aes(xmin = .data[[xmin_var]], xmax = .data[[xmax_var]]),
        height   = 0.2,
        position = position_dodge(width = 0.5)
      ) +
      geom_point(size = 4, position = position_dodge(width = 0.5)) +
      x_scale +
      scale_colour_manual(values = c("#339933", "#FF99CC", "#99CCFF", "#8888FF", "#CC9900")) +
      facet_wrap(~ comparison) +
      labs(
        x      = x_label,
        y      = NULL,
        colour = "Predictor",
        shape  = "Predictor",
        title  = title
      ) +
      theme_minimal() +
      theme(
        panel.grid.minor = element_blank(),
        strip.text       = element_text(face = "bold", size = 13),
        axis.title.x     = element_text(face = "plain", size = 11),
        legend.position  = "top",
        title            = element_text(face = "bold", size = 16)
      )
    
    if (length(unique(combined_results$variable)) == 1) {
      p <- p + theme(axis.text.y = element_blank())
    }
    p
  }
  
  # ---- Weights plot ----
  weights_results <- bind_rows(
    prep_weights(results_all,      "All Content"),
    prep_weights(results_nontroll, "Non-Troll Initiated Content")
  ) %>%
    mutate(comparison = factor(comparison, levels = c("All Content", "Non-Troll Initiated Content"))) %>%
    strip_keywords()
  
  plot_weights <- make_plot(
    weights_results,
    x_var    = "weight",
    xmin_var = "weight_lo",
    xmax_var = "weight_hi",
    x_label  = "Model Weight",
    vline    = 1/5,   # chance line for 5 models
    x_scale  = scale_x_continuous(labels = scales::percent, limits = c(0, 1))
  )
  
  # ---- Compare plot ----
  # Only build if compare data exists (backwards compatible with old results objects)
  plot_compare <- NULL
  compare_results <- NULL
  
  if (!is.null(results_all$compare) && !is.null(results_nontroll$compare)) {
    compare_results <- bind_rows(
      prep_compare(results_all,      "All Content"),
      prep_compare(results_nontroll, "Non-Troll Initiated Content")
    ) %>%
      mutate(comparison = factor(comparison, levels = c("All Content", "Non-Troll Initiated Content"))) %>%
      strip_keywords()
    
    plot_compare <- make_plot(
      compare_results,
      x_var    = "elpd_diff",
      xmin_var = "elpd_diff_lo",
      xmax_var = "elpd_diff_hi",
      x_label  = "ELPD Difference (relative to best model)",
      vline    = 0,    # best model is always at 0 in loo_compare
      x_scale  = scale_x_continuous()
    )
  }
  
  list(
    plot_weights         = plot_weights,
    plot_compare = plot_compare,
    data_weights         = weights_results,
    data_compare = compare_results
  )
}


# function that plots all of the variables at once so I don't need as much code 
plotWeightsComparisonAll = function(outcome_groups,
                                    titles = NULL,
                                    run_label = NULL,
                                    plot_type = "weights") # weights or compare
  {
  # titles can be a named vector (names = outcome group) or NULL
  plots <- lapply(seq_along(outcome_groups), function(i) {
    group <- outcome_groups[i]
    title <- if (!is.null(titles))
      titles[i]
    else
      NULL
    plotWeightsComparison(group, title = title, run_label = run_label)
  })
  
  # Return as named list so results can be accessed by outcome group name
  # e.g. results[["change_beliefs"]]$plot or results[["change_beliefs"]]$data
  results <- lapply(plots, function(p)
    list(plot = p[[paste0("plot_",plot_type)]], data = p[[paste0(plot_type,"_results")]]))
  names(results) <- outcome_groups
  results
}

p_beliefs_seen <- plotWeightsComparison("change_beliefs", title = "A. Political Beliefs")
p_beliefs_seen[["plot_compare"]]
```


Below shows the coefficients of the models shown in the plot above, so that we can interpret the directions of the effects. As you'd expect, the coefficients are negative for left wing posts seen, and positive for right wing posts seen. This suggests that, when we include all of the content people saw, (left hand side of the plot above) seeing left wing posts was associated with left-wing shifts, and seeing right-wing posts was associated with right-wing shifts. These effects pretty much disappeared, however, when we remove troll-initiated content. 

```{r}
loadFixedEffects = function(outcomes,
                            save_dir = "R/analyse/lm-output/posts-seen/",
                            run_label = NULL) {
  
  load(here(paste0(save_dir, "weights/", outcomes, run_label,".rdata")))
  
  bind_rows(
    results_all$fixef      %>% mutate(comparison = "All Content"),
    results_nontroll$fixef %>% mutate(comparison = "Non-Troll Content")
  ) %>%
    filter(term != "Intercept") %>%
    mutate(
      predictor = case_when(
        predictors == "Condition"                                ~ "Condition",
        predictors == "prop_right_all"                           ~ "Right",
        predictors == "prop_left_all"                            ~ "Left",
        predictors == "prop_right_all + prop_left_all"           ~ "Left + Right",
        predictors == "prop_right_nontroll"                      ~ "Right",
        predictors == "prop_left_nontroll"                       ~ "Left",
        predictors == "prop_right_nontroll + prop_left_nontroll" ~ "Left + Right",
        predictors == "prop_friendly_all"                        ~ "Friendly",
        predictors == "prop_friendly_nontroll"                    ~ "Friendly"
      ),
      credible = sign(Q2.5) == sign(Q97.5)
    ) %>%
    select(variable, term, Estimate, Q2.5, Q97.5, predictor) %>%
    arrange(variable, term)
}

# check strength direction of specific predictors 

loadFixedEffects("change_beliefs") %>% 
  filter(
    grepl("prop_right", term),
    !grepl("Before", term),
      predictor != "Left + Right",
    variable %in% c("BeliefTrans", "BeliefClimate", "BeliefOverall")
  )

loadFixedEffects("change_beliefs") %>% 
  filter(
    grepl("prop_left", term),
    !grepl("Before", term),
    predictor != "Left + Right",
    variable %in% c("BeliefAI", "BeliefIsrael", "BeliefOverall")
  )
```


```{r}
p_consensus_seen <- plotWeightsComparison("change_consensus", title = "B. Perceptions of Consensus")
p_consensus_seen[[1]]
```
The plot above suggests the amount of left wing posts seen was a strong predictor of perceptions of consensus when considering all content. The coefficients below suggest that the direction was such that seeing more left wing posts was associated with greater perceptions of consensus. The relative performance of left wing posts as a predictor diminishes substantially when we remove troll initiated content for most predictors, however it still performs above that we would expect if all models were performing similarly (dashed line) and is still the best model for two variables (AI and overall) and performance similarly to condition for the other variables.

```{r}
# loadFixedEffects("change_consensus") %>% 
#   filter(
#     grepl("prop_right", term),
#     !grepl("Before", term),
#     variable %in% c("ConsensusClimate", "ConsensusIsrael", "ConsensusPolitics")
#   )

loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("prop_left_all", term),
    !grepl("Before", term),
        predictor != "Left + Right",
    variable %in% c("ConsensusClimate", "ConsensusIsrael", "ConsensusPolitics", "ConsensusTrans")
  )

loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("prop_left_nontroll", term),
    !grepl("Before", term),
        predictor != "Left + Right",
    #variable %in% c("ConsensusClimate", "ConsensusIsrael", "ConsensusPolitics", "ConsensusTrans")
  )


loadFixedEffects("change_consensus") %>% 
  filter(
    grepl("friendly_all", term),
    !grepl("Before", term),
    variable %in% c("ConsensusAI")
  )
```


```{r}
p_trust_seen <-  plotWeightsComparison("change_trust")
p_trust_seen[[1]]
```
The amount of friendly posts seen was a very strong predictor of how much people trusted universities, with this strength persisting regardless of whether we considered troll-initiated content or not. It was also a decent predictor (though much weaker) of trust in media. According to the coefficients, this relationship was **negative**, such that seeing *more* friendly posts was associated with *less* trust in these institutions. I'm not sure what to make of this, especially for the very strong finding pertaining to universities. The only thing I can think of, since condition effects do not do very well here, is that there was some alternative discourse going on about universities, or if it is somehow related to their meta discourse about the study itself (since they knew they were participating in a university study.)

Consistent with the original model condition effects, we see that seeing more right wing posts is a good predictor of *more* trust in media (only after removing troll content), governments, and business. This makes sense for trusting businesses, but seems counter intuitive for the media and the government. The fact that these predictors got stronger *after* removing troll initiated content suggests that it is something about the broader discourse, not our specific troll accounts -- which might makes it more plausible that although it may have been right-wing discourse, it could have been less conventional right wing discourse that was shifting peoples' trust. I'm not completely sure though. 



```{r}
loadFixedEffects("change_trust") %>% 
  filter(
    grepl("friendly", term),
    !grepl("Before", term),
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustMedia", "TrustUnis")
  )

loadFixedEffects("change_trust") %>% 
  filter(
    grepl("prop_left_all", term),
    !grepl("Before", term),
    predictor != "Left + Right",
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustBusiness")
  )

loadFixedEffects("change_trust") %>% 
  filter(
    grepl("prop_right_all", term),
    !grepl("Before", term),
      predictor != "Left + Right",
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustGovt", "TrustBusiness", "TrustOverall")
  )

loadFixedEffects("change_trust") %>% 
  filter(
    grepl("prop_right_all", term),
    !grepl("Before", term),
      predictor != "Left + Right",
    #,comparison == "Non-Troll Content",
    variable %in% c("TrustGovt", "TrustBusiness", "TrustMedia")
  )
```

```{r}
p_experience_seen <- plotWeightsComparison("after_only_questions")
p_experience_seen[[1]]
```
The amount of right wing posts seen were generally the best predictors of the post survey experience questions. As shown below, seeing more right wing posts was associated with liking people less and feeling less aligned with other participants politically. Seeing more right wing posts was predicted thinking there was more troll posts, less so when removing troll initiated content (which makes sense). 

```{r}
loadFixedEffects("after_only_questions") %>% 
  filter(
    grepl("prop_right", term),
    !grepl("Before", term),
          predictor != "Left + Right",
    #,comparison == "Non-Troll Content",
    !variable %in% c("MagpieSimilarity")
  )

loadFixedEffects("after_only_questions") %>% 
  filter(
    grepl("prop_left_all", term),
    !grepl("Before", term),
          predictor != "Left + Right",
    #,comparison == "Non-Troll Content",
    variable %in% c("PropAligned", "OverallExperience")
  )

loadFixedEffects("after_only_questions") %>% 
  filter(
    grepl("friendly", term),
    !grepl("Before", term),
    #,comparison == "Non-Troll Content",
    variable %in% c("MagpieSimilarity")
  )
```

```{r}
makeCombinedSeenPlot = function(run_label = NULL,
                                plot_type = "weights",
                                filename  = "combined-seen-plot",
                                width     = 30,
                                height    = 35) {
  
  outcome_groups <- c(
    "change_beliefs",
    "change_consensus",
    "trust_overall",
    "overall_experience",
    "prop_liked",
    "prop_trolls",
    "prop_aligned",
    "magpie_similarity"
  )
  
  titles <- c(
    "A. Political Beliefs",
    "B. Perceptions of Consensus",
    "C. Overall trust",
    "D. Overall experience",
    "E. Proportion of users liked",
    "F. Proportion perceived as trolls",
    "G. Perceived political alignment",
    "H. Similarity to real social media"
  )
  
  all_plots <- plotWeightsComparisonAll(
    outcome_groups = outcome_groups,
    titles         = titles,
    run_label      = run_label,
    plot_type      = plot_type
  )
  
  p_beliefs_seen    <- all_plots[["change_beliefs"]]$plot
  p_consensus_seen  <- all_plots[["change_consensus"]]$plot
  p_trust_seen      <- all_plots[["trust_overall"]]$plot
  p_experience_seen <- all_plots[["overall_experience"]]$plot
  p_liked_seen      <- all_plots[["prop_liked"]]$plot
  p_trolls_seen     <- all_plots[["prop_trolls"]]$plot
  p_aligned_seen    <- all_plots[["prop_aligned"]]$plot
  p_similarity_seen <- all_plots[["magpie_similarity"]]$plot
  
  col_left <- (p_beliefs_seen / p_consensus_seen) +
    plot_layout(heights = c(1, 1))
  col_right <- (p_trust_seen / p_experience_seen / p_liked_seen / p_trolls_seen / p_aligned_seen / p_similarity_seen) +
    plot_layout(heights = c(1, 1, 1, 1, 1, 1))
  combined_seen_plot <- (col_left | col_right) +
    plot_layout(guides = "collect") &
    theme(legend.position = "bottom")
  
  ggsave(
    plot     = combined_seen_plot,
    filename = here(paste0("R/visualise/plots/", filename, run_label, "-", plot_type, ".png")),
    width    = width,
    height   = height,
    units    = "cm"
  )
  
  invisible(combined_seen_plot)
}

```

```{r}
# default weights plot
makeCombinedSeenPlot(run_label = NULL)

# loo_compare version
makeCombinedSeenPlot(run_label = NULL, plot_type = "compare")
```


## Re-running with only full visibility

```{r}
# default weights plot
makeCombinedSeenPlot(run_label = "_visibility100")

# loo_compare version
makeCombinedSeenPlot(run_label = "_visibility100", plot_type = "compare")
```

# Re-run with only >= 50% visibility (original criteria)

```{r}
# default weights plot
makeCombinedSeenPlot(run_label = "_visibility50")

# loo_compare version
makeCombinedSeenPlot(run_label = "_visibility50", plot_type = "compare")
```

```{r}
plotCoefficientsGrid = function(run_label = NULL, title = NULL) {

  outcome_groups <- c("change_beliefs", "change_consensus", "change_trust", "after_only_questions")

  group_to_category <- c(
    change_beliefs       = "Belief Change",
    change_consensus     = "Consensus Change",
    change_trust         = "Trust Change",
    after_only_questions = "After Only"
  )

  # Load and combine fixef from all outcome groups
  all_fixef <- map_dfr(outcome_groups, function(group) {
    load(here(paste0("R/analyse/lm-output/posts-seen/weights/", group, run_label, ".rdata")))

    bind_rows(
      results_all$fixef      %>% mutate(comparison = "All Content"),
      results_nontroll$fixef %>% mutate(comparison = "Non-Troll Content")
    ) %>%
      mutate(outcome_group = group,
             category      = group_to_category[group])
  })

  # Strip topic keywords per outcome group (mirrors strip_keywords logic)
  keywords <- c("AI", "Trans", "Climate", "Israel")

  d_plot <- all_fixef %>%
    # Drop intercept, before-covariate, condition effects, and joint Left+Right model
    filter(
      term != "Intercept",
      !grepl("Before$",    term),
      !grepl("^Condition", term),
      !predictors %in% c("Condition",
                         "prop_right_all + prop_left_all",
                         "prop_right_nontroll + prop_left_nontroll")
    ) %>%
    mutate(
      credible  = sign(Q2.5) == sign(Q97.5),
      predictor = case_when(
        predictors == "prop_right_all"      ~ "Prop. Right Seen",
        predictors == "prop_left_all"       ~ "Prop. Left Seen",
        predictors == "prop_friendly_all"   ~ "Prop. Friendly Seen",
        predictors == "prop_right_nontroll" ~ "Prop. Right Seen",
        predictors == "prop_left_nontroll"  ~ "Prop. Left Seen",
        predictors == "prop_friendly_nontroll" ~ "Prop. Friendly Seen"
      ),
      predictor  = factor(predictor,  levels = c("Prop. Right Seen", "Prop. Left Seen", "Prop. Friendly Seen")),
      comparison = factor(comparison, levels = c("All Content", "Non-Troll Content")),
      category   = factor(category,   levels = c("Belief Change", "Consensus Change",
                                                  "Trust Change", "After Only"))
    ) %>%
    # Apply keyword stripping per outcome group
    group_by(outcome_group) %>%
group_modify(function(df, key) {
  if (key$outcome_group == "change_trust") {
    df %>% mutate(
      variable = str_remove(variable, "^Trust"),
      variable = factor(variable, levels = c("Overall", "Media", "Unis", "Govt", "Business", "People"))
    )
  } else {
    extracted <- str_extract(df$variable, paste(keywords, collapse = "|"))
    if (any(extracted %in% keywords, na.rm = TRUE)) {
      df %>% mutate(
        variable = if_else(is.na(extracted), "Overall", extracted),
        variable = factor(variable, levels = rev(c(keywords, "Overall")))
      )
    } else {
      df %>% mutate(variable = factor(variable))
    }
  }
}) %>%
ungroup()

  ggplot(d_plot, aes(x = variable, y = Estimate,
                     colour = comparison, shape = comparison,
                     alpha  = credible)) +
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
    geom_pointrange(
      aes(ymin = Q2.5, ymax = Q97.5),
      position = position_dodge(width = 0.5),
      size     = 0.4
    ) +
    facet_grid(predictor ~ category, scales = "free_x", space = "free_x") +
    scale_alpha_manual(values  = c(`TRUE` = 1, `FALSE` = 0.3), guide = "none") +
    scale_colour_manual(values = c("All Content"       = "#E15759",
                                   "Non-Troll Content" = "#4E79A7")) +
    scale_shape_manual(values  = c("All Content"       = 16,
                                   "Non-Troll Content" = 17)) +
    theme_minimal(base_size = 9) +
    theme(
      axis.text.x      = element_text(angle = 45, hjust = 1, size = 7),
      strip.text.x     = element_text(size = 8, face = "bold"),
      strip.text.y     = element_text(size = 8, face = "bold"),
      legend.position  = "bottom",
      panel.spacing    = unit(0.8, "lines"),
      panel.grid.minor = element_blank()
    ) +
    labs(x = NULL, y = "Coefficient (95% CI)",
         colour = NULL, shape = NULL, title = title, subtitle = "Transparent coefficients overlap with 0")
}

# Usage
p_coef_grid <- plotCoefficientsGrid(run_label = "_visibility50", title = "Model coefficient estimates: All vs Non-Troll Content")
ggsave(plot = p_coef_grid,
       filename = here("R/visualise/plots/coefficients-grid.png"),
       width = 14, height = 7, units = "cm", scale = 2)

p_coef_grid
```

