---
title: "Supplementary Analyses"
subtitle: "Understanding online influence using a custom social media platform"
format:
  html:
    toc: true
    toc-depth: 3
    embed-resources: true
echo: false
message: false
warning: false
---

```{r}
#| label: setup
library(here)
library(tidyverse)
library(ggpubr)
library(patchwork)
library(cowplot)
library(brms)

# Shared helpers and colours
source(here("R/visualise/colour-palettes.R"))
source(here("R/helper-functions/lm-functions.R"))
# Grid-plotting functions shared with the main analysis (03_linear-modelling.qmd)
source(here("R/visualise/functions/posts-seen-grid-plots.R"))

# These match the settings used in 03_linear-modelling.qmd: report the Bayesian
# models, and load their saved output rather than re-fitting.
Bayesian   <- TRUE
run_models <- FALSE
```

```{r}
#| label: data
# load before and after data separately
load(here("data/magpie/original/combined/before.Rdata"))
load(here("data/magpie/original/combined/after.Rdata"))

# load before, after, change combined data
load(here("data/magpie/processed/combined/survey-before-after-change.Rdata"))

# Outcome variable groups (same derivations as 03_linear-modelling.qmd)
after_questions      <- colnames(d_after)
after_only_questions <- c("PropLiked", "PropTrolls", "PropAligned",
                          "MagpieSimilarity", "OverallExperience")

change_partisan  <- c(after_questions[grepl("Dem", after_questions) |
                                        grepl("Rep", after_questions)], "AffPol")
change_beliefs   <- after_questions[grepl("Belief", after_questions) != grepl("Extreme", after_questions)]
change_consensus <- after_questions[grepl("Consensus", after_questions)]
change_relative  <- after_questions[grepl("Relative", after_questions)]
change_trust     <- after_questions[grepl("Trust", after_questions)]
change_trust     <- change_trust["WVSTrust" != change_trust]

# scale all before/after/experience measures to (0, 1) for the Beta models
d_before_after_change_scale01 <- d_before_after_change %>%
  mutate(across(
    where(is.numeric) &
      (ends_with("Before") | ends_with("After") | any_of(after_only_questions)),
    scale_to_01
  ))

# d_lm = scaled data fed to the models; d_bar = raw data for the bar plots
d_lm  <- d_before_after_change_scale01
d_bar <- d_before_after_change
```

# Overview

This document collects the analyses referenced as "Supplementary Analyses" in
the manuscript. The complete analysis pipeline is split across the numbered
Quarto documents at the root of this repository, and full details of every
analysis reported in the paper can be reproduced from them:

- **`01_demographics.qmd`** — sample demographics, political identification, and
  initial beliefs (manuscript Figure 1).
- **`02_engagement.qmd`** — engagement and activity on the platform, including the
  chi-square tests of engagement composition and polarity (Figure 2).
- **`03_linear-modelling.qmd`** — the Bayesian beta-regression models of condition
  effects on beliefs, perceptions, trust, and experience (Figures 3–4), and the
  posts-seen models (Figure 5).
- **`04_supplementary-materials.qmd`** (this document) — the supplementary
  analyses below.

Shared code is factored into sourceable scripts so that nothing is defined
twice: model-fitting and plotting helpers live in
`R/helper-functions/lm-functions.R`, the posts-seen grid plotters in
`R/visualise/functions/posts-seen-grid-plots.R`, and the posts-seen correlation
computation in `R/analyse/posts-seen-correlations-prep.R`. Both this document and
`03_linear-modelling.qmd` source those scripts rather than redefining the
functions.

The sections below correspond to the places the manuscript points to the
Supplementary Analyses.

# Standardised residuals for the chi-square tests of engagement

*Referenced in the Engagement results: "To interpret the significant chi-square
result, we examined cellwise standardised residuals; values with $|z| > 1.96$
were taken to indicate cell counts that differed from the expectation. These
values are reported in the Supplementary Analyses."*

The engagement results report several chi-square tests. Here we give the cellwise
standardised residuals for each significant omnibus test, which indicate *which*
cells drove the effect: a positive residual means the observed count was larger
than expected under the null, a negative residual means it was smaller, and
$|z| > 1.96$ corresponds roughly to $p < .05$. The tests themselves (and the
figures they accompany) are reported in `02_engagement.qmd`; both documents
source the same script (`R/analyse/engagement-chisq.R`) so the tests are computed
only once.

```{r}
#| label: engagement-chisq
# Computes chisq_composition, chisq_polarity (list by engagement type), and
# chisq_friendly, each carrying its standardised residuals in $stdres.
source(here("R/analyse/engagement-chisq.R"))
```

## Composition of engagement types across conditions

The relative composition of engagement types (favourites, reblogs, replies, and
original posts) differed across conditions,
$\chi^2(`r chisq_composition$parameter`) = `r round(chisq_composition$statistic, 2)`$,
$p < .001$. Residuals (rows = condition, columns = engagement type) show that the
`Left` condition had more favourites and fewer reblogs than expected, while the
`Right` condition showed the opposite pattern (more reblogs, fewer favourites)
along with fewer original posts.

```{r}
#| label: residuals-composition
knitr::kable(round(chisq_composition$stdres, 2))
```

## Political polarity of engagement across conditions

For each engagement type we tested whether the political polarity of engagement
(left, neutral, right) differed across conditions. Residuals (rows = polarity,
columns = condition) show, for example, an over-representation of right-wing posts
and an under-representation of neutral posts in the `Right` condition, with the
strongest effects for reblogs and favourites.

```{r}
#| label: residuals-polarity
#| results: asis
for (t in names(chisq_polarity)) {
  test <- chisq_polarity[[t]]
  cat(sprintf("\n\n**%s** &mdash; $\\chi^2(%d) = %.2f$, $p = %.3f$\n\n",
              t, test$parameter, test$statistic, test$p.value))
  print(knitr::kable(round(test$stdres, 2)))
}
```

## Friendly versus non-friendly engagement across conditions

The number of friendly versus non-friendly engagements differed across conditions,
$\chi^2(`r chisq_friendly$parameter`) = `r round(chisq_friendly$statistic, 2)`$,
$p < .001$. Residuals (rows = condition) show that the `Right` condition had
significantly fewer friendly engagements than expected while the `Left` condition
had significantly more.

```{r}
#| label: residuals-friendly
knitr::kable(round(chisq_friendly$stdres, 2))
```

# Linear modelling of each trust, affective polarisation, and relative-belief sub-measure

*Referenced on p. 18: "An equivalent plot with the breakdown of each individual
trust measure is shown in the Supplementary Analyses."*

The main text reports condition effects on the aggregate trust measure
(`TrustOverall`), affective polarisation (`AffPol`), and relative-belief
(`RelativePolitics`) measures (Figure 3). Here we break those down into their
component sub-measures, using the same model structure
(`measure After ~ measure Before + Condition`, Bayesian beta regression) and the
same plotting function (`plot_lm_and_bar`) as the main analysis.

## Trust and affective polarisation sub-measures

The trust panel shows that, relative to the `Control`, trust in the `Left`
condition decreased for businesses, universities, and the government, and that
the increase in trust in other people was credibly smallest in the `Left`
condition. Trust in the media was the only sub-measure with no credible
difference from `Control`.

```{r}
#| label: trust-affpol-breakdown
#| fig.width: 13
#| fig.height: 15
variable_groups <- list(
  change_trust,
  change_partisan
)

titles <- c(
  "Trust Measures",
  "Affective Polarisation Measures"
)

x_labs_lm = c(
  "< 0 = trust less than control",
  "< 0 = less polarised than control"
)

x_labs_bar = c(
  "< 0 = became less trusting",
  "< 0 = became less polarised"
)

p_list_aff_trust <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  by_topic = FALSE,
  Bayesian = Bayesian,
  run_models = run_models
)
p_aff_trust <- ggarrange(
  plotlist = p_list_aff_trust,
  ncol = 1,
  heights = c(1, 2)
)
p_aff_trust
file = paste0("R/visualise/plots/combined-bar-lm-aff-trust-Bayes-", Bayesian, ".png")
ggsave(filename = file, width = 30, height = 37, units = "cm", plot = p_aff_trust) # roughly a4 size
```

## Relative-belief sub-measures (by topic)

```{r}
#| label: relative-breakdown
#| fig.width: 13
#| fig.height: 8
variable_groups <- list(
  change_relative
)

titles <- c(
  "Perceived own beliefs relative to population, by topic"
)

x_labs_lm = c(
  "< 0 = perceive beliefs more left wing than control"
)

x_labs_bar = c(
  "< 0 = perceive beliefs more left wing than before"
)

p_list_relative <- plot_lm_and_bar(
  variable_groups,
  x_labs_lm,
  x_labs_bar,
  titles,
  d_lm,
  d_bar,
  change = TRUE,
  ytext = TRUE,
  ylim = c(-10, 10),
  by_topic = FALSE,
  Bayesian = Bayesian,
  run_models = run_models
)
p_relative <- ggarrange(
  plotlist = p_list_relative,
  ncol = 1,
  heights = c(1, 2)
)
p_relative
file = paste0("R/visualise/plots/combined-bar-lm-relative-Bayes-", Bayesian, ".png")
ggsave(filename = file, width = 30, height = 37, units = "cm", plot = p_relative) # roughly a4 size
```

# Comparing the full sample to participants who did not have "posts seen" data available

*Referenced on p. 22 (footnote 4): "The sample with these exclusions did not
differ from the full sample in their initial beliefs, political identification,
perceptions of consensus, or age … See the Supplemental Materials for more
details."*

Posts-seen data could not be recorded for every participant (due to technical
issues for ~12% in `Left`, ~23% in `Right`, ~2% in `Control`), and the
posts-seen analysis was further restricted to participants who saw at least 50
posts. Here we check that the sub-sample with usable posts-seen data did not
differ from the full sample on the key baseline measures: initial beliefs
(`BeliefBefore`), political identification (`PoliticalIDNum`), extremity of
beliefs (`ExtremeBeliefBefore`), perceptions of consensus
(`ConsensusPoliticsBefore`), and age. Since we don't use the control condition in this analysis, we exclude this condidion here. 

```{r}
#| label: sample-comparison
load(here("data/magpie/processed/combined/posts-seen-by-user.Rdata"))

d_seen_compare <- unique_posts_seen_by_user %>%
  # Join the troll-only proportions
  left_join(
    unique_posts_seen_by_user_nontroll %>%
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_troll = prop_right,
             prop_left_troll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Join the non-troll proportions
  left_join(
    unique_posts_seen_by_user_troll %>%
      select(username, Condition, prop_right, prop_left) %>%
      rename(prop_right_nontroll = prop_right,
             prop_left_nontroll = prop_left),
    by = c("username", "Condition")
  ) %>%
  # Rename the all-posts proportions for clarity
  rename(
    prop_right_all = prop_right,
    prop_left_all = prop_left
  ) %>%
  # Replace NAs with 0 (participants who saw no troll/non-troll content)
  mutate(
    prop_right_troll = replace_na(prop_right_troll, 0),
    prop_left_troll = replace_na(prop_left_troll, 0),
    prop_right_nontroll = replace_na(prop_right_nontroll, 0),
    prop_left_nontroll = replace_na(prop_left_nontroll, 0)
  ) 

d_survey_compare <- d_before_after_change_scale01 %>%
  left_join(
    d_seen_compare,
    by = c(UserName = "username", "Condition")
  ) %>% filter(Condition != "Control")

print(paste0("Posts seen data is missing for ", sum(is.na(d_survey_compare$prop_left_nontroll)), " participants total"))
print("Breakdown by condition: ")
# check number of missing in each condition
d_survey_compare %>%
  group_by(Condition) %>%
  summarise(Missing = sum(is.na(prop_right_all)))

summarise_vars = function(data) {
  data %>%
    summarise(
      m_beliefs    = mean(BeliefBefore, na.rm = TRUE),
      sd_beliefs   = sd(BeliefBefore, na.rm = TRUE),
      m_polID      = mean(PoliticalIDNum, na.rm = TRUE),
      sd_polID     = sd(PoliticalIDNum, na.rm = TRUE),
      m_extreme    = mean(ExtremeBeliefBefore, na.rm = TRUE),
      sd_extreme   = sd(ExtremeBeliefBefore, na.rm = TRUE),
      m_consensus  = mean(ConsensusPoliticsBefore, na.rm = TRUE),
      sd_consensus = sd(ConsensusPoliticsBefore, na.rm = TRUE),
      m_age        = mean(Age, na.rm = TRUE),
      sd_age       = sd(Age, na.rm = TRUE)
    )
}

base_data <- d_survey_compare %>% filter(Condition != "Control")

summary_stats <- bind_rows(
  base_data %>% summarise_vars() %>% mutate(group = "Full Sample"),
  base_data %>% filter(!is.na(prop_right_all)) %>% summarise_vars() %>% mutate(group = "Posts Seen Data Available")
)

# Pivot to long format for plotting
summary_long <- summary_stats %>%
  pivot_longer(
    cols = -group,
    names_to = c(".value", "variable"),
    names_pattern = "(m|sd)_(.*)"
  )

# Bar graph
ggplot(summary_long, aes(x = group, y = m, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = m - sd, ymax = m + sd),
    position = position_dodge(width = 0.8),
    width = 0.25
  ) +
  facet_wrap(~ variable, scales = "free_y", labeller = labeller(variable = c(
    "beliefs"   = "Belief Before",
    "polID"     = "Political ID Before",
    "extreme"   = "Extremity of Beliefs Before",
    "consensus" = "Perceptions of Consensus Before",
    "age"       = "Age"
  ))) +
  labs(
    title = "Comparison of Variables by Posts Seen Data Availability",
    x     = NULL,
    y     = "Mean (Scaled except for age and Political ID)",
    fill  = "Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank()
  )
```

The means and standard errors of the baseline measures are very similar with and
without the posts-seen restriction, indicating that the missing posts-seen data
did not systematically bias the sub-sample.

For completeness, the table below reports the mean and variance of the total
proportion of political content seen in each condition, for all content, for
troll-initiated content, and for non-troll-initiated content.

```{r}
#| label: posts-seen-variance
d_survey_compare %>%
  group_by(Condition) %>%
  summarise(
    var_troll     = var(prop_right_troll + prop_left_troll, na.rm = TRUE),
    mean_troll    = mean(prop_right_troll + prop_left_troll, na.rm = TRUE),
    var_nontroll  = var(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    mean_nontroll = mean(prop_right_nontroll + prop_left_nontroll, na.rm = TRUE),
    var_all       = var(prop_right_all + prop_left_all, na.rm = TRUE),
    mean_all      = mean(prop_right_all + prop_left_all, na.rm = TRUE)
  )
```

# Posts-seen analysis: correlation equivalent of Figure 5

*Referenced on p. 23 (footnote 6): "We also repeated the same analyses as shown
in Figure 5 using correlations between the posts participants saw and each
variable, which yielded very similar results (see Supplementary Analyses)."*

Figure 5 in the main text uses Bayesian beta-regression coefficients to relate
the proportion of each post type a participant saw (Right, Left, Friendly) to the
change in each outcome measure, comparing all content seen to non-troll-initiated
content only. Here we reproduce that comparison using simple correlations rather
than the regression models. The correlation objects are computed in
`R/analyse/posts-seen-correlations-prep.R` (sourced below) and plotted with the
same `plotCorrelationsGrid()` plotting function used for the main figure, so the
two figures are directly comparable.

```{r}
#| label: correlations-prep
# Set the run configuration (50% visibility threshold), then compute the
# correlation objects (cor_all, cor_nontroll, tidy_cor, and the Change-suffixed
# outcome groups) used by plotCorrelationsGrid().
run_label <- "_visibility50"
source(here("R/analyse/posts-seen-correlations-prep.R"))
```

```{r}
#| label: correlations-grid-overall
#| fig.width: 14
#| fig.height: 9
p_cor_grid <- plotCorrelationsGrid(trust_type = "overall")
p_cor_grid
ggsave(plot = p_cor_grid,
       filename = here(paste0("R/visualise/plots/posts-seen-correlations-grid", run_label, ".png")),
       width = 22, height = 14, units = "cm", scale = 2)
```

As in the main analysis, the credible correlations between the proportion of
each post type seen and the outcome measures closely track the regression
results, and credible associations with beliefs and perceptions of consensus
disappear once troll-initiated content is removed. Note that there are a few additional credible effects, which may be because these correlations are slightly more powerful (at least for the before/after measures), but they are also less rigorous, so any effects that are not also seen in the model analyses should be interpreted with caution. 

## Trust sub-measures (correlation and coefficient grids)

The same posts-seen comparison broken down by individual trust sub-measure
rather than the aggregate trust measure, shown both as correlations and as the
Bayesian regression coefficients from Figure 5.

## Correlations

```{r}
#| label: correlations-grid-trust-subscales
#| fig.width: 14
#| fig.height: 11
p_cor_grid_supp <- plotCorrelationsGrid(trust_type = "subscales")
p_cor_grid_supp
ggsave(plot = p_cor_grid_supp,
       filename = here(paste0("R/visualise/plots/posts-seen-correlations-grid-trust-subscales", run_label, ".png")),
       width = 22, height = 18, units = "cm", scale = 2)
```

## Model Coefficients (same as in manuscript)


```{r}
#| label: coefficients-grid-trust-subscales
#| fig.width: 14
#| fig.height: 13
p_coef_grid_supp <- plotCoefficientsGrid(run_label = run_label, trust_type = "subscales")
p_coef_grid_supp
ggsave(plot = p_coef_grid_supp,
       filename = here(paste0("R/visualise/plots/posts-seen-coefficients-grid-trust-subscales", run_label, ".png")),
       width = 14, height = 22, units = "cm", scale = 2)
```
