---
title: "Merge Global Data across Conditions"
output:
  html_document:
    df_print: paged
---
```{r message=FALSE, warning=FALSE, echo=FALSE}
rm(list=ls())
library(tidyverse)
library(here)
library(stringi)
library(assertthat)
library(jsonlite)
library(lubridate)

options(scipen=999,digits=20)

DRY_RUN <- FALSE
```

Data directory
```{r}
raw_magpie_dir <- "data/magpie/original"
processed_magpie_dir <- "data/magpie/processed"
raw_files_mastodon_dir <- "data/mastodon/files/raw"
processed_files_mastodon_dir <- "data/mastodon/files/processed"
```

```{r}

save_processed_file = function(data, file, dry_run = DRY_RUN) {
  if (! dry_run) {
    # create the directory if it does not exist
    dir.create(dirname(file), recursive = TRUE, showWarnings = FALSE)
    cat("saving to: ", file)
    write_csv(data, file=file)
  } else {
    cat("(dry_run) skipping saving to: ", file)
  }
}
```

Next, let's just check that "here()" returns what we think it should. If things are configured correctly, here should relate to the top-level directory for the project - as per the github repository.

```{r}
# Assert that the here() function returns what we expect.
# We do this by checking that it contains the "R" and "data" directories.

assert_that(
    dir.exists(file.path(here(), "R")),
    msg = "The 'here()' function does not point to the expected directory."
)
```

The readr package (e.g. v2.1.5 under R 4.5) has a "bug" such that when read_csv is used
to read columns containing numeric values > 32 bit (e.g. integer values used as database keys,
for example), the value may be silently corrupted. The root cause seems to be that R (e.g. 4.5)
silently misrepresents the long numbers when converting to "numeric" type.

For example, the follwing code yields FALSE where it should return TRUE

<pre>
id <- "112911754871964075"
as.character(as.numeric(id)) == id
</pre>

The following check determines whether the current version of readr/R has the bug or not,
in case a version is released that guards against the underyling issue.

```{r}
#sessionInfo()

# show current package versions
readr_version <- packageVersion("readr")

# The following simulates a single column CSV file where the
# each row contains a different number.

data <- "MySQLID\n112917130127682334\n112917130127682336"

# read_csv does not have a "text" argument
ids <- read_csv(file = I(data), show_col_types = FALSE)

# The two numbers are different, so the following assertion should hold.
# However, due to the aforementioned bug, this assertion is likely to fail.

readr_preserves <- ids[1, 1] != ids[2, 1]

cat(paste0("readr::read_csv ",
           readr_version,
           ifelse(readr_preserves, " does", " does not"),
           " preserve long numeric identifiers\n")
)

ids_correct <- read_csv(col_types = cols(MySQLID = "c"), file = I(data))

ignoreSuccess <- assert_that(ids_correct[1, 1] != ids_correct[2, 1],
                             msg = "readr::read_csv workaround failed")

cat("But using explicit col_types works as expected")

```

# Make global participants by condition

```{r}
condition = "left"
```

## Load the mastodon participant data.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# first load the mastodon participant data
mastodon_participant_colSpec <- cols_only(account_id = "c", UserName = "c")

mastodon_participant_file <- here(raw_magpie_dir,
                                  tolower(condition),
                                  "mastodon_participant_ids.csv")

mastodon_account_ids <-
  read_csv(file = mastodon_participant_file,
           col_types = mastodon_participant_colSpec) %>%
  rename(MagpieID = account_id)
```

```{r}
prolific_participant_colSpec <- cols(.default = "c")

prolific_participant_file <- here(raw_magpie_dir,
                                  tolower(condition),
                                  "prolific_participant_ids.csv")

prolific_account_ids <-
  read_csv(file = prolific_participant_file,
           col_types = prolific_participant_colSpec)
```

# Create a file containing the full set of identifiers (mastodon, prolific, qualtrics etc.)

```{r}
d_names <-
  prolific_account_ids %>%
  mutate(Troll = as.numeric(startsWith(ProlificID, "fake")))
```

```{r}
d_init <- mastodon_account_ids %>%
  left_join(d_names,by="UserName") %>%
  mutate(Subject = ifelse(UserName=="Admin", "Admin", Subject))

global_participant_colSpec <- cols(Troll = "n", .defult = "c")

global_participant_file <- here(processed_magpie_dir,
                                tolower(condition),
                                "global_participant_ids.csv")

d_init %>% save_processed_file(file = global_participant_file)
```

# M24-CPAR

## Load demographics
```{r}
demographics_colSpec <- cols(.default = "c")

demographics_file <- here(
  raw_magpie_dir,
  "combined",
  "demographics.csv"
)

demographics <- read_csv(
    file      = demographics_file,
    col_types = demographics_colSpec
  ) %>%
  # 1) normalize the condition column name & values
  rename(condition = Condition) %>%
  mutate(condition = tolower(condition)) %>%
  
  # 2) drop all the "after" timepoints, keep only the "before"
  filter(tolower(TimePoint) == "before") %>%
  
  # 3) now distinct() so each (condition, UserName) appears only once
  distinct(condition, UserName, .keep_all = TRUE)
```

## Combine 3 condition
```{r}
# Define conditions and column specification
conditions <- c("control", "right", "left")
global_participant_colSpec <- cols(Troll = "n", .default = "c")

# Read, tag with condition, and combine files
combined_global <- map_dfr(
  conditions,
  function(cond) {
    global_participant_file <- here(processed_magpie_dir, tolower(cond), "global_participant_ids.csv")
    read_csv(file = global_participant_file, col_types = global_participant_colSpec) %>%
      mutate(condition = cond)
  }
)

combined_global <- combined_global %>% 
  left_join(
    demographics %>% 
      select(
        condition,
        UserName,
        Age,
        Sex,
        Gender,
        PoliticalID,
        PoliticalIDNum,
      ),
    by = c("condition", "UserName")
  )

# Rename columns
combined_global <- combined_global %>%
  rename(
    age = Age,
    sex = Sex,
    gender = Gender,
    political_id = PoliticalID,
    political_id_numetric = PoliticalIDNum,
    mastodon_account_id = MagpieID,
    mastodon_username = UserName,
    mastodon_display_name = UserNameSpaces,
    is_confederate = Troll,
    qualtrics_subject_id = Subject,
    prolific_participant_id = ProlificID
  ) %>%
  # Reorder columns
  select(
    condition, 
    mastodon_account_id, 
    mastodon_username,
    mastodon_display_name,
    is_confederate,
    qualtrics_subject_id,
    prolific_participant_id,
    age,
    sex,
    gender,
    political_id_numetric,
    political_id,
  )

# Define output file path
combined_global_file <- here(processed_magpie_dir, "combined", "combined_participant_ids.csv")

# Save combined result
save_processed_file(combined_global, file = combined_global_file)
  
```


# M24-CSTAT

## Load Bao's label message (condition, status_id, message_topic, condition)

```{r}
# 1. Your three conditions
conditions <- c("control", "left", "right")

# 2. Read & combine all three JSONs into one tibble
all_annotations <- map_dfr(
  conditions,
  function(cond) {
    file_path <- here(processed_files_mastodon_dir, tolower(cond), "status_groundtruth.json")
    raw      <- fromJSON(file_path)
    
    # flatten each conversation → rows of (status_id, message_topic)
    map_dfr(
      raw,
      function(status_map) {
        tibble(
          status_id     = names(status_map),
          message_topic_rater_1 = as.character(status_map)
        )
      },
      .id = "conversation_id"
    ) %>%
      mutate(condition = cond)
  }
)

# 4. Save out
annotations_colSpec <- cols(.default = "c")
annotations_output_file <- here(
  processed_files_mastodon_dir,
  "combined",
  "statuses_with_annotations.csv"   # or whatever name you prefer
)

all_annotations %>% 
  save_processed_file(file = annotations_output_file)
```

## Set condition and root date

```{r}
condition <- "right"

if (condition == "control") {
  start_time <- ymd_hms("2024-08-06 21:00:00")
  end_time   <- ymd_hms("2024-08-09 21:00:00")
} else if (condition == "right") {
  start_time <- ymd_hms("2024-08-20 21:00:00")
  end_time   <- ymd_hms("2024-08-23 21:00:00")
} else if (condition == "left") {
  start_time <- ymd_hms("2024-09-03 20:30:00")
  end_time   <- ymd_hms("2024-09-06 20:30:00")
} else {
  stop("Unknown condition: ", condition)
}
```

Load additional csv files 

```{r}
global_participant_colSpec <- cols(Troll = "n", .default = "c")

global_participant_file <- here(processed_magpie_dir,
                                tolower(condition),
                                "global_participant_ids.csv")

d_init <- read_csv(file = global_participant_file, col_types = global_participant_colSpec)

prolific_participant_colSpec <- cols(.default = "c")

prolific_participant_file <- here(raw_magpie_dir,
                                  tolower(condition),
                                  "prolific_participant_ids.csv")

prolific_account_ids <-
  read_csv(file = prolific_participant_file,
           col_types = prolific_participant_colSpec)

d_names <-
  prolific_account_ids %>%
  mutate(Troll = as.numeric(startsWith(ProlificID, "fake")))
```

## Create processed status.csv

```{r}
replacementVec <- d_init %>% select(MagpieID,UserName) %>%
  filter(!is.na(MagpieID)) %>% arrange(MagpieID)
rv <- replacementVec$UserName
names(rv) <- replacementVec$MagpieID

raw_statuses_colSpec <- cols(.default = "c")
raw_statuses_file <- here(raw_files_mastodon_dir,
                      tolower(condition),
                      "statuses.csv")

# read the statuses data
d_stat <- read_csv(file = raw_statuses_file, col_types = raw_statuses_colSpec) %>%
  rename(StatusID=id,Time=created_at,MagpieID=account_id,
         StatusReplyID=in_reply_to_id,
         StatusReblogID=reblog_of_id,Reply=reply,Visibility=visibility,
         ConvID=conversation_id,AccountReply=in_reply_to_account_id,
         PollID=poll_id,DeletedTime=deleted_at,EditedTime=edited_at,
         AttachID=ordered_media_attachment_ids,Text=text)

d_stat$MagpieID <- as.character(d_stat$MagpieID)
d_stat <- d_stat %>%
  left_join(d_init,by=join_by(MagpieID)) %>%
  mutate(condition=condition) %>%
  select(Subject,UserName,condition,Time,StatusID,StatusReplyID,
         StatusReblogID,Reply,Visibility,AccountReply,ConvID,PollID,
         AttachID,PollID,DeletedTime,
         EditedTime,Text) %>%
  mutate(Text = str_replace_all(Text,rv)) %>%
  mutate(AccountReply = str_replace_all(AccountReply,rv)) %>%
  filter(ymd_hms(Time) >= start_time, ymd_hms(Time) <= end_time)

d_stat$StatusID <- as.character(d_stat$StatusID)
d_stat$StatusReplyID <- as.character(d_stat$StatusReplyID)
d_stat$StatusReblogID <- as.character(d_stat$StatusReblogID)
d_stat$AccountReply <- as.character(d_stat$AccountReply)

d_statowner <- d_stat %>% select(StatusID,UserName) %>% arrange(StatusID)
userRV <- d_statowner$UserName
names(userRV) <- d_statowner$StatusID

d_names_short <- d_names %>% select(UserName,Troll)

d_stat <- d_stat %>%
  mutate(AccountReblog = str_replace_all(StatusReblogID,userRV)) %>%
  left_join(d_names_short,by="UserName")

for (i in 1:nrow(d_stat)) {
  if (!is.na(d_stat$StatusReblogID[i])) {
    j <- which(d_stat$StatusID==d_stat$StatusReblogID[i])
    if (length(j)>0) {
      d_stat$Text[i] <- d_stat$Text[j]
    }
  }
}

processed_statuses_colSpec <- cols(.default = "c")
processed_statuses_file <- here(processed_files_mastodon_dir,
                      tolower(condition),
                      "statuses.csv")

d_stat %>% save_processed_file(file = processed_statuses_file)
```

## Create processed status_summaries.csv

```{r}
# read the post tag data for control condition
raw_statuses_stats_colSpec <- cols(.default = "c")
raw_statuses_stats_file <- here(raw_files_mastodon_dir,
                          tolower(condition),
                          "status_stats.csv")

d_posts <- read_csv(file = raw_statuses_stats_file, col_types =  raw_statuses_stats_colSpec) %>%
  mutate(condition=tolower(condition)) %>%
  rename(PostID=id,TimeCreated=created_at,TimeUpdated=updated_at,
         StatusID=status_id,ReplyN=replies_count,ReblogsN=reblogs_count,
         FavouritesN=favourites_count) %>%
  mutate(StatusID = as.character(StatusID)) %>%
  left_join(d_statowner,by="StatusID") %>%
  left_join(d_names_short %>% 
              filter(!is.na(UserName)), by = "UserName") %>%
  rename(StatusAuthor = UserName) %>%
  select(StatusID,condition,StatusAuthor,Troll,TimeCreated,TimeUpdated,
         ReplyN,ReblogsN,FavouritesN) %>%
  filter(ymd_hms(TimeCreated) >= start_time, ymd_hms(TimeCreated) <= end_time)


processed_statuses_stats_colSpec <- cols(.default = "c")
processed_statuses_stats_file <- here(processed_files_mastodon_dir,
                                    tolower(condition),
                                    "status_summaries.csv")

d_posts %>% save_processed_file(file = processed_statuses_stats_file)
```

## Create processed statuses_full.csv

```{r}
d_stats_full <- d_stat %>%
  left_join(
    d_posts %>% select(StatusID, ReplyN, ReblogsN, FavouritesN),
    by = "StatusID"
  ) %>%
  
  # 2) Rename the core columns so they match combined_global
  rename(
    mastodon_username    = UserName,
    qualtrics_subject_id = Subject,
    is_confederate       = Troll
  ) %>%
  
  # 3) Join in account‐level metadata from combined_global
  left_join(
    combined_global %>% 
      select(
        condition, 
        mastodon_account_id, 
        mastodon_username,
        mastodon_display_name,
        prolific_participant_id,
        age,
        sex,
        gender,
        political_id_numetric,
        political_id,
      ),
    by = c("condition", "mastodon_username")
  ) %>%

  # 4) Rename the engagement stats
  rename(
    status_id        = StatusID,
    conversation_id  = ConvID,
    text             = Text,
    creation_time    = Time,
    last_edit_time   = EditedTime,
    replies_count    = ReplyN,
    reblogs_count    = ReblogsN,
    favourites_count = FavouritesN,
    is_reply_to      = StatusReplyID,
    replied_to_username = AccountReply,
    is_reblog_of        = StatusReblogID,
    reblogged_username  = AccountReblog,
  ) 

processed_statuses_full_colSpec <- cols(.default = "c", 
                                        replies_count    = "n",
                                        reblogs_count    = "n",
                                        favourites_count = "n"
                                    )
processed_statuses_full_file <- here(processed_files_mastodon_dir,
                                    tolower(condition),
                                    "statuses_full.csv")

d_stats_full %>% save_processed_file(file = processed_statuses_full_file)
```

```{r}
sum(duplicated(d_stat$StatusID))     # number of duplicates in d_stat
sum(duplicated(d_posts$StatusID))    # number of duplicates in d_posts
```

## Combined statuses_full from 3 conditions

```{r}
processed_statuses_full_colSpec <- cols(.default = "c", 
                                        replies_count    = "n",
                                        reblogs_count    = "n",
                                        favourites_count = "n"
                                        )

# 2. Which folders to pull in
conditions <- c("left", "right", "control")

# 3. Read & tag each condition’s file
all_statuses_full <- map_dfr(conditions, function(cond) {
  read_csv(
    here(processed_files_mastodon_dir, tolower(cond), "statuses_full.csv"),
    col_types = processed_statuses_full_colSpec
  ) %>%
    mutate(condition = cond)
})

# 4. Bring in your annotations (conversation_id + message_topic)
all_statuses_full <- all_statuses_full %>%
  left_join(
    all_annotations %>%
      select(
        status_id,
        condition,
        message_topic_rater_1
      ),
    by = c("status_id", "condition")
  )

# 5. Derive reply/reblog flags and the corresponding usernames
#    (assumes you already have a named vector `rv` mapping MagpieID→UserName)
all_statuses_full <- all_statuses_full %>%
  mutate(
    is_reply            = !is.na(is_reply_to),
    is_reblog           = !is.na(is_reblog_of),
  )
  
# 6. Reorder exactly as you asked
all_statuses_full <- all_statuses_full %>%
  select(
    condition, 
    mastodon_account_id, 
    mastodon_username,
    mastodon_display_name,
    is_confederate,
    qualtrics_subject_id,
    prolific_participant_id,
    age,
    sex,
    gender,
    political_id_numetric,
    political_id,
    status_id,
    conversation_id,
    text,
    message_topic_rater_1,
    creation_time,
    last_edit_time,
    replies_count,
    reblogs_count,
    favourites_count,
    is_reply,
    is_reply_to,
    replied_to_username,
    is_reblog,
    is_reblog_of,
    reblogged_username,
  )
processed_statuses_global_file <- here(
  processed_magpie_dir,
  "combined",
  "combined_statuses_with_global_ids.csv"
)

all_statuses_full %>% 
  save_processed_file(file = processed_statuses_global_file)
    
```

# Get time window for each condition
```{r}
time_windows <- all_statuses_full %>%
  # 1) Parse the Time column, including fractional seconds:
  mutate(creation_time = ymd_hms(creation_time)) %>%
  # 2) Group by condition:
  group_by(condition) %>%
  # 3) Compute min and max of Time:
  summarise(
    start_time = min(creation_time, na.rm = TRUE),
    end_time   = max(creation_time, na.rm = TRUE),
    time_diff  = end_time - start_time
  )

time_windows
```

# M24-BLF
claim_topic,
short_text,
polarity,
belief_adjusted_pre,
belief_raw_pre,
belief_distance_from_centre_pre,
belief_adjusted_post,
belief_raw_post,
belief_distance_from_centre_post,
belief_adjusted_delta,
belief_raw_delta,
belief_distance_from_centre_delta
order,
code,
claim

```{r}
belief_colSpec <- cols(.default = "c",
                       Belief = "n", 
                       RawBelief = "n", 
                       ExtremeBelief = "n")

# 2. File path
belief_file <- here(raw_magpie_dir, "combined", "beliefs_long.csv")

# 3. Read & rename the anchor columns
belief_long <- read_csv(belief_file, col_types = belief_colSpec) %>%
  rename(
    qualtrics_subject_id  = Subject,
    mastodon_username     = UserName,
    condition             = Condition,
    claim_topic           = Topic,
    short_text            = ShortText,
    polarity              = Polarity,
    order                 = Order,
    code                  = Code,
    claim                 = Claim
  ) %>%
  # normalize TimePoint for pivoting
  mutate(TimePoint = tolower(TimePoint),
         condition = tolower(condition),
         )

# 4. Pivot wider so each metric has _before and _after columns
belief_wide <- belief_long %>%
  pivot_wider(
    id_cols     = c(
      qualtrics_subject_id, mastodon_username, condition, claim_topic, short_text,
      polarity, order, code, claim
    ),
    names_from  = TimePoint,
    values_from = c(Belief, RawBelief, ExtremeBelief),
    names_glue  = "{.value}_{TimePoint}"
  ) %>%
  # 5. Rename into your _pre / _post schema
  rename(
    belief_adjusted_pre               = Belief_before,
    belief_raw_pre                    = RawBelief_before,
    belief_distance_from_centre_pre   = ExtremeBelief_before,
    belief_adjusted_post              = Belief_after,
    belief_raw_post                   = RawBelief_after,
    belief_distance_from_centre_post  = ExtremeBelief_after
  ) %>%
  # 6. Compute the deltas
  mutate(
    belief_adjusted_delta               = belief_adjusted_post - belief_adjusted_pre,
    belief_raw_delta                    = belief_raw_post - belief_raw_pre,
    belief_distance_from_centre_delta   = belief_distance_from_centre_post - belief_distance_from_centre_pre
  ) %>%
  # 5. Join in subject metadata from combined_global
  left_join(
    combined_global, 
    by = c("condition", "qualtrics_subject_id", "mastodon_username")
  ) %>%
  select(
    condition, 
    mastodon_account_id, 
    mastodon_username,
    mastodon_display_name,
    is_confederate,
    qualtrics_subject_id,
    prolific_participant_id,
    age,
    sex,
    gender,
    political_id_numetric,
    political_id,
    claim_topic,
    short_text,
    polarity,
    belief_adjusted_pre,
    belief_raw_pre,
    belief_distance_from_centre_pre,
    belief_adjusted_post,
    belief_raw_post,
    belief_distance_from_centre_post,
    belief_adjusted_delta,
    belief_raw_delta,
    belief_distance_from_centre_delta,
    order,
    code,
    claim,
  )

# Define output file path
combined_belief_wide_file <- here(processed_magpie_dir, "combined", "combined_beliefs_wide.csv")

# Save combined result
save_processed_file(belief_wide, file = combined_belief_wide_file)
```

# M24-THERM
```{r}
thermometer_colSpec <- cols(.default = "c")

before_file <- here(raw_magpie_dir, "combined", "before.csv")
after_file  <- here(raw_magpie_dir, "combined", "after.csv")

# 3. Read each in and tag with time_point
before <- read_csv(before_file,  col_types = thermometer_colSpec) %>% 
  mutate(time_point = "before")

after  <- read_csv(after_file,   col_types = thermometer_colSpec) %>% 
  mutate(time_point = "after")

# 4. Stack them
combined_thermometer <- bind_rows(before, after) %>%

  # 5. Rename keys and all your thermometer / affect columns
  rename(
    condition                   = Condition,
    qualtrics_subject_id        = Subject,
    mastodon_username           = UserName,
    republican_thermometer      = RepThermometer,
    democrat_thermometer        = DemThermometer,
    affective_polarisation      = AffPol,
    republican_negative         = RepNeg,
    republican_positive         = RepPos,
    democrat_negative           = DemNeg,
    democrat_positive           = DemPos,
    republican_angry            = RepAngry,
    republican_contempt         = RepContempt,
    republican_admire           = RepAdmire,
    republican_fear             = RepFear,
    republican_enthusiastic     = RepEnthusiastic,
    republican_pride            = RepPride,
    democrat_angry              = DemAngry,
    democrat_contempt           = DemContempt,
    democrat_admire             = DemAdmire,
    democrat_fear               = DemFear,
    democrat_enthusiastic       = DemEnthusiastic,
    democrat_pride              = DemPride,
  ) %>%
  # normalize the condition column
  mutate(condition = tolower(condition)) %>%

  # 6. Join in your participant metadata
  left_join(
    combined_global %>%
      select(
        condition,
        qualtrics_subject_id,
        mastodon_username,
        mastodon_account_id,
        mastodon_display_name,
        is_confederate,
        prolific_participant_id,
        age,
        sex,
        gender,
        political_id_numetric,
        political_id
      ),
    by = c("condition", "qualtrics_subject_id", "mastodon_username")
  ) %>%

  # 7. Reorder exactly as requested
  select(
    condition, 
    mastodon_account_id, 
    mastodon_username,
    mastodon_display_name,
    is_confederate,
    qualtrics_subject_id,
    prolific_participant_id,
    age,
    sex,
    gender,
    political_id_numetric,
    political_id,
    time_point,
    republican_thermometer,
    democrat_thermometer,
    affective_polarisation,
    republican_negative,
    republican_positive,
    democrat_negative,
    democrat_positive,
    republican_angry,
    republican_contempt,
    republican_admire,
    republican_fear,
    republican_enthusiastic,
    republican_pride,
    democrat_angry,
    democrat_contempt,
    democrat_admire,
    democrat_fear,
    democrat_enthusiastic,
    democrat_pride
  )

# 8. Write out the combined result
combined_thermometer_file <- here(
  processed_magpie_dir,
  "combined",
  "combined_thermometer.csv"
)

combined_thermometer %>%
  save_processed_file(file = combined_thermometer_file)

```
