---
title: "01_explore-demographics"
format: html
echo: false
message: false
warning:  false
---

```{r}
library(here)
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthdata) 
library(sf)
library(see) # for half violin plots
library(patchwork)


source(here("R/functions/colour-palettes.R"))
```


# Demographics

In this section, we will explore the characteristics of our sample. 

```{r}
# load "before" survey data
d_before <- read_csv(here("data/magpie/original/combined/before.csv"))

# set factor levels
d_before <- d_before %>%
  mutate(Education = factor(Education, levels = c("highschool", "somecollege","undergrad", "postgrad")), # roughly ordered by number of years
         Religion = factor(Religion, levels = c("christian", "mormon", "jewish", "muslim", "eastern", "other", "none")),
         Condition = factor(d_before$Condition, 
                             levels=c("Left","Control","Right"))) # order doesn't matter as long as other/none are last

# set factors 

# 

```


```{r}

demographic_table <- function(data, var, condition_var) {
  
  # Raw counts
  tab <- table(data[[var]], data[[condition_var]])
  tab_df <- as.data.frame.matrix(tab)
  
  # Total N
  N <- sum(tab_df)
  
  # Compute percentages of the TOTAL sample
  pct_total <- round(100 * tab_df / N)
  
  # Format cells as "count (xx%)"
  formatted <- tab_df
  for (i in seq_len(nrow(tab_df))) {
    for (j in seq_len(ncol(tab_df))) {
      formatted[i, j] <- paste0(
        tab_df[i, j],
        " (", pct_total[i, j], "%)"
      )
    }
  }
  
  # Row totals (also % of N)
  row_totals <- rowSums(tab_df)
  row_totals_fmt <- paste0(
    row_totals,
    " (", round(100 * row_totals / N), "%)"
  )
  
  # Add row totals
  formatted$Total <- row_totals_fmt
  
  # Add row names as first column
  formatted <- tibble::rownames_to_column(as.data.frame(formatted), var)
  
  return(formatted)
}
```

## **Gender**

```{r}
demographic_table(d_before, "Gender", "Condition")
```

## **Trans**

Someone was considered trans if their gender didn't match their sex, including nonbinary/genderqueer).

```{r}
demographic_table(d_before, "Trans", "Condition")
```

### **Orientation**

Breakdown of sexual orientation of participants.

```{r}
#demographic_table(d_before, "Orientation", "Condition")
```


## **LGBQT**

This is calculated by taking the answers to trans and orientation together. Someone was considered LGBTQ if they were trans (as defined above) or their orientation was anything other than straight. **Orientation is not in d_before for some reason**.

```{r}
demographic_table(d_before, "LGBT", "Condition")
```


## **Education**

```{r}
demographic_table(d_before, "Education", "Condition")
```

```{r}
plot_dem_breakdown = function(data,
                              var,
                              colour_pallette = NULL,
                              legend.position = "top",
                              legend.rows = 2, 
                              title_prefix = NULL) {
  myTable <- d_before %>%
    group_by(Condition, .data[[var]]) %>%
    summarise(Number = n()) %>%
    ungroup() %>%
    filter(!is.na(.data[[var]]))
  
  
  
  p <- myTable %>%
    ggplot(mapping = aes(y = Condition, x = Number, fill = .data[[var]])) +
    geom_col(position = position_stack(reverse = TRUE),
             colour = "black") +
    theme_bw() +
    theme(
      axis.text.y = element_text(angle = 90, size = 10),
      axis.ticks.y = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
      legend.position = legend.position,
      legend.title = element_blank()
    ) +
    labs(title = paste0(title_prefix,var,""))+
    guides(fill = guide_legend(nrow = legend.rows)) # Specifies the legend for the 'fillr' aesthetic

  
  if (!is.null(colour_pallette)) {
    p <- p +
      scale_fill_manual(values = colour_pallette)
  }
  
  ggsave(paste0("output/figures/demographics/",var,"_breakdown.png"),
       plot=p,device="png",
       width=12,height=8, units="cm")
  
  p
}


```

```{r}

p_education <- plot_dem_breakdown(d_before, "Education", title_prefix = "B. ")

p_education <- p_education + 
    scale_fill_brewer(palette="Blues",direction=-1)

p_education 

# saving it again even though the function does it automatically because original doesn't have colour palette
ggsave(paste0("output/figures/demographics/religion_breakdown.png"),
       plot=p_education,device="png",
       width=12,height=8, units="cm")
```
## **Religion**

```{r}
demographic_table(d_before, "Religion", "Condition")

p_religion <- plot_dem_breakdown(d_before, "Religion", title_prefix = "C. ")

p_religion <- p_religion + 
    scale_fill_brewer(palette="Purples",direction=-1)

p_religion

# saving it again even though the function does it automatically because original doesn't have colour palette
ggsave(paste0("output/figures/demographics/religion_breakdown.png"),
       plot=p_religion,device="png",
       width=12,height=8, units="cm")
```
## **Race**

```{r}
demographic_table(d_before, "Race", "Condition")

```

```{r}
demographic_table(d_before, "Race", "Condition")

p_race <- plot_dem_breakdown(d_before, "Race", title_prefix = "A. ")

p_race <- p_race + 
  scale_fill_brewer(palette="Greens",direction=-1) 

p_race

# saving it again even though the function does it automatically because original doesn't have colour palette
ggsave(paste0("output/figures/demographics/Race_breakdown.png"),
       plot=p_race,device="png",
       width=12,height=8, units="cm")
```
### Middle Eastern

It's useful to know what proportion of our sample had middle-eastern ethnicity, since that directly concerns the Israel/Palestine conflict. 

```{r}
demographic_table(d_before, "RaceMidEast", "Condition")
```


## **Political ID**

Whether people identified as democrat/republican, etc. 

```{r}
demographic_table(d_before, "PoliticalID", "Condition")
```

```{r}
p_polID <- plot_dem_breakdown(d_before, "PoliticalID", colour_pallette = politicalIDColours, legend.position = "top", legend.rows = 2)
p_polID
```

### Political rating 

Instead of just a categorical rating, we also asked how they identified numerically. Where  6 = strong Republican, 5 = Republican, 4 = slight Republican; 3 = independent; 2 = slight Democrat, 1 = Democrat, 0 = strong Democrat. 

```{r}

polID_num_sum <- d_before %>%
  group_by(Condition) %>%
  summarise(mean = mean(PoliticalIDNum, na.rm = TRUE), sd = sd(PoliticalIDNum, na.rm = TRUE), n = n()) %>%
  mutate(se = sd/sqrt(n()))

p_politicalID_num <- polID_num_sum %>%
  ggplot(aes(x = Condition, y = mean - 3)) +
  geom_jitter(data = d_before, aes(y = PoliticalIDNum - 3, color = PoliticalIDNum), 
              position = position_jitter(height = 0.1, width = 0.2), alpha = 0.6) +
    geom_point(aes(fill = mean), size = 3, alpha = .8) +
    geom_errorbar(aes(ymin = mean - 3 - se, ymax = mean - 3 + se), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_gradientn(
    name = "Political ID",
    colors = c("#3399CC", "#9999FF", "#CC0066"),
    values = scales::rescale(c(0, 3, 6)),
    limits = c(0, 6),
    breaks = c(0, 3, 6),
    labels = c(str_wrap("Strong Democrat",width = 5), "Independent", str_wrap("Strong Republican", width = 5)),
    guide = guide_colorbar(barwidth = 9.5, barheight = 0.5, title.position = "top")
  ) +
  scale_color_gradientn(
    name = "Political ID",
    colors = c("#3399CC", "#9999FF", "#CC0066"),
    values = scales::rescale(c(0, 3, 6)),
    limits = c(0, 6),
    breaks = c(0, 3, 6),
labels = c(str_wrap("Strong Democrat",width = 5), "Independent", str_wrap("Strong Republican", width = 5)),    guide = guide_colorbar(barwidth = 9.5, barheight = 0.5, title.position = "top")
  ) +
  scale_y_continuous(
    #limits = c(-3, 3),
    breaks = c(-3, 0, 3), 
    labels = c(str_wrap("Strong Democrat",width = 5), "Independent", str_wrap("Strong Republican", width = 5)),
  ) +
  coord_flip() +
  theme_bw() +
  labs(y = NULL, x = "Condition", title = "D. Political ID") +
  theme(
    legend.position = "top",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.title = element_blank(),
    #legend.title.align = 0.5
  )
p_politicalID_num

```


## **Location**

Now we can look at where people come from. Let's use latitude and longitude for that as it is more exact (I rounded them to the closest whole number so as to keep people anonymous, so this gives their location within about a 60 mile square). 

```{r}
dtemp <- d_before %>% filter(TimePoint=="Before")
world <- ne_countries(scale = "medium", returnclass = "sf")
d_sf <- st_as_sf(dtemp, coords = c('LON', 'LAT'))

p_location <- d_sf %>% 
  st_set_crs(4326) %>%
  ggplot() +
    theme_bw() +
    geom_sf(data=world,show.legend=FALSE,
            colour="darkgrey",fill="white") +
    geom_sf(aes(colour = PoliticalID),
            alpha=0.7,show.legend=FALSE,size=1.5) +
    coord_sf(xlim = c(-140,-50), ylim = c(10,60)) +
    scale_fill_manual(values=politicalIDColours) +
    scale_colour_manual(values=politicalIDColours) +
    facet_wrap(~Condition,ncol=3) +
    labs(title = "E. Location by political ID")+
    theme(strip.background = element_rect(colour = "black", fill = "white"),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(), 
          axis.ticks.x = element_blank(),
          plot.margin = margin(0, 0, 0,0, "pt")) 
p_location

ggsave("output/figures/demographics/location.png",
       plot=p_location,device="png",
       width=24,height=8, units="cm")
```

# Priors

## **Beliefs**

```{r}
# function to put the by topic sub-ratings of a variable and the overall score in long format for plotting
getLongVariable = function(d, variable) {
  topics <- c("AI", "Trans", "Climate", "Israel")

d_long <- d %>%
  select(UserName, Condition, starts_with(variable)) %>%
  pivot_longer(
    cols = starts_with(variable),
    names_to = "Topic",
    values_to = variable
  ) %>%
  mutate(
    Topic = case_when(
      # Check if Topic contains any of the topics
      str_detect(Topic, paste(topics, collapse = "|")) ~ 
        str_extract(Topic, paste(topics, collapse = "|")),
      # Otherwise, it's just variable or similar - replace with "Overall"
      TRUE ~ "Overall"
    )
  )

d_long
}

```

```{r}
plotViolin = function(d, variable, title, ylab, verbose = FALSE) {
  topics <- c("AI", "Trans", "Climate", "Israel")
  d_long <- getLongVariable(d,variable) %>%
    mutate(Topic = factor(Topic, levels = c(topics,"Overall")))

  if(verbose) print(head(d_long))

  # create summary variable for mean and se 
  d_summ <- d_long %>%
    group_by(Condition, Topic) %>%
    summarise(mean = mean(get(variable)), sd = sd(get(variable)), n = n()) %>%
    mutate(se = sd/sqrt(n))
  
  if(verbose) print(d_summ)
  
  p <- d_long %>%
    mutate(Condition = factor(Condition, levels = c("Left", "Control", "Right")))%>%
    ggplot(mapping = aes(
      x = Condition,
      fill = Topic
    )) +
    geom_violinhalf(aes( y = get(variable)), alpha = .7) +
    # add a point with the mean and error bars with SE
    geom_point(data = d_summ, aes(y = mean)) + 
    geom_errorbar(data = d_summ, aes(ymin = mean - se, ymax = mean + se), width = .1) + 
    facet_wrap(~Topic, nrow = 1)+
    scale_fill_manual(values = topicColours) +
    scale_colour_manual(values = topicColours) +
    scale_x_discrete(expand = expansion(add = c(0.1, 0.1))) +  # Add this line
    #lims(y = c(0,NA))+
    coord_flip()+
    #scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +  # Add this line
    theme_bw() +
    geom_hline(yintercept = 50, linetype = "dashed")+
    labs(#title = str_wrap(title,25),
        title = title,
         y = str_wrap(ylab,65),
         x = "Troll Condition") +
    theme(legend.position = "none", 
          axis.text.y = element_text(angle = 90,hjust = 0.5),
          strip.background = element_rect(colour = "black", fill = "white"))

p
}

p_initial_beliefs <- plotViolin(d_before, "Belief", "F. Initial Political Beliefs", "Lower = more Left-wing, Higher = more Right-wing")
p_initial_beliefs 
ggsave(plot = p_initial_beliefs, filename = here("output/figures/priors/initial-beliefs.png"), width = 3, height = 10)

```
## **Perceptions of consensus**

```{r}
p_initial_consensus<- plotViolin(d_before, "Consensus", "Initial Perceived Consensus About Topics", "0 = no agreement, 100 = total agreement")
p_initial_consensus
ggsave(plot = p_initial_consensus, filename = here("output/figures/priors/initial-consensus.png"), width = 3, height = 10)
```

## **Relative Beliefs**

```{r}
p_initial_relative<- plotViolin(d_before, "Relative", "Initial Perceived Own Beliefs Relative to Population", "Lower = more left wing than population, higher = more right wing")
p_initial_relative
ggsave(plot = p_initial_relative, filename = here("output/figures/priors/initial-relative.png"), width = 3, height = 10)
```

# Combined demographics plot for manuscript 

```{r}
#| fig.width: 13
#| fig.height: 11
p_demographics<- (p_race|p_education|p_religion|p_politicalID_num) + plot_layout(widths = c(1,1,1,1.3))
p_location_polid <- (p_location)#| p_polID) + plot_layout(widths = c(3, 1))

p_combined <-(p_demographics / p_location_polid/ p_initial_beliefs)+ plot_layout(heights = c(2.8,3,2.8)) & theme(text = element_text(size = 12))
p_combined
ggsave(plot = p_combined, filename = here("output/figures/combined-demographics.png"), width = 13, height = 11)
```

