---
title: "02_explore-engagement"
format: html
echo: false
message: false
warning:  false
---

```{r}
library(here)
library(tidyverse)
library(patchwork)
source(here("R/functions/colour-palettes.R"))

```

```{r}
# Engagement data prep (d_statuses_annotated, d_engagement_summ, status_colours)
# and the manuscript chi-square tests (chisq_composition, chisq_polarity,
# chisq_friendly) are defined in a shared script. The same script is sourced by
# 04_supplementary-materials.qmd, where the standardised residuals are reported.
source(here("R/functions/engagement-chisq.R"))
```
```{r}
p_engage_total <- d_engagement_summ %>%
  group_by(Condition, Type) %>%
  summarise(n = sum(n)) %>%
  ggplot(mapping=aes(y=Condition,x=n,fill=Type)) +
  geom_col(position="stack",orientation="y",colour="black") +
  theme_bw() +
  scale_y_discrete(limits = rev) +
  theme(axis.text.y = element_text(angle = 90, size=10, hjust=0.5),
        #axis.title.y = element_blank(), 
        axis.title.x=element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "top") +
  scale_fill_manual(values=status_colours) +
  guides(fill = guide_legend(reverse = TRUE)) +  
  labs(title = "A. Engagement by condition", y = "Troll Condition") 

p_engage_total

ggsave(paste0("output/figures/engagement/engagement-by-condition.png"),
       plot=p_engage_total,device="png",
       width=12,height=8, units="cm")
```

Number of posts and replies written by participants in each condition, and the share of all posts and replies contributed by troll accounts.

```{r}
d_engagement_summ %>%
  filter(Type %in% c("Post", "Reply", "Troll Post")) %>%
  group_by(Condition) %>%
  summarise(`User posts + replies` = sum(n[Type != "Troll Post"]),
            `Troll posts` = sum(n[Type == "Troll Post"]),
            `Troll share (%)` = round(100 * `Troll posts` / sum(n), 1))
```

```{r}
# Composition of engagement types (Post/Reply/Reblog/Favourite) across conditions.
# Computed in the sourced script; standardised residuals are reported in the
# Supplementary Analyses (04_supplementary-materials.qmd).
chisq_composition
```


```{r}
p_engagement_polarity <- d_engagement_summ %>%
  rename("Polarity" = "category") %>%
  mutate(Polarity = ifelse(Polarity == "not_applicable" & Topic == "Friendly", "Friendly", Polarity)) %>%
  group_by(Condition, Type, Polarity) %>%
  summarise(n = sum(n)) %>%
  filter(Type!="Sum", Polarity %in% c("Left", "Neutral", "Right")) %>%
  ggplot(mapping=aes(x=Polarity,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black") +
  theme_bw() +
  facet_wrap(~Condition,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  #scale_y_discrete(limits=rev) +
  #scale_x_continuous(limits=c(0,450)) +
  theme(#axis.text.y = element_blank(), #element_text(angle = 30, size=9, hjust=0),
    #axis.title.y = element_blank(), 
    #axis.title.x=element_blank(),
    legend.position = "none",
    axis.ticks.y = element_blank()) +
  scale_fill_manual(values=status_colours) +
    guides(fill = guide_legend(reverse = TRUE)) + 
  labs(title = str_wrap("B. Political polarity of activity by troll condition",70), x = "Polarity of Engagement", y = "Total Activity") 

p_engagement_polarity

ggsave(paste0("output/figures/engagement/engagement-by-polarity.png"),
       plot=p_engagement_polarity,device="png",
       width=12,height=8, units="cm")
```

We can also ask whether the political polarity of engagement (left, neutral, right) was the same across conditions. E.g., was there a higher share of right wing posts and replies in the right wing condition compared to control/left? We test this separately for each engagement type (Post, Reply, Reblog, Favourite). These tests are computed in the sourced script (`chisq_polarity`); the standardised residuals are reported in the Supplementary Analyses (`04_supplementary-materials.qmd`).

```{r}
imap_dfr(chisq_polarity, ~ tibble(
  `Engagement type` = .y,
  `chi-square`      = round(.x$statistic, 2),
  df                = .x$parameter,
  `p-value`         = signif(.x$p.value, 3)
))
```


```{r}
political_topics <- c("AI", "Climate", "Israel", "Trans")
text_user_political <- str_wrap("User (Political)",5)
text_user_non_political <- str_wrap("User (Non-Political)",5)

d_summ_political_post_basic <- d_engagement_summ %>%
  filter(Type == "Post" | Type == "Troll Post" ) %>%# & Condition %in% c("Left", "Right"))  %>%
  mutate(total_engagement = n_reply + n_fav + n_reblog) %>%
  group_by(Type) %>%
  summarise(total_engagement = sum(total_engagement), total_posts = sum(n),
            replies = sum(n_reply)) %>%
  mutate(engagement_per_post = total_engagement/total_posts, replies_per_post = replies/total_posts) %>%
  column_to_rownames(var = "Type")

# troll engagement per post relative to user engagement per post (troll / user - 1)
perc_troll_engagement_total <- round((d_summ_political_post_basic["Troll Post","engagement_per_post"] / d_summ_political_post_basic["Post","engagement_per_post"]) - 1,2)*100

print(paste0("Collapsing across everything else, troll posts received ",perc_troll_engagement_total,"% more engagment than posts by regular users."))

perc_troll_engagement_replies <- round((d_summ_political_post_basic["Troll Post","replies_per_post"] / d_summ_political_post_basic["Post","replies_per_post"]) - 1,2)*100

print(paste0("Collapsing across everything else, troll posts received ",perc_troll_engagement_replies,"% more replies than posts by regular users."))

d_summ_political_post <- d_engagement_summ %>%
  filter(Type == "Post" | Type == "Troll Post")  %>%
  mutate(
  Account = case_when(
      Type == "Post" & Topic %in% political_topics ~ text_user_political,# str_wrap is so the plot labels are across two lines
      Type == "Troll Post" ~ "Troll",
      TRUE ~ text_user_non_political
    ), 
  Account = factor(Account, levels = c(text_user_non_political, "Troll", text_user_political))
  )%>%
  select(-Type) %>% # redundant now because we're just looking at primary posts
  pivot_longer(cols = starts_with("n_"),
               names_to = "Type") %>%
  mutate(Type = case_when(
    Type == "n_fav" ~ "Favourite",
    Type == "n_reblog" ~ "Reblog",
    Type == "n_reply" ~ "Reply"
  )) %>%
  group_by(Condition,Account, Type) %>%
  summarise(Count = sum(value, na.rm = TRUE), n = sum(n)) %>%
  mutate(`Engagement Per Post` = Count/n)


p_troll_engagement<- d_summ_political_post %>%
  ggplot(aes(x = Account, y = `Engagement Per Post`, fill = Type)) +
  scale_fill_manual(values=status_colours) +
  geom_col(position="stack",orientation="x",colour="black")+
  labs(y = "Engagement Per Post", x = "Account Type", fill = "Engagement Type", title = str_wrap("C. Engagement per post by author in each condition",80)) + 
  facet_wrap(~Condition) +
  theme_bw()+
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(legend.position = "none")


ggsave(paste0("output/figures/engagement/troll-engagement.png"),
       plot=p_troll_engagement,device="png",
       width=12,height=8, units="cm")

p_troll_engagement
```

```{r}

p_engagement_topic <- d_engagement_summ %>%
  group_by(Condition, Type, Topic) %>%
  summarise(n = sum(n)) %>%
  ggplot(mapping=aes(x=Topic,y=n,fill=Type)) +
  geom_col(position="stack",orientation="x",colour="black") +
  theme_bw() +
  facet_wrap(~Condition,ncol=7) +
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)
    ) +
  scale_fill_manual(values=status_colours) +
  labs(title = str_wrap("D. Topic of activity by troll condition",70), x = "Topic", y = "Total Activity")

p_engagement_topic  

ggsave(paste0("output/figures/engagement/engagement-by-topic.png"),
       plot=p_engagement_topic,device="png",
       width=12,height=8, units="cm")

```

Let's see whether the "friendly" engagement is evenly distributed across conditions. 

```{r}
# Friendly vs non-friendly engagement (posts and replies) across conditions.
# Computed in the sourced script; standardised residuals are reported in the
# Supplementary Analyses (04_supplementary-materials.qmd).
chisq_friendly
```


# **Replies received**
```{r}
#| plot.width: 12

# get polarity of replies
d_activity_annotated_with_reply_polarity <- d_statuses_annotated %>%
  left_join(
    d_statuses_annotated %>%
      select(StatusID, category) %>%
      rename(StatusReplyID = StatusID,
             ReplyPolarity = category),
    by = "StatusReplyID"
  )

troll_accounts <- unique(d_statuses_annotated[d_statuses_annotated$Troll == 1, "UserName"])

polarity_of_replies_received <- d_activity_annotated_with_reply_polarity %>%
  group_by(AccountReply, Condition, Topic, category) %>%
  summarise(NeutralReceived = sum(category == "Neutral" | is.na(category)),
            DissentingLeftReceived = sum(category == "Left" & ReplyPolarity == "Right", na.rm = TRUE), # Left wing replies to right wing posts
            DissentingRightReceived = sum(category == "Right" & ReplyPolarity == "Left", na.rm = TRUE), # Right wing replies to left wing posts
            SupportingLeftReceived = sum(category == "Left" & ReplyPolarity == "Left", na.rm = TRUE), # Left wing replies to left wing posts
            SupportingRightReceived = sum(category == "Right" & ReplyPolarity == "Right", na.rm = TRUE), # Right wing replies to right wing posts
  ) %>%
  # remove confederate accounts
  filter(!AccountReply %in% troll_accounts) %>%
  rename("UserName" = AccountReply)
  
d_replies_type_long <- polarity_of_replies_received %>%
         #   mutate(Dissenting = DissentingLeftReceived + DissentingRightReceived,
         # Supporting = SupportingLeftReceived + SupportingRightReceived) %>%
  pivot_longer(
    cols = c("DissentingLeftReceived","DissentingRightReceived", "NeutralReceived", "SupportingLeftReceived", "SupportingRightReceived"),
    names_to = "ReplyType",
    values_to = "Count"
  )  %>%
  mutate(Stance = case_when(
    grepl("Dissenting", ReplyType) ~ "Dissenting",
    grepl("Neutral", ReplyType) ~ "Neutral",
    grepl("Supporting", ReplyType) ~ "Supporting",
  ),
  Polarity = case_when(
    grepl("Left", ReplyType) ~ "Left",
    grepl("Right", ReplyType) ~ "Right",
    grepl("Neutral", ReplyType) ~ "Neutral"
  )) 

```

```{r}

p_engagement_replies <- d_replies_type_long %>%
  group_by(Condition, Stance, Polarity) %>%
  summarise(n_replies = sum(Count)) %>%
  ggplot(aes(x = Stance, y = n_replies, fill = Polarity)) +
  geom_col(position="stack",orientation="x",colour="black") +
  facet_wrap(~Condition) +
  scale_fill_manual(values=polarityColours) +
  theme_bw()+
  theme(strip.background = element_rect(colour = "black", fill = "white")) +
  theme(
    #legend.position = "none",
    axis.ticks.y = element_blank(),
    #axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)
  ) +
  #scale_fill_manual(values=status_colours) +
  labs(title = str_wrap("E. Stance and polarity of replies by troll condition",70), x = "Stance of Engagement", y = "Total Number of Replies")

p_engagement_replies
```
# **Combine**

```{r}
#| fig.width: 13
#| fig.height: 11
p_engagement_combined <- (p_engage_total / ((p_engagement_polarity / p_troll_engagement) | (p_engagement_topic/p_engagement_replies))) + plot_layout(heights = c(1,2.5))
  
p_engagement_combined

ggsave(plot = p_engagement_combined, filename = here("output/figures/combined-engagement.png"), width = 13, height = 11)
```

